### 2013-09-30 paper.tex
Updated the gitignore and added some initial writing for the paper.

\documentclass[twocolumn,11pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{fancyhdr}
\usepackage{algpseudocode}
\usepackage[toc,page]{appendix}
\usepackage{url}

\setlength{\parskip}{5pt plus1pt minus1pt}

\DeclareMathSizes{36}{36}{36}{36}

\title{Train Harder, Better:\\Using graph theory to improve your
  training regimen}
\author{Forest Trimble\\trimbf@rpi.edu}
\begin{document}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{Forest Trimble}
\fancyhead[R]{Train Harder, Better}
\maketitle

\begin{abstract}
  \emph{Cyclists are always in search of the perfect ride on the perfect
  roads. They have criteria like distance and elevation gain to ensure
  that they get in the workout that they want. Unfortunately, in order to
  find this ideal ride manually, it takes a great deal of exploring and
  time, and eventually, one may settle into the habit of using the same
  roads that he/she already knows. We research a way to improve this
  paradigm, and to generate cyclists exactly the route they are looking
  for, without them having to do any work.}
\end{abstract}

\section{Background}

Cycling can be wildly different based on the roads that one takes: On busy
roads with no shoulders, it can be borderline miserable, while few things in
the world are better than spinning down a smoothly paved road with beautiful
vistas of open countryside. Unfortunately, cyclists need to invest massive
amounts of time and energy exploring the roads and amassing a repertoire that
they can use. Additionally, it is difficult to satisfy criteria for training,
like an elevation gain and distance, using only that mental repertoire. This
paper chronicles the attempt to unroll a solution for this problem.

Specifically, a good solution should take as input a distance to travel, a
start point, and, optionally, an elevation gain, and generate a route from the
start point that satisfies the distance and elevation gain within some
$\epsilon$. A fully robust solution would also utilize user data to ensure that
it traverses the most pleasant roads to ride on and avoids the worst.

\section{Tools}

In order to do this in a useful way

\end{document}

### 2013-10-22 paper.tex
Added serious changes to the writeup to include information about the algorithm.

@@
 \documentclass[twocolumn,11pt]{article}
+
+\textheight 9 in
+\voffset -.75 in
 
@@
 \usepackage{epstopdf}
+\usepackage{tikz}
 \usepackage{fancyhdr}
@@
 \setlength{\parskip}{5pt plus1pt minus1pt}
+\setlength{\headheight}{15pt}
 
@@
 
-\title{Train Harder, Better:\\Using graph theory to improve your
-  training regimen}
+\title{Train Harder, Smarter:\\Using Graph Theory to Create Route Sugestions}
 \author{Forest Trimble\\trimbf@rpi.edu}
@@
 \fancyhead[L]{Forest Trimble}
-\fancyhead[R]{Train Harder, Better}
+\fancyhead[R]{Train Harder, Smarter}
 \maketitle
@@
 the world are better than spinning down a smoothly paved road with beautiful
-vistas of open countryside. Unfortunately, cyclists need to invest massive
-amounts of time and energy exploring the roads and amassing a repertoire that
-they can use. Additionally, it is difficult to satisfy criteria for training,
-like an elevation gain and distance, using only that mental repertoire. This
-paper chronicles the attempt to unroll a solution for this problem.
+vistas of open countryside and no traffic. Unfortunately, cyclists need to
+invest massive amounts of time and energy exploring the roads and amassing a
+repertoire that they can use. Additionally, it is difficult to satisfy criteria
+for training, like an elevation gain and distance, using only that mental
+repertoire. This paper chronicles the attempt to unroll a solution for this
+problem.
 
@@
 
-In order to do this in a useful way
+Creating a solution to this problem from scratch would require immense amounts
+of time and effort that are simply not available. Fortunately, the larger part
+of this problem has already been solved: maps have already been digitized and
+parsers for the data format already exist. This section details the various
+tools and technologies that the algorithm leverages.
+
+First and foremost, we opted to use the Open Street Map format, which is open
+source, fairly robust, and has a very active community that contributes to both
+the maps themselves and to various (mostly open-source) software projects that
+utilize the format. More information on this format can be found on their
+website, openstreetmap.org.
+
+INFO ON OSRM
+
+\section{Algorithm}
+
+The most important part of all of this is how it actually works. The core idea
+is that at any point along the route, the engine generates weights for each
+different possible direction to take, generates a random number, and picks a
+direction according to the random number and the weights. There are several
+different ideas that are competing for weight, so we'll break it down into the
+individual components first, and then describe the combination at the end.
+
+Additionally, the algorithm requires a few inputs from the user (in addition
+to the Open Street Map network of roads):
+\begin{itemize}
+\item A distance to travel, $d$.
+\item A direction in which to head $\phi$.
+\item An elevation to gain, $h$.
+\item A start point, $x_0$.
+\end{itemize}
+
+\subsection{Weight for Distance}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \node (init) at (-0.5,0) {$\mbox{pos}_0$};
+    \filldraw (0,0) circle(0.05);
+
+    \draw (2,0) circle(2);
+    \draw[dashed] (0,0) -- (0.3,-.5) -- (0.8,-0.2) -- (0.5,0.1) -- (0.8,0.4) --
+    (1.0,0.8) -- (1.1,1.3) -- (1.3,1.0) -- (1.3,0.4) -- (1.4, 0) -- (1.6, -0.5)
+    -- (1.8, -1) -- (2.0,-1.5) -- (2.1,-1.8) -- (2.4,-1.8) -- (2.6,-2.3) --
+    (2.7,-2.8) -- (3.1,0.7) -- (3.4,0.8) -- (3.2,0.9) -- (3.0,0.4) -- (2.8,0.9)
+    -- (2.4,1.3) -- (2.2,0.6) -- (2.3,0.3) -- (2.0,-0.4) -- (1.7, -0.2) --
+    (1.4,-1) -- (1.0,-1.3) -- (-0.2,-1) -- (0,0);
+
+    \node (mainleg) at (5,2) {The ideal loop};
+    \node (altleg) at (5,1.5) {A possible loop};
+    \draw (3,2) -- (3.5,2);
+    \draw[dashed] (3,1.5) -- (3.5,1.5);
+  \end{tikzpicture}
+  \caption{The ideal loop starting at $\mbox{pos}_0$ contrasted with a possible
+    actual loop} \label{fig:ideal}
+\end{figure}
+
+The first weight is based on distance. The idea is that there is a theoretical,
+perfect loop that covers exactly the amount of distance that you would like,
+and the algorithm does its best to direct you along that loop. See
+Figure~\ref{fig:ideal} for an example of what this might look like.
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \node (theta) at (0,4.2) {$\theta$};
+
+    \node (max) at (0.2,3) {2};
+    \node (min) at (0.35,1) {0.5};
+    \node (avg1) at (-1,2.2) {1};
+    \node (avg2) at (1,2.2) {1};
+
+    \draw[thick,<->] (0,0) -- (0,4);
+    \draw[thick,<->] (-2,2) -- (2,2);
+  \end{tikzpicture}
+  \caption{A possible weighted compass} \label{fig:weights}
+\end{figure}
+
+In order to direct you along this loop, weights are generated based on
+direction. We'll consider the method for finding the optimal direction,
+$\theta$, briefly. First, consider how the weights are generated once
+that direction is discovered. Basically, there is a weighted compass oriented
+along $\theta$, with weights from 0.5 to 2. See Figure~\ref{fig:weights} to
+see what we mean. As shown, the weights do not scale linearly, instead, the
+weight of any angle, $\tau$, is calculated as follows:
+\begin{equation}
+  \mbox{WEIGHT} = 2^{1-\frac{2}{\pi}|\theta-\tau|}. \label{eq:weight}
+\end{equation}
+
+Now, we consider the method for finding the ideal direction. The idea behind the
+direction loop is that if we had an ideal route, it would run exactly along that
+path. Then the ideal direction is the one that puts us in the correct location
+along that loop. First, consider how the loop is derived. It is a perfect
+circle, passing through $x_0$, with a circumfrence of $d$, oriented according to
+$\phi$. Note that $d$ and $x_0$ are fairly easy to understand, but the meaning
+ of $\phi$ is less obvious. In order to understand what we mean, first consider
+the parametric equations for a circle:
+\[ x = \cos t \]
+\[ y = \sin t \]
+These equations generate the unit circle around the origin, something that we
+will address later. For now, we are concerned only about what they mean for
+$\phi$. Note that without alteration these equations will generate a
+west-oriented loop: the circle starts at the rightmost point and proceeds left.
+Consider a revised set of equations incorporating $\phi$:
+\[ x = \cos (t + \phi) \]
+\[ y = \sin (t + \phi). \]
+As mentioned already, $\phi = 0$ corresponds to the west-oriented loop, and one
+can quickly see that $\phi = \frac{\pi}{2}$ corresponds to the southern loop,
+$\phi = \pi$ to the eastern, and $\phi = \frac{3\pi}{2}$ to the northern. That
+being said, none of these loops actually start at the proper point; they are
+centered around the origin rather than beginning at it. In order to have any
+choice of $\phi$ generate a loop that starts at the origin, we can simply zero
+out the initial value:
+\[ x = \cos (t + \phi) - \cos \phi \]
+\[ y = \sin ( t + \phi ) - \sin \phi. \]
+This gives a much more obvious representation of our ideal loop, which starts
+at (0,0), and traces out a loop according to $\phi$. One thing of interest is
+that $\phi$ is exactly $\pi$ plus the compass direction that we would expect.
+
+Once you recall that our distance goal, $d$, is the circumfrence of the loop,
+it is easy to see that the radius is $\frac{d}{2\pi}$. We can then adjust our
+equation to correspond with our starting point and radius as follows:
+\[ x = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + x_0.x \]
+\[ y = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + x_0.y \]
+Of course, this needs some adjustment to deal with the difference of using
+latitude and longitude over a cartesian coordinate system, since latitude
+and longitude are not actually coordinates on a 2-d plane, but rather angles
+that are made against the center of the Earth. For now, this is sufficient to
+get an idea of what is happening, but we'll cover how this will be converted
+into a latitude/longitude format in Section~\ref{sec:latlong}.
+
+Until now, we've used $t$ to represent the angle in the parametric equation,
+without delving into what it really means. However, we can use a much more
+useful expression to represent this angle: $\frac{2\pi}{d}d_i$, where $d_i$ is
+the current distance travelled, gives us the
+angle in terms of a percentage of the requisite distance travelled. This gives
+us the advantage of knowing exactly where in the loop we should be at any
+current distance travelled. This also needs to be capped after $d_i \geq d$.
+Incorporating this yields the final equations:
+\[ x = \frac{d}{2\pi}(\cos (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \cos \phi) + x_0.x \]
+\[ y = \frac{d}{2\pi}(\sin (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \sin \phi)+ x_0.y. \]
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \draw (2,0) circle(2);
+    \filldraw (0,0) circle(0.05);
+    \node at (0.4,0.1) {$x_0$};
+
+    \draw[thick,<->] (-0.2,0) arc (180:300:2.2);
+    \node at (0.6,-2) {$d_i$};
+    \filldraw (3.05,-1.7) circle(0.05);
+
+    \draw[thick,<->] (4.2,0) arc (0:-60:2.2);
+    \node at (4.2,-1.3) {$d_j$};
+
+    \filldraw (4,0) circle(0.05);
+    \node at (4.2,0.2) {$x_j$};
+
+    \node at (1.8,-0.7) {$x_i$};
+    \node at (2.7,-1.4) {$x_{\mbox{{\tiny ideal}}}$};
+
+    \filldraw (2.1,-0.7) circle (0.05);
+
+    \draw[dashed] (2.1,-0.7) -- (4,0) node[above,midway,sloped] {$d_j$};
+
+    \draw[dashed] (2.1,-0.7) -- (3.2,-0.7);
+    \draw[<->] (3.2,-0.7) arc(0:20:1.1);
+    \node at (3.4,-0.5) {$\theta$};
+  \end{tikzpicture}
+  \caption{Important values for the algorithm \emph{Note: not to scale}}
+  \label{fig:algvals}
+\end{figure}
+
+The next step is to utilize these equations to calculate $\theta$. At any point
+along the algorithm, we are at some $x_i$, and we have travelled a distance,
+$d_i$. Figure~\ref{fig:algvals} should help to understand what exactly the
+algorithm is attempting to achieve. The idea is this: if we have travelled some
+distance $d_i$, then there is an $x_{\mbox{{\tiny ideal}}}$ on the ``ideal''
+loop. The arc between $x_{\mbox{{\tiny ideal}}}$ and $x_0$ will be of length
+$d_i$. The algorithm searches for a point $x_j$ such that the arc between
+$x_{\mbox{{\tiny ideal}}}$ and $x_j$ will have the \emph{same} distance as the
+line between $x_i$ and $x_j$. Fortunately, we have framed the equations for
+calculating $x_j$ in terms of the distance travelled along the arc, and the
+distance between $x_i$ and $x_j$ can easily be calculated using the pythagorean
+theorem. Note that we find $x_j$ as follows:
+\begin{align}
+  x_j.x = \frac{d}{2\pi} ( & \cos( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
+                                  + \phi ) \notag \\ & - \cos \phi ) + x_0.x
+                                  \label{eq:xjx} \\
+  x_j.y = \frac{d}{2\pi} ( & \sin( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
+                                  + \phi ) \notag \\ & - \sin \phi ) + x_0.y.
+                                  \label{eq:xjy}
+\end{align}
+To satisfy our constraint, we have
+\begin{equation}
+  d_j = \sqrt{ ( x_j.x - x_i.x )^2 + ( x_j.y - x_i.y )^2 }. \label{eq:dists}
+\end{equation}
+Obviously, this is a rather difficult equation to truly solve, so we must only
+heuristically find a solution. Luckily, we
+have a fairly small search space, since $d - d_i > d_j > 0$. On the other hand,
+it is not readily apparent how these solutions will behave. We can, however,
+be certain that it is continuous, so we can proceed as follows:
+\begin{enumerate}
+\item Check if the optimal solution would require that we move around the loop
+  again. This will happen if
+  \[d_i+\sqrt{(x_0.x-x_i.x)^2+(x_0.y-x_i.y)^2} > d.\]
+  In this case, we set $x_j = x_0$, and stop searching.
+\item \emph{NEEDS MORE WORK}
+\end{enumerate}
+
+At this point, we have found $x_j$. From here, calculating $\theta$ is fairly
+straightforward:
+\begin{align}
+  \tan \theta = & \frac{x_j.y - x_i.y}{x_j.x-x_i.x} \notag \\
+  \theta = & \tan^{-1} \frac{x_j.y - x_i.y}{x_j.x-x_i.x} \label{eq:theta}
+\end{align}
+
+Finally, we have a method for calculating the weights based on distance and
+direction! Use \eqref{eq:xjx}, \eqref{eq:xjy}, and \eqref{eq:dists} to find
+an $x_j$, and plug into \eqref{eq:theta} to find a $\theta$. Finally, use
+$\theta$ in conjunction with \eqref{eq:weight} to assign weights to
+directions.
+
+\subsection{Weight for Elevation Gain}
+
+Now that weights have been assigned based on distance and direction, we can
+move on to worrying about elevation gain.
+
+FILL IN THIS SECTION
+
+\subsection{Miscellaneous Weights}
+
+There are a few more important characteristics to consider when calculating
+weights. Perhaps the easiest of these to deal with are the built in road types
+that the Open Street Map format provides. It is easy enough to assign these
+priorities based on what a cyclist would reasonably hope to see. Basically,
+busy roads get weighted lower than low-traffic roads, but things like
+pedestrian walkways and other unridable roads also get high weights.
+
+Another characteristic to consider is whether a road has already been
+travelled. Repeatedly riding along the same stretch of road can make a ride
+rather boring, so by weighting against this, it can be avoided.
+
+ARE THERE MORE FOR THIS SECTION?
+
+\subsection{Using the Weights Together}
+
+\section{Moving to Three Dimensions} \label{sec:latlong}
 

### 2013-11-08 paper.tex
Added the pyroute files to the repo.
This is perhaps a bit silly, as most of the development will
occur only in the pyroutelib functions, but it's being done
nonetheless.

@@
 \setlength{\parskip}{5pt plus1pt minus1pt}
-\setlength{\headheight}{15pt}
 
@@
 
-\title{Train Harder, Smarter:\\Using Graph Theory to Create Route Sugestions}
+\title{Train Harder, Smarter:\\Using Graph Theory to Create Route Suggestions}
 \author{Forest Trimble\\trimbf@rpi.edu}
 \begin{document}
+
+\setlength{\headheight}{15pt}
 
@@
   roads. They have criteria like distance and elevation gain to ensure
-  that they get in the workout that they want. Unfortunately, in order to
+  that they get in the workout that they want. Unfortunately, to
   find this ideal ride manually, it takes a great deal of exploring and
@@
 start point that satisfies the distance and elevation gain within some
-$\epsilon$. A fully robust solution would also utilize user data to ensure that
+tolerance. A fully robust solution would also utilize user data to ensure that
 it traverses the most pleasant roads to ride on and avoids the worst.
@@
 
-Creating a solution to this problem from scratch would require immense amounts
-of time and effort that are simply not available. Fortunately, the larger part
-of this problem has already been solved: maps have already been digitized and
+Creating a solution to this problem from scratch is unnecessary. The larger part
+of this problem has already been solved: maps have been digitized and
 parsers for the data format already exist. This section details the various
@@
 
-INFO ON OSRM
+Additionally, we leveraged some existing code to more easily be able to create
+a demonstrable algorithm. Pyroute was used, since it has the very nice feature
+that the navigation component was entirely decoupled into PyrouteLib. This
+allows easy utilization of the Pyroute tools for GUI setup and OSM download
+while also making it rather explicit where the navigation functions are. The
+OSM wiki pages have a good deal of information
+on Pyroute and PyrouteLib; refer to them for more information.
 
@@
 
-The most important part of all of this is how it actually works. The core idea
+The core idea of our algorithm
 is that at any point along the route, the engine generates weights for each
@@
 along $\theta$, with weights from 0.5 to 2. See Figure~\ref{fig:weights} to
-see what we mean. As shown, the weights do not scale linearly, instead, the
-weight of any angle, $\tau$, is calculated as follows:
+see what we mean. As shown, the weights do not scale linearly. Instead, they
+scale exponentially. This ensures that the weights are mostly centered around
+the perpendicular, with growth accelerating farther from the perpendicular.
+The idea is to have the weight be double in the ideal
+direction, half moving exactly opposite the ideal direction, and unchanged
+perpendicular to the ideal direction. Considering these three pieces of
+information, we are looking for some $f : [0,2\pi] \to [0.5,2]$ as follows:
+\begin{align*}
+  2 = & f(\theta) \\
+  1 = & f(\theta \pm \frac{\pi}{2}) \\
+  \frac{1}{2} = & f(\theta \pm \pi)
+\end{align*}
+Let $\tau$ be the angle under consideration. We let
+\[ \mbox{ang}(\tau, \theta) = |\theta - \tau \mbox{ mod } \pi|. \]
+This allows us to define $f$ in terms of the angle between $\tau$ and
+$\theta$. This function is necessary because $\theta$ is not necessarily
+0. Note that this function only allows $\mbox{ang}(\tau, \theta)
+\in [0,\pi]$. We accept this since we would like a compass symmetric
+over the angle $\theta$, and we don't care if the angles are negative
+or positive. However, the original function was defined in terms of the
+value of $\tau$; instead, we are interested in a function based on the
+angle between $\tau$ and $\theta$, which requires a slight redefinition:
+\begin{align*}
+  2 = & g(0) \\
+  1 = & g(\frac{\pi}{2}) \\
+  \frac{1}{2} = & g(\pi)
+\end{align*}
+We've already expressed the fact that we're interested in an exponential
+function, and a base of two seems the obvious choice, leading to another
+reduction:
+\begin{align*}
+  2 = 2^{h(0)} & \to & h(0) = 1 \\
+  1 = 2^{h(\frac{\pi}{2})} & \to & h(\frac{\pi}{2}) = 0\\
+  \frac{1}{2} = 2^{h(\pi)} & \to & h(\pi) = -1
+\end{align*}
+This yields two sets of three collinear points, which is easy enough to
+map one to the other. Consider $h : [0,\pi] \to [-1,1]$ as follows:
+\[ h(\mbox{ang}(\tau,\theta)) = 1 - \frac{2}{\pi}\mbox{ang}(\tau, \theta). \]
+This satisfies the three points we gave, so we plug it in and calculate weight
+accordingly:
 \begin{equation}
-  \mbox{WEIGHT} = 2^{1-\frac{2}{\pi}|\theta-\tau|}. \label{eq:weight}
+  \mbox{WEIGHT} = 2^{1-\frac{2}{\pi}\mbox{ang}(\tau,\theta)}. \label{eq:weight}
 \end{equation}
@@
 
-ARE THERE MORE FOR THIS SECTION?
-
 \subsection{Using the Weights Together}
@@
 
+\section{Experimentation \& Results}
+
+\section{Discussion}
+
+\section{Future Work}
+
+There are many ways to expand the algorithm developed here. While we have done
+our best to utilize as much data as possible, expanding the set of data utilized
+to generate the routes will likely improve the algorithm.
+
+ (ASK DAN FOR THIS
+PAPER) There has been research done into analyzing the probability of accidents
+on a road based on certain metadata. This metadata is readily available to the
+cities that own the roads, but it is seldom available for direct access inside
+of maps. If this data becomes more readily available, then it can be integrated
+into the application to help increase user safety.
+
+Additionally, this has been a facet of a three pronged project developing a
+platform for bicycle training. The other two aspects are developing an Android
+application to track training data during a ride and a website to track
+long-term training data. Ideally, this algorithm will eventually be seamlessly
+integrated into the mobile and web projects, so that routes can be generated
+and sent directly to the application for the user to follow.
+
+Once the three prongs of this project have been integrated together, leveraging
+the data from the other parts would also provide valuable input for the
+algorithm. One of the most exciting applications of this information is to
+generate something similar to a heatmap of roads that users of the website
+ride. With this heatmap, the weights could be improved and generated based on
+popularity.
+
+Finally, it might be interesting to generate routes that are not necessarily
+circuits. Loops are generally more useful since cyclists are likely to want
+to return home after a good training ride, but it might also be useful to
+have some sort of quasi-navigation that aims for the most fun route
+between two locations rather than the most direct route.
+
 \end{document}

### 2013-11-08 pyroute/applications/routing/pyroute-dev/dataStore.py

@@ -1,0 +1,49 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Global data table
+
+Usage:
+	(library code for pyroute GUI, not for direct use)
+
+Types of data stored:
+	* Options and settings
+	* Data (e.g. current position)
+	* Event-related data (e.g. position of last click)
+
+Not stored here:
+	* Routes (internal within the routing module)
+	* POIs and map data
+
+TODO:
+	* Event handling code needs to be moved into a module
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from base import pyrouteModule
+
+class DataStore(pyrouteModule):
+	def __init__(self, modules):
+		pyrouteModule.__init__(self,modules)
+		self.options = {}
+
+	def getData(self,name,default=None):
+		return(self.options.get(name,default))
+
+	def setData(self,name,value):
+		self.options[name] = value

### 2013-11-08 pyroute/applications/routing/pyroute-dev/events.py

@@ -1,0 +1,150 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Event handler.  Messages (as text) get sent here, telling pyroute
+to do various things (e.g. save a waypoint, open a menu, route to
+some point)
+
+Usage:
+	(library code)
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from base import pyrouteModule
+
+class pyrouteEvents(pyrouteModule):
+	def __init__(self, modules):
+		pyrouteModule.__init__(self,modules)
+
+	def handle_zoom(self,params):
+		"""zoom:[in|out|zoomlevel] - zooms to a quadtile level (17=max detail, <6=whole world)"""
+		if(params == 'in'):
+			self.m['projection'].setZoom(1, True)
+		elif(params == 'out'):
+			self.m['projection'].setZoom(-1, True)
+		else:
+			self.m['projection'].setZoom(int(params))
+		self.set("needRedraw", True)
+
+	def handle_menu(self,params):
+		"""menu:(name) - displays a menu. Use blank name to hide the menu"""
+		self.set('menu', params)
+
+	def handle_mode(self,params):
+		"""mode:(name) - sets the transport type in use (e.g. car, bike)"""
+		self.set('mode', params)
+
+	def handle_save(self,params):
+		whichModule = params
+		self.m[whichModule].save()
+
+	def handle_option(self,params):
+		"""option:add|toggle:(name):(value)"""
+		method, name = params.split(':',1)
+		if(method == 'toggle'):
+			self.set(name, not self.get(name))
+		elif(method == 'add'):
+			name,add = name.split(':')
+			self.set(name, self.get(name,0) + float(add))
+		elif(method == 'set'):
+			name,value = name.split(':')
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/geoPosition.py

@@ -1,0 +1,115 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""report "current position" (currently accepts replayed GPX
+files from follow.py)
+
+Usage:
+	pos = geoPosition(filename_of_latlong_file)
+	lat,lon = pos.get()
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from time import sleep
+import os
+import re
+import socket
+import sys
+
+class geoPosition:
+	def __init__(self):
+		self.mode = "none"
+		try:
+			self.s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+			self.s.connect(("127.0.0.1", 2947))
+			self.mode = "socket"
+		except socket.error:
+			print "No GPSD detected, position information will not be available"
+			pass # leave mode at "none"
+
+		self.filename = os.path.join(os.path.dirname(__file__), "pos.txt")
+		if(os.path.exists(self.filename)):
+			self.mode = "file"
+			print "Using %s as position reference" % self.filename
+
+		self.filename = os.path.join(os.path.dirname(__file__), "init_pos.txt")
+		if(os.path.exists(self.filename)):
+			self.mode = "initfile"
+			print "Using %s as initial position reference" % self.filename
+
+	def get(self):
+		try:
+				function = getattr(self, 'get_%s' % self.mode)
+		except AttributeError:
+				return({'valid':False,'message':"function for %s not defined" % self.mode})
+		return(function())
+
+	def get_none(self):
+		return({'valid':False,'message':"no gps"})
+
+	def socket_cmd(self, cmd):
+		self.s.send("%s\r\n" % cmd)
+		return self.s.recv(8192)
+
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/gui.py

@@ -1,0 +1,409 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Pyroute main GUI
+
+Usage:
+	gui.py
+
+Controls:
+	* drag left/right along top of window to zoom in/out
+	* drag the map to move around
+	* click on the map for a position menu
+			* set your own position, if the GPS didn't already do that
+			* set that location as a destination
+			* route to that point
+	* click on the top-left of the window for the main menu
+			* download routing data around your position
+			* browse geoRSS, wikipedia, and OSM points of interest
+			* select your mode of transport for routing
+					* car, bike, foot currently supported
+			* toggle whether the map is centred on your GPS position
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from gtk import gdk
+from math import sqrt
+from time import clock
+import cairo
+import gobject
+import gtk
+import os
+import pygtk
+import sys
+import urllib
+pygtk.require('2.0')
+
+# Our modules:
+from base import pyrouteModule
+from dataStore import *
+from events import pyrouteEvents
+from geoPosition import *
+from meta import moduleInfo
+from mod_osmData import osmData
+from overlay import *
+from poi_geoRss import geoRss
+from poi_geonames import geonames
+from poi_osm import osmPoiModule
+from poi_waypoints import waypointsModule
+from projection import Projection
+from routeOrDirect import *
+from sketch import sketching
+from tilenames import *
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/lib_gpx.py

@@ -1,0 +1,85 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Library for handling GPX files
+
+Usage:
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from xml.sax import make_parser, handler
+import cairo
+import os
+
+class lib_gpx(handler.ContentHandler):
+	""""""
+	def __init__(self):
+		self.lines = []
+
+	def draw(self,cr,proj):
+		cr.set_line_cap(cairo.LINE_CAP_ROUND)
+		cr.set_source_rgb(0.7,0.7,0)
+		cr.set_line_width(5)
+
+		for l in self.lines:
+			first = 1
+			for p in l:
+				x,y = proj.ll2xy(p[0], p[1])
+				if(first):
+					cr.move_to(x,y)
+					first = 0
+				else:
+					cr.line_to(x,y)
+			cr.stroke()
+
+	def saveAs(self,filename, title="untitled"):
+		file = open(filename,"w")
+		file.write("<?xml version=\"1.0\"?>\n")
+		file.write('<gpx>\n')
+		file.write('<trk>\n')
+		file.write('<name>%s</name>\n' % title)
+		for l in self.lines:
+			file.write('<trkseg>\n')
+			for p in l:
+				file.write('<trkpt lat="%f" lon="%f"/>\n'%(p[0], p[1]))
+			file.write('</trkseg>\n')
+		file.write('</trk>\n')
+		file.write('</gpx>\n')
+
+		file.close()
+
+	def load(self, filename):
+		if(not os.path.exists(filename)):
+			print "No such tracklog \"%s\"" % filename
+			return
+		self.inField = False
+		parser = make_parser()
+		parser.setContentHandler(self)
+		parser.parse(filename)
+
+	def startElement(self, name, attrs):
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/listable.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Interface for things which can be listed
+
+Usage:
+	(base-class for pyroute GUI libraries)
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+class listable:
+	"""Base-class (interface) for anything that can be listed in a menu"""
+	def numItems(self):
+		"""Return how many items are available"""
+		return(0)
+
+	def getItemText(self,n):
+		"""Return the label for any item number"""
+		return("-")
+
+	def getItemStatus(self,n):
+		"""Return current status for any item number"""
+		return("-")
+
+	def isLocation(self,n):
+		"""Return true if the item represents a location"""
+		return(False)
+
+	def getItemLatLon(self,n):
+		"""If the item represents a location, return it's position"""
+		return(0,0)
+
+	def getItemClickable(self,n):
+		"""If not a location, return true if the item should have a button to click on"""
+		return(False)
+
+	def getItemAction(self,n):
+		"""If the item isn't a location, return what happens if it's selected"""
+		return("")
+

### 2013-11-08 pyroute/applications/routing/pyroute-dev/mod_osmData.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from base import pyrouteModule
+from loadOsm import LoadOsm
+import os
+import urllib
+
+class osmData(pyrouteModule):
+	def __init__(self, modules):
+		pyrouteModule.__init__(self,modules)
+		self.data = LoadOsm(None)
+
+	def defaultFilename(self):
+		return("data/routing.osm")
+
+	def loadDefault(self):
+		self.load(self.defaultFilename())
+
+	def load(self,filename):
+		print "Loading OSM data from %s"%filename
+		self.data.loadOsm(filename)
+
+	def download(self,params):
+		ownpos = self.get('ownpos')
+		if(not ownpos['valid']):
+			print "Can only download around own position"
+			return
+
+		lat = ownpos['lat']
+		lon = ownpos['lon']
+		size = 0.2
+
+		url = "http://informationfreeway.org/api/0.5/way[bbox=%1.4f,%1.4f,%1.4f,%1.4f][highway|railway|waterway=*]" % (lon-size,lat-size,lon+size,lat+size)
+
+		print "downloading %s" % url
+
+		filename = self.defaultFilename()
+
+		if(os.path.exists(filename)):
+			print "Removing existing file"
+			os.remove(filename)
+
+		urllib.urlretrieve(url, filename)
+
+		print "Finished downloading"
+		self.load(filename)

### 2013-11-08 pyroute/applications/routing/pyroute-dev/overlay.py

@@ -1,0 +1,457 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from base import pyrouteModule
+from colorsys import hsv_to_rgb
+from menuIcons import menuIcons
+from overlayArea import overlayArea
+from pyrouteMenu import *
+import cairo
+import geometry
+import os
+
+class guiOverlay(pyrouteModule):
+	def __init__(self, modules):
+		pyrouteModule.__init__(self, modules)
+		self.modules = modules
+		self.icons = menuIcons()
+		self.menus = loadMenus(os.path.join(os.path.dirname(__file__), 'Menus'))
+		self.dragbar = None
+		self.dragpos = 0
+
+	def fullscreen(self):
+		"""Asks if the menu is fullscreen -- if it is, then the
+		map doesn't need to be drawn underneath"""
+		return(self.get('menu'))
+
+	def handleDrag(self,dx,dy,startX,startY):
+		if(self.dragbar):
+			if(self.dragbar.contains(startX,startY)):
+				scale = -20.0 / float(self.rect.h)
+				self.dragpos = self.dragpos + dy * scale
+				if(self.dragpos < 0):
+					self.dragpos = 0
+				#print "Dragging %1.2f (by %1.2f * %1.2f)" % (self.dragpos, dy,scale)
+				return(True)
+		return(False)
+
+	def handleClick(self,x,y):
+		"""return 1 if click was handled"""
+		for cell in self.clickable:
+			if(cell.contains(x,y)):
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/overlayArea.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Graphics library for drawing pyroute GUI menus
+
+Usage:
+	(library code for pyroute GUI)
+
+Features:
+	Start by initialising a 'rectangle' that covers a certain bit of screen
+	Then you can
+		* Draw an icon there
+		* Draw text in the rectangle
+		* Make it clickable (so that it triggers an event when clicked)
+		* Split it into smaller rectangles (to do complex GUI layouts)
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+import cairo
+import os
+
+class overlayArea:
+	def __init__(self,cr,x,y,dx,dy,modules,iconSet):
+		self.cr = cr
+		self.x1 = x;
+		self.y1 = y;
+		self.x2 = x + dx;
+		self.y2 = y + dy;
+		self.w = dx
+		self.h = dy
+		self.cx = x + 0.5 * dx
+		self.cy = y + 0.5 * dy
+		self.event = None
+		self.modules = modules
+		self.iconSet = iconSet
+	def fill(self,r,g,b,outline=0,alpha=None):
+		if(alpha == None):
+			self.cr.set_source_rgb(r,g,b)
+		else:
+			self.cr.set_source_rgba(r,g,b,alpha)
+		self.cr.rectangle(self.x1,self.y1,self.w,self.h)
+		if(outline):
+			self.cr.stroke()
+		else:
+			self.cr.fill()
+	def drawTextSomewhere(self,text,px1,py1,px2,py2):
+		if(text == None or text == ''):
+			return
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/poi_osm.py

@@ -1,0 +1,123 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""OSM POI handler for pyroute
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from poi_base import *
+from xml.sax import make_parser, handler
+import os
+import urllib
+
+class osmPoiModule(poiModule, handler.ContentHandler):
+	def __init__(self, modules):
+		poiModule.__init__(self, modules)
+		self.draw = False
+		self.loadPOIs("all", "amenity|shop=*")
+
+	def loadPOIs(self, name, search):
+		filename = os.path.join(os.path.dirname(__file__),
+														"data", "poi_%s.osm" % name)
+
+		url = "http://www.informationfreeway.org/api/0.5/node[%s][%s]" %(search,
+																																		 self.bbox())
+
+		if(not os.path.exists(filename)):
+			print "Downloading POIs from OSM"
+			urllib.urlretrieve(url, filename)
+		self.load(filename, os.path.join(os.path.dirname(__file__),
+														"Setup", "poi.txt"))
+
+	def bbox(self):
+		# TODO: based on location!
+		return "bbox=-6,48,2.5,61"
+
+	def load(self, filename, listfile):
+		self.filters = []
+		print "Loading POIs from %s" % listfile
+		f = open(listfile,"r")
+		try:
+			for line in f:
+				if(len(line) > 1):
+					text = line.rstrip()
+					name, filter = text.split('|')
+					group = poiGroup(name)
+					self.groups.append(group)
+					self.filters.append({'name':name,'filter':filter,'group':group})
+		finally:
+			f.close()
+
+		if(not os.path.exists(filename)):
+			print "Can't load %s"%filename
+			return
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/pyroute.py

@@ -1,0 +1,296 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""pyRoute, a routing program for OpenStreetMap-style data
+
+Usage:
+ pyroute.py [input OSM file] [start node] [end node]
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from xml.sax import make_parser, handler
+import cairo
+import math
+import sys
+
+class GetRoutes(handler.ContentHandler):
+	"""Parse an OSM file looking for routing information, and do routing with it"""
+	def __init__(self):
+		"""Initialise an OSM-file parser"""
+		self.routing = {}
+		self.nodes = {}
+		self.minLon = 180
+		self.minLat = 90
+		self.maxLon = -180
+		self.maxLat = -90
+	def startElement(self, name, attrs):
+		"""Handle XML elements"""
+		if name in('node','way','relation'):
+			if name == 'node':
+				"""Nodes need to be stored"""
+				id = int(attrs.get('id'))
+				lat = float(attrs.get('lat'))
+				lon = float(attrs.get('lon'))
+				self.nodes[id] = (lat,lon)
+				if lon < self.minLon:
+					self.minLon = lon
+				if lat < self.minLat:
+					self.minLat = lat
+				if lon > self.maxLon:
+					self.maxLon = lon
+				if lat > self.maxLat:
+					self.maxLat = lat
+			self.tags = {}
+			self.waynodes = []
+		elif name == 'nd':
+			"""Nodes within a way -- add them to a list"""
+			self.waynodes.append(int(attrs.get('ref')))
+		elif name == 'tag':
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/pyrouteMenu.py

@@ -1,0 +1,154 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Loads touchscreen menus from textfiles on disk
+
+Usage:
+	(library code for pyroute GUI, not for direct use)
+
+Format:
+	* One menu per textfile  (menuname.txt)
+	* One line per 'column'
+	* Line containing "-----" starts a new row
+		 (the first line should also contain one of these)
+	* 4 rows of 3 columns. all must be defined, even if blank
+	* Item is "name" or "name|event"
+		* name should be unique amongst all menus
+		* name is currently displayed as-is (TODO: translation table)
+		* "Up" is a special name that closes the menu
+			 * Typically the top/left item is always 'Up'
+		* event is a message to send when the menu item is pressed
+		* lines can be blank to represent no menu item in that position
+"""
+
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+import os
+import re
+
+def loadMenu(filename):
+	menu = {}
+	try:
+		file = open(filename, "r")
+		x = 0
+		y = -1
+		for line in file:
+			line = line.rstrip()
+			if(line == '-----'):
+				x = 0
+				y = y + 1
+				continue
+			try:
+				name,action = line.split('|', 2)
+			except ValueError:
+				name,action = (line,None)
+			#print "%d,%d: %s" % (x,y,action)
+			icon = name.lower()
+			icon = re.sub('\s+', '_', icon)
+			menu["%d,%d"%(x,y)] = {'name':name,'action':action,'icon':icon}
+			x = x + 1
+
+		file.close()
+	except IOError:
+		print "Can't open file %s" % filename
+	return menu
+
+def loadMenus(directory):
+	menus = {}
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/routeAsGpx.py

@@ -1,0 +1,69 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""routeAsOsm - routes within an OSM file, and generates a
+GPX file containing the result
+
+Usage:
+	routeAsGpx.py [input OSM file] [start node] [end node] [transport] [description]
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from route import *
+
+def routeToGpx(nodeList, osmData, description=""):
+	"""Format a route (as list of nodes) into a GPX file"""
+
+	output = ''
+	output = output + "<?xml version='1.0'?>\n";
+
+	output = output + "<gpx version='1.1' creator='pyroute' xmlns='http://www.topografix.com/GPX/1/1' xmlns:xsi='http://www.w3.org/2001/XMLSchema-instance' xsi:schemaLocation='http://www.topografix.com/GPX/1/1 http://www.topografix.com/GPX/1/1/gpx.xsd'>\n"
+
+	output = output + " <rte>\n"
+	output = output + "  <name>%s</name>\n" % description
+
+	count = 0;
+	for i in nodeList:
+		output = output + "   <rtept lat='%f' lon='%f'>\n" % ( \
+			osmData.nodes[i][0],
+			osmData.nodes[i][1])
+		output = output + "    <name>%d</name>\n" % count
+		output = output + "   </rtept>\n"
+		count = count + 1
+	output = output + " </rte>\n</gpx>\n"
+
+	return(output)
+
+if __name__ == "__main__":
+	try:
+		# Load data
+		data = LoadOsm(sys.argv[1])
+
+		# Do routing
+		router = Router(data)
+		result, route = router.doRoute(int(sys.argv[2]), int(sys.argv[3]), sys.argv[4])
+
+		# Display result
+		if result == 'success':
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/routeOrDirect.py

@@ -1,0 +1,65 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from route import Router
+
+class RouteOrDirect(Router):
+	def __init__(self, data):
+		Router.__init__(self,data)
+		self.route = {'valid':False}
+		self.mode = 'direct';
+	def setMode(self, mode):
+		self.mode = mode
+	def setStartNode(self,node):
+		self.route['startnode'] = node
+		self.route['startpos'] = self.data.nodes[node]
+	def setEndNode(self,node):
+		self.route['endnode'] = node
+		self.route['endpos'] = self.data.nodes[node]
+	def setStartLL(self,lat,lon,transport):
+		self.route['startnode'] = self.data.findNode(lat,lon,transport)
+		self.route['startpos'] = (lat,lon)
+		self.route['transport'] = transport
+	def setEndLL(self,lat,lon,transport):
+		self.route['endnode'] = self.data.findNode(lat,lon,transport)
+		self.route['endpos'] = (lat,lon)
+		self.route['transport'] = transport
+	def update(self):
+		if(self.mode == 'route'):
+			result, newroute = self.doRouteAsLL( \
+				self.route['startnode'],
+				self.route['endnode'],
+				self.route['transport'])
+			if result == 'success':
+				self.route['route'] = newroute
+				self.route['valid'] = True
+			else:
+				self.route['route'] = [self.route['startpos'],self.route['endpos']]
+				self.route['valid'] = True
+		else:
+			self.route['route'] = []
+			self.route['route'].append(self.route['startpos'])
+			self.route['route'].append(self.route['endpos'])
+			self.route['valid'] = True
+
+	def valid(self):
+		return(self.route['valid'])

### 2013-11-08 pyroute/applications/routing/pyroute-dev/tilenames.py

@@ -1,0 +1,104 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""Translates between lat/long and the slippy-map tile
+numbering scheme
+
+http://wiki.openstreetmap.org/index.php/Slippy_map_tilenames
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from math import *
+
+def numTiles(z):
+	return(pow(2,z))
+
+def sec(x):
+	return(1/cos(x))
+
+def latlon2relativeXY(lat,lon):
+	x = (lon + 180) / 360
+	y = (1 - log(tan(radians(lat)) + sec(radians(lat))) / pi) / 2
+	return(x,y)
+
+def latlon2xy(lat,lon,z):
+	n = numTiles(z)
+	x,y = latlon2relativeXY(lat,lon)
+	return(n*x, n*y)
+
+def tileXY(lat, lon, z):
+	x,y = latlon2xy(lat,lon,z)
+	return(int(x),int(y))
+
+def xy2latlon(x,y,z):
+	n = numTiles(z)
+	relY = y / n
+	lat = mercatorToLat(pi * (1 - 2 * relY))
+	lon = -180.0 + 360.0 * x / n
+	return(lat,lon)
+
+def latEdges(y,z):
+	n = numTiles(z)
+	unit = 1 / n
+	relY1 = y * unit
+	relY2 = relY1 + unit
+	lat1 = mercatorToLat(pi * (1 - 2 * relY1))
+	lat2 = mercatorToLat(pi * (1 - 2 * relY2))
+	return(lat1,lat2)
+
+def lonEdges(x,z):
+	n = numTiles(z)
+	unit = 360 / n
[…]

### 2013-11-08 pyroute/applications/routing/pyroute-dev/tracklog.py

@@ -1,0 +1,49 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from base import pyrouteModule
+from lib_gpx import lib_gpx
+import cairo
+import os
+
+class tracklog(pyrouteModule, lib_gpx):
+	""""""
+	def __init__(self, modules):
+		lib_gpx.__init__(self)
+		pyrouteModule.__init__(self, modules)
+		self.active = []
+		self.lines.append(self.active)
+		self.pointsSinceSave = 0
+
+	def addPoint(self,lat,lon):
+		self.active.append([lat,lon])
+		self.pointsSinceSave = self.pointsSinceSave + 1
+
+	def checkIfNeedsSaving(self, forceSave = False):
+		if(self.pointsSinceSave > 20 or forceSave):
+			self.save()
+
+	def save(self):
+		self.saveAs(os.path.join(os.path.dirname(__file__),
+														 "data","tracklogs.gpx"), "tracklogs")
+		self.pointsSinceSave = 0
+

### 2013-11-08 pyroute/applications/routing/pyroute-dev/util_binary.py

@@ -1,0 +1,47 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+"""
+
+__version__ = "$Rev$"[1:-2]
+__license__ = """This program is free software: you can redistribute it and/or modify
+it under the terms of the GNU General Public License as published by
+the Free Software Foundation, either version 3 of the License, or
+(at your option) any later version.
+
+This program is distributed in the hope that it will be useful,
+but WITHOUT ANY WARRANTY; without even the implied warranty of
+MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
+GNU General Public License for more details.
+
+You should have received a copy of the GNU General Public License
+along with this program. If not, see <http://www.gnu.org/licenses/>."""
+_debug = 0
+
+
+from struct import *
+
+def encodeLL(lat,lon):
+	pLat = (lat + 90.0) / 180.0
+	pLon = (lon + 180.0) / 360.0
+	iLat = encodeP(pLat)
+	iLon = encodeP(pLon)
+	return(pack("II", iLat, iLon))
+
+def encodeP(p):
+	i = int(p * 4294967296.0)
+	return(i)
+
+
+def decodeLL(data):
+	iLat,iLon = unpack("II", data)
+	pLat = decodeP(iLat)
+	pLon = decodeP(iLon)
+	lat = pLat * 180.0 - 90.0
+	lon = pLon * 360.0 - 180.0
+	return(lat,lon)
+
+def decodeP(i):
+	p = float(i) / 4294967296.0
+	return(p)

### 2013-11-08 pyroute/applications/routing/pyroute/poi_osm.py

@@ -1,0 +1,128 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+# OSM POI handler for pyroute
+#
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+from xml.sax import make_parser, handler
+from poi_base import *
+import os
+from xml.sax._exceptions import SAXParseException
+import urllib
+
+class osmPoiModule(poiModule, handler.ContentHandler):
+	def __init__(self, modules):
+		poiModule.__init__(self, modules)
+		self.draw = False
+		self.loadPOIs("all", "amenity|shop=*")
+		
+	def loadPOIs(self, name, search):
+		filename = os.path.join(os.path.dirname(__file__),
+								"data", "poi_%s.osm" % name)
+		
+		url = "http://www.informationfreeway.org/api/0.5/node[%s][%s]" %(search,
+																		self.bbox())
+		
+		if(not os.path.exists(filename)):
+			print "Downloading POIs from OSM"
+			urllib.urlretrieve(url, filename)
+		self.load(filename, os.path.join(os.path.dirname(__file__),
+														"Setup", "poi.txt"))
+
+	def bbox(self):
+		# TODO: based on location!
+		return "bbox=-6,48,2.5,61"
+	
+	def load(self, filename, listfile):
+		self.filters = []
+		print "Loading POIs from %s" % listfile
+		f = open(listfile,"r")
+		try:
+			for line in f:
+				if(len(line) > 1):
+					text = line.rstrip()
+					name, filter = text.split('|')
+					group = poiGroup(name)
+					self.groups.append(group)
+					self.filters.append({'name':name,'filter':filter,'group':group})
+		finally:
[…]

### 2013-11-08 pyroute/applications/routing/pyroute/tilenames.py

@@ -1,0 +1,91 @@
+#!/usr/bin/env python
+#-------------------------------------------------------
+# Translates between lat/long and the slippy-map tile
+# numbering scheme
+#
+# http://wiki.openstreetmap.org/index.php/Slippy_map_tilenames
+#
+# Written by Oliver White, 2007
+# This file is public-domain
+#-------------------------------------------------------
+from math import *
+
+def numTiles(z):
+  return(pow(2,z))
+
+def sec(x):
+  return(1/cos(x))
+
+def latlon2relativeXY(lat,lon):
+  x = (lon + 180) / 360
+  y = (1 - log(tan(radians(lat)) + sec(radians(lat))) / pi) / 2
+  return(x,y)
+
+def latlon2xy(lat,lon,z):
+  n = numTiles(z)
+  x,y = latlon2relativeXY(lat,lon)
+  return(n*x, n*y)
+
+def tileXY(lat, lon, z):
+  x,y = latlon2xy(lat,lon,z)
+  return(int(x),int(y))
+
+def xy2latlon(x,y,z):
+  n = numTiles(z)
+  relY = y / n
+  lat = mercatorToLat(pi * (1 - 2 * relY))
+  lon = -180.0 + 360.0 * x / n
+  return(lat,lon)
+
+def latEdges(y,z):
+  n = numTiles(z)
+  unit = 1 / n
+  relY1 = y * unit
+  relY2 = relY1 + unit
+  lat1 = mercatorToLat(pi * (1 - 2 * relY1))
+  lat2 = mercatorToLat(pi * (1 - 2 * relY2))
+  return(lat1,lat2)
+
+def lonEdges(x,z):
+  n = numTiles(z)
+  unit = 360 / n
+  lon1 = -180 + x * unit
+  lon2 = lon1 + unit
+  return(lon1,lon2)
+
+def tileEdges(x,y,z):
+  lat1,lat2 = latEdges(y,z)
+  lon1,lon2 = lonEdges(x,z)
+  return((lat2, lon1, lat1, lon2)) # S,W,N,E
+
+def mercatorToLat(mercatorY):
+  return(degrees(atan(sinh(mercatorY))))
+
+def tileSizePixels():
+  return(256)
+
+def tileLayerExt(layer):
+  if(layer in ('oam')):
+    return('jpg')
+  return('png')
+
+def tileLayerBase(layer):
+  layers = { \
[…]

### 2013-11-08 pyroute/applications/routing/pyroute/tiles.py

@@ -1,0 +1,160 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Tile image handler (download, cache, and display tiles)
+#
+# Usage:
+#   (library code for pyroute GUI, not for direct use)
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from base import pyrouteModule
+from tilenames import *
+import urllib
+import os
+import cairo
+from threading import Thread
+
+def downloadTile(x,y,z,layer,filename):
+  url = tileURL(x,y,z,layer)
+  print url
+  if(tileLayerExt(layer) != "png"):
+    base,ext = os.path.splitext(filename)
+    tempFilename = "%s.%s" % (base, tileLayerExt(layer))
+    urllib.urlretrieve(url, tempFilename)
+    sys = "convert %s %s" % (tempFilename, filename)
+    print "Running \"%s\"" % sys
+    os.system(sys)
+    os.unlink(tempFilename)
+  else:
+    urllib.urlretrieve(url, filename)
+
+class tileLoader(Thread):
+  """Downloads images in a separate thread"""
+  def __init__(self, x,y,z,layer,filename):
+    """Download a tile image"""
+    self.x = x
+    self.y = y
+    self.z = z
+    self.layer = layer
+    self.finished = 0
+    self.filename = filename
+    Thread.__init__(self)
+
+  def run(self):
+    downloadTile( \
+      self.x,
+      self.y,
+      self.z,
+      self.layer,
+      self.filename)
+
+    self.finished = 1
+
+class tileHandler(pyrouteModule):
+  """Loads and displays map tiles"""
+  def __init__(self, modules):
[…]

### 2013-11-08 pyroute/applications/routing/pyroutelib2/routeAsGpx.py

@@ -1,0 +1,87 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+# routeAsOsm - routes with OSM data, and generates a
+# GPX file containing the result
+#
+#------------------------------------------------------
+# Usage:
+#  routeAsGpx.py [lat1] [lon1] [lat2] [lon2] [transport]
+#------------------------------------------------------
+# Copyright 2007-2008, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+from route import *
+
+def routeToGpx(lat1,lon1,lat2,lon2, transport, description="", style="track"):
+  """Format a route (as list of nodes) into a GPX file"""
+  data = LoadOsm(transport)
+
+  node1 = data.findNode(lat1,lon1)
+  node2 = data.findNode(lat2,lon2)
+
+  router = Router(data)
+  result, route = router.doRoute(node1, node2)
+  if result != 'success':
+    return
+
+  output = ''
+  output = output + "<?xml version='1.0'?>\n";
+
+  output = output + "<gpx version='1.1' creator='pyroute' xmlns='http://www.topografix.com/GPX/1/1' xmlns:xsi='http://www.w3.org/2001/XMLSchema-instance' xsi:schemaLocation='http://www.topografix.com/GPX/1/1 http://www.topografix.com/GPX/1/1/gpx.xsd'>\n"
+
+  if(style == 'track'):
+    output = output + " <trk>\n"
+    output = output + "  <name>%s</name>\n" % description
+    output = output + "  <trkseg>\n"
+    count = 0;
+    for i in route:
+      node = data.rnodes[i]
+      output = output + "   <trkpt lat='%f' lon='%f'>\n" % ( \
+        node[0],
+        node[1])
+      output = output + "   </trkpt>\n"
+      count = count + 1
[…]

### 2013-11-08 pyroute/applications/routing/yours/branches/version-1.0-via/www/routing.js

@@ -1,0 +1,1390 @@
+// Waypoint class for storing all waypoint related data (marker, route to
+// next way point)
+function Waypoint()
+{
+	this.set_prev= function(prev)
+	{
+		this.prev= prev;
+
+		this.style= style_mid;
+		if (this.prev == undefined)
+			this.style= style_from;
+		else if (this.next == undefined)
+			this.style= style_to;
+	}
+
+	this.set_next= function(next)
+	{
+		this.next= next;
+
+		this.style= style_mid;
+		if (this.prev == undefined)
+			this.style= style_from;
+		else if (this.next == undefined)
+			this.style= style_to;
+	}
+
+	this.set_position= function(lonlat)
+	{
+		this.clear_position();
+
+		var marker_url= 'markers/marker-yellow.png';
+		if (this.prev == undefined)
+			marker_url= 'markers/marker-green.png';
+		if (this.next == undefined)
+			marker_url= 'markers/marker-red.png';
+		var size = new OpenLayers.Size(21,25);
+		var offset = new OpenLayers.Pixel(-(size.w/2), -size.h);
+
+		var icon = new OpenLayers.Icon(marker_url,
+			size,offset);
+		this.marker = new OpenLayers.Marker(lonlat.clone(), icon);
+		markers.addMarker(this.marker);
+
+		if (this.pos_el != undefined)
+		{
+			map_ll= lonlat.clone();
+			map_ll.transform(map.projection,
+				map.displayProjection);
+
+			precision= 6;
+			str= map_ll.lat.toFixed(precision) + ', ' +
+				map_ll.lon.toFixed(precision);
+			this.pos_el.innerHTML= str;
+		}
+	}
+	this.clear_position= function()
+	{
+		if (this.marker != undefined)
+		{
+			markers.removeMarker(this.marker);
+			this.marker.destroy();
+			this.marker= undefined;
+
+			this.remove_route();
+			if (this.prev != undefined)
+				this.prev.remove_route();
+			if (this.pos_el != undefined)
+				this.pos_el.innerHTML= "";
+		}
+	}
+	this.set_route= function(routelist)
+	{
+		if (this.route != undefined)
+		{
+			alert('Waypoint.set_route: should update route');
+			return;
+		}
+		this.route= routelist;
+	}
+	this.set_distance= function(distance)
+	{
+		this.distance= parseFloat(distance);
+	}
+	this.remove_route= function()
+	{
+		if (this.route == undefined)
+			return;
[…]

### 2013-11-08 pyroute/applications/routing/yours/branches/version-1.1/www/routing.js

@@ -1,0 +1,925 @@
+var lon = 5;
+var lat = 40;
+var zoom = 5;
+var map, layer, markers, routelayer;
+var markerFrom, markerTo;
+var mode, position;
+var permalink, WindowLocation;
+
+/*
+xmlhttp['object'] = The AJAX JavaScript object that does all the work
+xmlhttp['what'] = Indicates what kind of request we're performing (e.g. NameFinder 'to' query or Gosmore 'route' query)
+xmlhttp['url'] = The URL to query
+*/
+var xmlhttp = new Array();
+
+function init(){
+	WindowLocation = String(window.location);
+
+	OpenLayers.Feature.Vector.style['default']['strokeWidth'] = '2';
+	OpenLayers.Feature.Vector.style['default']['fillColor'] = '#0000FF';
+	OpenLayers.Feature.Vector.style['default']['strokeColor'] = '#0000FF';
+	
+	// Map definition based on http://wiki.openstreetmap.org/index.php/OpenLayers_Simple_Example
+	map = new OpenLayers.Map ("map", {
+                controls:[
+                    new OpenLayers.Control.Navigation(),
+                    new OpenLayers.Control.PanZoomBar(),
+                    new OpenLayers.Control.LayerSwitcher(),
+                    new OpenLayers.Control.Attribution()
+				],
+				eventListeners: {
+			        //"moveend": mapEvent,
+			        //"zoomend": mapEvent,
+			        //"changelayer": mapLayerChanged,
+			        "changebaselayer": onChangeBaseLayer
+					},
+                maxExtent: new OpenLayers.Bounds(-20037508.34,-20037508.34,20037508.34,20037508.34),
+                maxResolution: 156543.0399,
+                numZoomLevels: 20,
+                units: 'm',
+                projection: new OpenLayers.Projection("EPSG:900913"),
+                displayProjection: new OpenLayers.Projection("EPSG:4326")
+            } );
+	
+	//map.events.register("changebaselayer", map, onChangeBaseLayer(this));
+    		
+	layerMapnik = new OpenLayers.Layer.OSM.Mapnik("Mapnik");
+	layerCycle = new OpenLayers.Layer.OSM.CycleMap("Cycle Map", {
+					 displayOutsideMaxExtent: true,
+					 wrapDateLine: true
+					 });
+					 
+	layerCycleNetworks = new OpenLayers.Layer.OSM.CycleMap("Cycle Networks", {
+					 displayOutsideMaxExtent: true,
+					 wrapDateLine: true
[…]

### 2013-11-08 pyroute/applications/routing/yours/trunk/www/api/dev/yours.js

@@ -1,0 +1,1324 @@
+/* Copyright (c) 2009, L. IJsselstein and others
+  Yournavigation.org All rights reserved.
+ */
+
+if (document.location.pathname.charAt(document.location.pathname.length-1) == "/") {
+	var apiUrl = document.location.protocol + "//" + document.location.hostname + document.location.pathname + "api/dev/";
+} else {
+	var apiUrl = document.location.protocol + "//" + document.location.hostname + document.location.pathname + "/api/dev/";
+}
+var namefinderUrl = "transport.php?url=http://gazetteer.openstreetmap.org/namefinder/search.xml&";
+var nominatimUrl = "http://nominatim.openstreetmap.org/";
+var reverseNamefinderUrl = "transport.php?url=http://dev.openstreetmap.nl/~rullzer/rev_namefinder/&";
+
+/*
+	Yours NameSpace with Classes and functions
+	@requires OpenLayers
+	@requires jQuery
+ */
+var routeCache = {};
+
+// Create OpenLayers Control Click handler
+OpenLayers.Control.Click = OpenLayers.Class(OpenLayers.Control, {
+		defaultHandlerOptions: {
+			'single': true,
+			'double': false,
+			'pixelTolerance': 0,
+			'stopSingle': false,
+			'stopDouble': false
+		},
+		/*
+		 * Initialize is called when the Click control is activated
+		 * It sets the behavior of a click on the map
+		 */
+		initialize: function() {
+			this.handlerOptions = OpenLayers.Util.extend(
+				{}, this.defaultHandlerOptions
+				);
+			OpenLayers.Control.prototype.initialize.apply(
+				this, arguments
+				);
+			this.handler = new OpenLayers.Handler.Click(
+				this, {
+					'click': this.trigger
+				}, this.handlerOptions
+				);
+		},
+
+		/*
+		 * How OpenLayers should react to a user click on the map.
+		 * Get the LonLat from the user click and position
+		 */
+		trigger: function(e) {
+			var location = this.map.getLonLatFromViewPortPx(e.xy);
+			this.route.updateWaypoint("selected", location);
+		}
+	}
+);
+
+/**
+*
+*  URL encode / decode
+*  http://www.webtoolkit.info/
+*
+**/
+
+var Url = {
+
+    // public method for url encoding
+    encode : function (string) {
+        return escape(this._utf8_encode(string));
+    },
+
+    // public method for url decoding
+    decode : function (string) {
+        return this._utf8_decode(unescape(string));
+    },
+
[…]

### 2013-11-08 pyroute/applications/routing/yours/trunk/www/jquery/jquery-ui.js

@@ -1,0 +1,1 @@
+link jquery-ui-1.8.custom.min.js

### 2013-11-08 pyroute/applications/routing/yours/trunk/www/jquery/jquery.js

@@ -1,0 +1,1 @@
+link jquery-1.6.1.min.js

### 2013-11-14 paper.tex
Reorganized the pyroute files and created a preliminary grower.
The grower has a few issues at the moment. Most problematically, it does not
take input for parameters. Additionally, it needs some work to adjust the
parameters to proper units.

@@
 \begin{enumerate}
-\item Check if the optimal solution would require that we move around the loop
-  again. This will happen if
-  \[d_i+\sqrt{(x_0.x-x_i.x)^2+(x_0.y-x_i.y)^2} > d.\]
-  In this case, we set $x_j = x_0$, and stop searching.
-\item \emph{NEEDS MORE WORK}
+\item Calculate \eqref{eq:xjx} and \eqref{eq:xjy} for all $\{ d_j |
+  0 \leq d_j \leq d - d_i \mbox{ and } d_j = n(0.01d), n \in \mathbb{Z} \}$.
+\item Calculate \eqref{eq:dists} for each of these values.
+\item If the minimal difference between the $d_j$ calculated in \eqref{eq:dists}
+  and the $d_j$ provided in \eqref{eq:xjx} and \eqref{eq:xjy} is less than
+  10\% of $d$, then use the $x_j$ calculated there.
+\item Otherwise, use $x_0$ as $x_j$.
 \end{enumerate}

### 2013-11-14 grower/grower.py

@@ -1,0 +1,197 @@
+#!/usr/bin/python
+#
+################################################################################
+#
+# Cycles for cycling using OSM data and extending pyroutelib2.
+#
+################################################################################
+#
+# Copyright 2013, Forest Trimble
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#
+################################################################################
+
+import sys
+import math
+import random
+
+sys.path.append("../pyroute")
+sys.path.append("../pyroute/pyroutelib2")
+from loadOsm import *
+from route import *
+
+class Grower:
+  def __init__(self, data):
+    self.data = data
+
+  def distance(self,n1,n2):
+    """Calculate distance between two nodes"""
+    lat1 = self.data.nodes[n1][0]
+    lon1 = self.data.nodes[n1][1]
+    lat2 = self.data.nodes[n2][0]
+    lon2 = self.data.nodes[n2][1]
+    return self.coordDist(lat1,lon1,lat2,lon2)
+
+  def coordDist(self, lat1, lon1, lat2, lon2):
+    # TODO: projection issues
+    dlat = lat2 - lat1
+    dlon = lon2 - lon1
+    dist2 = dlat * dlat + dlon * dlon
+    dist = math.sqrt(dist2)
+    return(dist)
+
+  def eleDist(self, node1, node2):
+    # TODO implement this
+    return 0
+
+  NORTH = math.pi/2
+  SOUTH = -math.pi/2
+  WEST = math.pi
+  EAST = 0
+
+  def getWeight(self, fromNode, toNode, theta, initWeight = 1):
+    tau = self.getAngleFromCoords(self.data.nodes[fromNode][0],
+                                  self.data.nodes[fromNode][1],
+                                  self.data.nodes[toNode][0],
+                                  self.data.nodes[toNode][1])
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/base.py

@@ -1,47 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Projection code (lat/long to screen conversions)
-
-Usage:
-	* Derive all pyroute modules fom this class
-	* Put "pyrouteModule.__init__(self,modules)" in your init function
-	* Instantiate using modules.append(yourmodule(modules))
-		 where "modules" is the list of all pyroute modules
-
-Features:
-	* Get and set data from the global table
-	* Send messages or trigger events
-	* Access other modules (using "self.m['modulename']")
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-class pyrouteModule:
-	def __init__(self, modules):
-		self.m = modules
-	def get(self, name, default=None):
-		return(self.m['data'].getData(name, default))
-	def set(self, name, value):
-		return(self.m['data'].setData(name, value))
-	def action(self, message):
-		self.m['events'].handleEvent(message)
-	def ownPos(self):
-		return(self.m['position'].get())
-	# Meta-info
-	def getStatus(self):
-		return("")

### 2013-11-14 pyroute/applications/routing/pyroute-dev/colorsys.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-"""Conversion functions between RGB and other color systems.
-
-This modules provides two functions for each color system ABC:
-
-	rgb_to_abc(r, g, b) --> a, b, c
-	abc_to_rgb(a, b, c) --> r, g, b
-
-All inputs and outputs are triples of floats in the range [0.0...1.0]
-(with the exception of I and Q, which covers a slightly larger range).
-Inputs outside the valid range may cause exceptions or invalid outputs.
-
-Supported color systems:
-RGB: Red, Green, Blue components
-YIQ: Luminance, Chrominance (used by composite video signals)
-HLS: Hue, Luminance, Saturation
-HSV: Hue, Saturation, Value
-"""
-
-# References:
-# http://en.wikipedia.org/wiki/YIQ
-# http://en.wikipedia.org/wiki/HLS_color_space
-# http://en.wikipedia.org/wiki/HSV_color_space
-
-__all__ = ["rgb_to_yiq","yiq_to_rgb","rgb_to_hls","hls_to_rgb",
-			 "rgb_to_hsv","hsv_to_rgb"]
-
-# Some floating point constants
-
-ONE_THIRD = 1.0/3.0
-ONE_SIXTH = 1.0/6.0
-TWO_THIRD = 2.0/3.0
-
-# YIQ: used by composite video signals (linear combinations of RGB)
-# Y: perceived grey level (0.0 == black, 1.0 == white)
-# I, Q: color components
-
-def rgb_to_yiq(r, g, b):
-	y = 0.30*r + 0.59*g + 0.11*b
-	i = 0.60*r - 0.28*g - 0.32*b
-	q = 0.21*r - 0.52*g + 0.31*b
-	return (y, i, q)
-
-def yiq_to_rgb(y, i, q):
-	r = y + 0.948262*i + 0.624013*q
-	g = y - 0.276066*i - 0.639810*q
-	b = y - 1.105450*i + 1.729860*q
-	if r < 0.0: r = 0.0
-	if g < 0.0: g = 0.0
-	if b < 0.0: b = 0.0
-	if r > 1.0: r = 1.0
-	if g > 1.0: g = 1.0
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/feedparser.py

@@ -1,2859 +1,0 @@
-﻿#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-"""Universal feed parser
-
-Handles RSS 0.9x, RSS 1.0, RSS 2.0, CDF, Atom 0.3, and Atom 1.0 feeds
-
-Visit http://feedparser.org/ for the latest version
-Visit http://feedparser.org/docs/ for the latest documentation
-
-Required: Python 2.1 or later
-Recommended: Python 2.3 or later
-Recommended: CJKCodecs and iconv_codec <http://cjkpython.i18n.org/>
-"""
-
-__version__ = "4.1"# + "$Revision$"[11:15] + "-cvs"
-__license__ = """Copyright (c) 2002-2006, Mark Pilgrim, All rights reserved.
-
-Redistribution and use in source and binary forms, with or without modification,
-are permitted provided that the following conditions are met:
-
-* Redistributions of source code must retain the above copyright notice,
-  this list of conditions and the following disclaimer.
-* Redistributions in binary form must reproduce the above copyright notice,
-  this list of conditions and the following disclaimer in the documentation
-  and/or other materials provided with the distribution.
-
-THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS 'AS IS'
-AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
-IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
-ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE
-LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
-CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
-SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
-INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
-CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
-ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/geoPosition.py

@@ -1,115 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""report "current position" (currently accepts replayed GPX
-files from follow.py)
-
-Usage:
-	pos = geoPosition(filename_of_latlong_file)
-	lat,lon = pos.get()
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from time import sleep
-import os
-import re
-import socket
-import sys
-
-class geoPosition:
-	def __init__(self):
-		self.mode = "none"
-		try:
-			self.s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
-			self.s.connect(("127.0.0.1", 2947))
-			self.mode = "socket"
-		except socket.error:
-			print "No GPSD detected, position information will not be available"
-			pass # leave mode at "none"
-
-		self.filename = os.path.join(os.path.dirname(__file__), "pos.txt")
-		if(os.path.exists(self.filename)):
-			self.mode = "file"
-			print "Using %s as position reference" % self.filename
-
-		self.filename = os.path.join(os.path.dirname(__file__), "init_pos.txt")
-		if(os.path.exists(self.filename)):
-			self.mode = "initfile"
-			print "Using %s as initial position reference" % self.filename
-
-	def get(self):
-		try:
-				function = getattr(self, 'get_%s' % self.mode)
-		except AttributeError:
-				return({'valid':False,'message':"function for %s not defined" % self.mode})
-		return(function())
-
-	def get_none(self):
-		return({'valid':False,'message':"no gps"})
-
-	def socket_cmd(self, cmd):
-		self.s.send("%s\r\n" % cmd)
-		return self.s.recv(8192)
-
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/geometry.py

@@ -1,91 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Handles geometry on the earth's surface (e.g. bearing/distance)
-
-Usage:
-	(library code)
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from math import *
-from time import clock
-
-def bearing(a,b):
-	dlat = radians(b[0] - a[0])
-	dlon = radians(b[1] - a[1])
-
-	dlon = dlon * cos(radians(a[0]))
-
-	return(degrees(atan2(dlon, dlat)))
-
-def distance(a,b, haversine=False):
-	if(haversine):
-		return(distance_haversine(a,b))
-	lat1 = radians(a[0])
-	lon1 = radians(a[1])
-	lat2 = radians(b[0])
-	lon2 = radians(b[1])
-	d = acos(sin(lat1)*sin(lat2) + cos(lat1)*cos(lat2) * cos(lon2-lon1)) * 6371;
-	return(d)
-
-
-def distance_haversine(a,b):
-	dlat = radians(b[0] - a[0])
-	dlon = radians(b[1] - a[1])
-	a1 = sin(0.5 * dlat)
-	a2a = cos(radians(a[0]))
-	a2b = cos(radians(b[0]))
-	a3 = sin(0.5 * dlon)
-
-	a = a1*a1 + a2a*a2b * a3*a3
-	c = 2 * atan2(sqrt(a), sqrt(1-a))
-	d = 6371 * c
-	return(d)
-
-def compassPoint(x):
-	points = ('N','NNE','NE','ENE','E','ESE','SE','SSE','S','SSW','SW','WSW','W','WNW','NW','NNW')
-	part = 360.0 / len(points)
-	x = x + 0.5 * part
-	while(x < 0):
-		x = x + 360
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/lib_gpx.py

@@ -1,85 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Library for handling GPX files
-
-Usage:
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from xml.sax import make_parser, handler
-import cairo
-import os
-
-class lib_gpx(handler.ContentHandler):
-	""""""
-	def __init__(self):
-		self.lines = []
-
-	def draw(self,cr,proj):
-		cr.set_line_cap(cairo.LINE_CAP_ROUND)
-		cr.set_source_rgb(0.7,0.7,0)
-		cr.set_line_width(5)
-
-		for l in self.lines:
-			first = 1
-			for p in l:
-				x,y = proj.ll2xy(p[0], p[1])
-				if(first):
-					cr.move_to(x,y)
-					first = 0
-				else:
-					cr.line_to(x,y)
-			cr.stroke()
-
-	def saveAs(self,filename, title="untitled"):
-		file = open(filename,"w")
-		file.write("<?xml version=\"1.0\"?>\n")
-		file.write('<gpx>\n')
-		file.write('<trk>\n')
-		file.write('<name>%s</name>\n' % title)
-		for l in self.lines:
-			file.write('<trkseg>\n')
-			for p in l:
-				file.write('<trkpt lat="%f" lon="%f"/>\n'%(p[0], p[1]))
-			file.write('</trkseg>\n')
-		file.write('</trk>\n')
-		file.write('</gpx>\n')
-
-		file.close()
-
-	def load(self, filename):
-		if(not os.path.exists(filename)):
-			print "No such tracklog \"%s\"" % filename
-			return
-		self.inField = False
-		parser = make_parser()
-		parser.setContentHandler(self)
-		parser.parse(filename)
-
-	def startElement(self, name, attrs):
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/listable.py

@@ -1,55 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Interface for things which can be listed
-
-Usage:
-	(base-class for pyroute GUI libraries)
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-class listable:
-	"""Base-class (interface) for anything that can be listed in a menu"""
-	def numItems(self):
-		"""Return how many items are available"""
-		return(0)
-
-	def getItemText(self,n):
-		"""Return the label for any item number"""
-		return("-")
-
-	def getItemStatus(self,n):
-		"""Return current status for any item number"""
-		return("-")
-
-	def isLocation(self,n):
-		"""Return true if the item represents a location"""
-		return(False)
-
-	def getItemLatLon(self,n):
-		"""If the item represents a location, return it's position"""
-		return(0,0)
-
-	def getItemClickable(self,n):
-		"""If not a location, return true if the item should have a button to click on"""
-		return(False)
-
-	def getItemAction(self,n):
-		"""If the item isn't a location, return what happens if it's selected"""
-		return("")
-

### 2013-11-14 pyroute/applications/routing/pyroute-dev/overlay.py

@@ -1,457 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from base import pyrouteModule
-from colorsys import hsv_to_rgb
-from menuIcons import menuIcons
-from overlayArea import overlayArea
-from pyrouteMenu import *
-import cairo
-import geometry
-import os
-
-class guiOverlay(pyrouteModule):
-	def __init__(self, modules):
-		pyrouteModule.__init__(self, modules)
-		self.modules = modules
-		self.icons = menuIcons()
-		self.menus = loadMenus(os.path.join(os.path.dirname(__file__), 'Menus'))
-		self.dragbar = None
-		self.dragpos = 0
-
-	def fullscreen(self):
-		"""Asks if the menu is fullscreen -- if it is, then the
-		map doesn't need to be drawn underneath"""
-		return(self.get('menu'))
-
-	def handleDrag(self,dx,dy,startX,startY):
-		if(self.dragbar):
-			if(self.dragbar.contains(startX,startY)):
-				scale = -20.0 / float(self.rect.h)
-				self.dragpos = self.dragpos + dy * scale
-				if(self.dragpos < 0):
-					self.dragpos = 0
-				#print "Dragging %1.2f (by %1.2f * %1.2f)" % (self.dragpos, dy,scale)
-				return(True)
-		return(False)
-
-	def handleClick(self,x,y):
-		"""return 1 if click was handled"""
-		for cell in self.clickable:
-			if(cell.contains(x,y)):
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/overlayArea.py

@@ -1,159 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Graphics library for drawing pyroute GUI menus
-
-Usage:
-	(library code for pyroute GUI)
-
-Features:
-	Start by initialising a 'rectangle' that covers a certain bit of screen
-	Then you can
-		* Draw an icon there
-		* Draw text in the rectangle
-		* Make it clickable (so that it triggers an event when clicked)
-		* Split it into smaller rectangles (to do complex GUI layouts)
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-import cairo
-import os
-
-class overlayArea:
-	def __init__(self,cr,x,y,dx,dy,modules,iconSet):
-		self.cr = cr
-		self.x1 = x;
-		self.y1 = y;
-		self.x2 = x + dx;
-		self.y2 = y + dy;
-		self.w = dx
-		self.h = dy
-		self.cx = x + 0.5 * dx
-		self.cy = y + 0.5 * dy
-		self.event = None
-		self.modules = modules
-		self.iconSet = iconSet
-	def fill(self,r,g,b,outline=0,alpha=None):
-		if(alpha == None):
-			self.cr.set_source_rgb(r,g,b)
-		else:
-			self.cr.set_source_rgba(r,g,b,alpha)
-		self.cr.rectangle(self.x1,self.y1,self.w,self.h)
-		if(outline):
-			self.cr.stroke()
-		else:
-			self.cr.fill()
-	def drawTextSomewhere(self,text,px1,py1,px2,py2):
-		if(text == None or text == ''):
-			return
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/poi_geonames.py

@@ -1,66 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from poi_base import *
-from xml.sax import make_parser, handler
-import feedparser
-
-class geonamesParser(handler.ContentHandler):
-	def __init__(self, filename):
-		self.entries = []
-		parser = make_parser()
-		parser.setContentHandler(self)
-		parser.parse(filename)
-	def startElement(self, name, attrs):
-		if(name == "entry"):
-			self.entry = {}
-		self.text = ''
-	def characters(self, text):
-		self.text = self.text + text
-	def endElement(self, name):
-		if(name in ('title')):
-			self.entry[name] = self.text
-		if(name in ('lat','lng')):
-			self.entry[name] = float(self.text)
-		if(name == "entry"):
-			self.entries.append(self.entry)
-
-class geonames(poiModule):
-		def __init__(self, modules):
-				poiModule.__init__(self, modules)
-				g = geonamesParser("data/wiki.xml")
-				self.add("Wikipedia entries",g)
-
-		def add(self, name, parser):
-				group = poiGroup(name)
-				count = 0
-				for item in parser.entries:
-						x = poi(item['lat'], item['lng'])
-						x.title = item['title']
-						group.items.append(x)
-						count = count + 1
-				print "Added %d items from %s" % (count, name)
-
-				self.groups.append(group)
-
-if __name__ == "__main__":
-		g = geonamesParser("data/wiki.xml")

### 2013-11-14 pyroute/applications/routing/pyroute-dev/projection.py

@@ -1,155 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Projection code (lat/long to screen conversions)
-
-Usage:
-	(library code for pyroute GUI, not for direct use)
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from tilenames import *
-
-class Projection:
-	def __init__(self):
-		self.xyValid = False
-		self.llValid = False
-		self.needsEdgeFind = False
-
-		# Scale is the number of display pixels per projected unit
-		self.scale = tileSizePixels()
-
-	def isValid(self):
-		"""Test if the module contains all the information needed to do conversions"""
-		return(self.xyValid and self.llValid)
-
-	def setView(self,x,y,w,h):
-		"""Setup the display"""
-		self.w = w
-		self.h = h
-		self.xc = x + self.w
-		self.yc = y + self.h
-		self.xyValid = True
-		if(self.needsEdgeFind):
-			self.findEdges()
-
-	def recentre(self,lat,lon,zoom = None):
-		"""Move the projection to a particular geographic location
-		(with optional zoom level)"""
-		self.lat = lat
-		self.lon = lon
-		if(zoom != None):
-			self.implementNewZoom(zoom)
-			# note: implementNewZoom calls findEdges, hence the else: statement
-		else:
-			self.findEdges()
-		self.llValid = True
-
-	def setZoom(self, value, isAdjustment=False):
-		"""Change the zoom level, keeping same map centre
-		if isAdjustment is true, then value is relative to current zoom
-		otherwise it's an absolute value"""
-		if(isAdjustment):
-			# TODO: maybe we don't want all zoom levels?
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/pyroute.py

@@ -1,296 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""pyRoute, a routing program for OpenStreetMap-style data
-
-Usage:
- pyroute.py [input OSM file] [start node] [end node]
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from xml.sax import make_parser, handler
-import cairo
-import math
-import sys
-
-class GetRoutes(handler.ContentHandler):
-	"""Parse an OSM file looking for routing information, and do routing with it"""
-	def __init__(self):
-		"""Initialise an OSM-file parser"""
-		self.routing = {}
-		self.nodes = {}
-		self.minLon = 180
-		self.minLat = 90
-		self.maxLon = -180
-		self.maxLat = -90
-	def startElement(self, name, attrs):
-		"""Handle XML elements"""
-		if name in('node','way','relation'):
-			if name == 'node':
-				"""Nodes need to be stored"""
-				id = int(attrs.get('id'))
-				lat = float(attrs.get('lat'))
-				lon = float(attrs.get('lon'))
-				self.nodes[id] = (lat,lon)
-				if lon < self.minLon:
-					self.minLon = lon
-				if lat < self.minLat:
-					self.minLat = lat
-				if lon > self.maxLon:
-					self.maxLon = lon
-				if lat > self.maxLat:
-					self.maxLat = lat
-			self.tags = {}
-			self.waynodes = []
-		elif name == 'nd':
-			"""Nodes within a way -- add them to a list"""
-			self.waynodes.append(int(attrs.get('ref')))
-		elif name == 'tag':
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/route.py

@@ -1,145 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Routing for OSM data
-
-Usage as library:
-	router = Router(LoadOsmObject)
-	result, route = router.doRoute(node1, node2, transport)
-
-Usage from command-line:
-	route.py filename.osm node1 node2 transport
-
-(where transport is cycle, foot, car, etc...)
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from loadOsm import *
-import math
-import sys
-
-class Router:
-	def __init__(self, data):
-		self.data = data
-	def distance(self,n1,n2):
-		"""Calculate distance between two nodes"""
-		lat1 = self.data.nodes[n1][0]
-		lon1 = self.data.nodes[n1][1]
-		lat2 = self.data.nodes[n2][0]
-		lon2 = self.data.nodes[n2][1]
-		# TODO: projection issues
-		dlat = lat2 - lat1
-		dlon = lon2 - lon1
-		dist2 = dlat * dlat + dlon * dlon
-		return(math.sqrt(dist2))
-	def doRouteAsLL(self,start,end,transport):
-		result, nodes = self.doRoute(start,end,transport)
-		if(result != 'success'):
-			return(result,[])
-		pos = []
-		for node in nodes:
-			lat,lon = self.data.nodes[node]
-			pos.append((lat,lon))
-		return(result,pos)
-	def doRoute(self,start,end,transport):
-		"""Do the routing"""
-		self.searchEnd = end
-		closed = [start]
-		self.queue = []
-
-		# Start by queueing all outbound links from the start node
-		blankQueueItem = {'end':-1,'distance':0,'nodes':str(start)}
-		try:
-			for i, weight in self.data.routing[transport][start].items():
-				self.addToQueue(start,i, blankQueueItem, weight)
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/routeAsGpx.py

@@ -1,69 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""routeAsOsm - routes within an OSM file, and generates a
-GPX file containing the result
-
-Usage:
-	routeAsGpx.py [input OSM file] [start node] [end node] [transport] [description]
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from route import *
-
-def routeToGpx(nodeList, osmData, description=""):
-	"""Format a route (as list of nodes) into a GPX file"""
-
-	output = ''
-	output = output + "<?xml version='1.0'?>\n";
-
-	output = output + "<gpx version='1.1' creator='pyroute' xmlns='http://www.topografix.com/GPX/1/1' xmlns:xsi='http://www.w3.org/2001/XMLSchema-instance' xsi:schemaLocation='http://www.topografix.com/GPX/1/1 http://www.topografix.com/GPX/1/1/gpx.xsd'>\n"
-
-	output = output + " <rte>\n"
-	output = output + "  <name>%s</name>\n" % description
-
-	count = 0;
-	for i in nodeList:
-		output = output + "   <rtept lat='%f' lon='%f'>\n" % ( \
-			osmData.nodes[i][0],
-			osmData.nodes[i][1])
-		output = output + "    <name>%d</name>\n" % count
-		output = output + "   </rtept>\n"
-		count = count + 1
-	output = output + " </rte>\n</gpx>\n"
-
-	return(output)
-
-if __name__ == "__main__":
-	try:
-		# Load data
-		data = LoadOsm(sys.argv[1])
-
-		# Do routing
-		router = Router(data)
-		result, route = router.doRoute(int(sys.argv[2]), int(sys.argv[3]), sys.argv[4])
-
-		# Display result
-		if result == 'success':
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/routeAsOsm.py

@@ -1,71 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""routeAsOsm - routes within an OSM file, and generates an
-OSM file containing the result
-
-Usage:
-	routeAsOsm.py [input OSM file] [start node] [end node] [transport] [description]
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from route import *
-
-def routeToOsm(nodeList, osmData, description="", transport=""):
-	"""Format a route (as list of nodes) into an OSM file"""
-	output = ''
-	output = output + "<?xml version='1.0' encoding='UTF-8'?>\n";
-	output = output + "<osm version='0.5' generator='pyroute'>\n";
-
-	for i in nodeList:
-		output = output + " <node id='%d' lat='%f' lon='%f' />\n" % ( \
-			i,
-			osmData.nodes[i][0],
-			osmData.nodes[i][1])
-
-	output = output + " <way id='1'>\n"
-	for i in nodeList:
-		output = output + "	<nd ref='%d' />\n" % i
-
-	output = output + "  <tag k='route_display' v='yes' />\n"
-	output = output + "  <tag k='name' v='%s' />\n" % description
-	output = output + "  <tag k='transport' v='%s' />\n" % transport
-	output = output + " </way>\n"
-	output = output + "</osm>"
-
-	return(output)
-
-
-if __name__ == "__main__":
-	try:
-		# Load data
-		data = LoadOsm(sys.argv[1])
-
-		# Do routing
-		router = Router(data)
-		result, route = router.doRoute(int(sys.argv[2]), int(sys.argv[3]), sys.argv[4])
-
-		# Display result
-		if result == 'success':
-			print routeToOsm(route, data, sys.argv[5], sys.argv[4])
-		else:
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/sketch.py

@@ -1,49 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Sketch-on-map module for pyroute
-
-Usage:
-"""
-
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from base import pyrouteModule
-from lib_gpx import lib_gpx
-import cairo
-import os
-
-class sketching(pyrouteModule, lib_gpx):
-	""""""
-	def __init__(self, modules):
-		lib_gpx.__init__(self)
-		pyrouteModule.__init__(self, modules)
-
-	def startStroke(self,x,y):
-		lat,lon = self.m['projection'].xy2ll(x,y)
-		self.latest = [(lat,lon)]
-		self.lines.append(self.latest)
-
-	def moveTo(self,x,y):
-		lat,lon = self.m['projection'].xy2ll(x,y)
-		self.latest.append((lat,lon))
-		self.set("needRedraw", 1)
-
-	def save(self):
-			self.saveAs("data/sketches/latest.gpx")
-

### 2013-11-14 pyroute/applications/routing/pyroute-dev/tilenames.py

@@ -1,104 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""Translates between lat/long and the slippy-map tile
-numbering scheme
-
-http://wiki.openstreetmap.org/index.php/Slippy_map_tilenames
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from math import *
-
-def numTiles(z):
-	return(pow(2,z))
-
-def sec(x):
-	return(1/cos(x))
-
-def latlon2relativeXY(lat,lon):
-	x = (lon + 180) / 360
-	y = (1 - log(tan(radians(lat)) + sec(radians(lat))) / pi) / 2
-	return(x,y)
-
-def latlon2xy(lat,lon,z):
-	n = numTiles(z)
-	x,y = latlon2relativeXY(lat,lon)
-	return(n*x, n*y)
-
-def tileXY(lat, lon, z):
-	x,y = latlon2xy(lat,lon,z)
-	return(int(x),int(y))
-
-def xy2latlon(x,y,z):
-	n = numTiles(z)
-	relY = y / n
-	lat = mercatorToLat(pi * (1 - 2 * relY))
-	lon = -180.0 + 360.0 * x / n
-	return(lat,lon)
-
-def latEdges(y,z):
-	n = numTiles(z)
-	unit = 1 / n
-	relY1 = y * unit
-	relY2 = relY1 + unit
-	lat1 = mercatorToLat(pi * (1 - 2 * relY1))
-	lat2 = mercatorToLat(pi * (1 - 2 * relY2))
-	return(lat1,lat2)
-
-def lonEdges(x,z):
-	n = numTiles(z)
-	unit = 360 / n
[…]

### 2013-11-14 pyroute/applications/routing/pyroute-dev/tracklog.py

@@ -1,49 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from base import pyrouteModule
-from lib_gpx import lib_gpx
-import cairo
-import os
-
-class tracklog(pyrouteModule, lib_gpx):
-	""""""
-	def __init__(self, modules):
-		lib_gpx.__init__(self)
-		pyrouteModule.__init__(self, modules)
-		self.active = []
-		self.lines.append(self.active)
-		self.pointsSinceSave = 0
-
-	def addPoint(self,lat,lon):
-		self.active.append([lat,lon])
-		self.pointsSinceSave = self.pointsSinceSave + 1
-
-	def checkIfNeedsSaving(self, forceSave = False):
-		if(self.pointsSinceSave > 20 or forceSave):
-			self.save()
-
-	def save(self):
-		self.saveAs(os.path.join(os.path.dirname(__file__),
-														 "data","tracklogs.gpx"), "tracklogs")
-		self.pointsSinceSave = 0
-

### 2013-11-14 pyroute/applications/routing/pyroute-dev/util_binary.py

@@ -1,47 +1,0 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-"""
-"""
-
-__version__ = "$Rev$"[1:-2]
-__license__ = """This program is free software: you can redistribute it and/or modify
-it under the terms of the GNU General Public License as published by
-the Free Software Foundation, either version 3 of the License, or
-(at your option) any later version.
-
-This program is distributed in the hope that it will be useful,
-but WITHOUT ANY WARRANTY; without even the implied warranty of
-MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-GNU General Public License for more details.
-
-You should have received a copy of the GNU General Public License
-along with this program. If not, see <http://www.gnu.org/licenses/>."""
-_debug = 0
-
-
-from struct import *
-
-def encodeLL(lat,lon):
-	pLat = (lat + 90.0) / 180.0
-	pLon = (lon + 180.0) / 360.0
-	iLat = encodeP(pLat)
-	iLon = encodeP(pLon)
-	return(pack("II", iLat, iLon))
-
-def encodeP(p):
-	i = int(p * 4294967296.0)
-	return(i)
-
-
-def decodeLL(data):
-	iLat,iLon = unpack("II", data)
-	pLat = decodeP(iLat)
-	pLon = decodeP(iLon)
-	lat = pLat * 180.0 - 90.0
-	lon = pLon * 360.0 - 180.0
-	return(lat,lon)
-
-def decodeP(i):
-	p = float(i) / 4294967296.0
-	return(p)

### 2013-11-14 pyroute/applications/routing/pyroute/Menus/report.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-./menu.py list > debug/list.txt
-./menu.py icons > debug/missing_icons.txt
-./menu.py strings > debug/strings.txt

### 2013-11-14 pyroute/applications/routing/pyroute/compress/compress.py

@@ -1,141 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-#
-#------------------------------------------------------
-# Usage: 
-#
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-import sys
-import os
-from xml.sax import make_parser, handler
-import xml
-from struct import *
-
-class BinaryOsm(handler.ContentHandler):
-  
-  def __init__(self):
-    pass
-    
-  def encode(self, filename, output):
-    self.nextKID = 3
-    self.nextVID = 1
-    self.tags = {}
-    self.values = {}
-    
-    if(not os.path.exists(filename)):
-      print "No such data file %s" % filename
-      return
-    try:
-      self.out = open(output, "wb")
-      parser = make_parser()
-      parser.setContentHandler(self)
-      parser.parse(filename)
-      self.out.write("X")
-      self.out.close()
-    except xml.sax._exceptions.SAXParseException:
-      print "Error loading %s" % filename
-
-  def startElement(self, name, attrs):
-    """Handle XML elements"""
-    if(name =='node'):
-      self.meta = { \
-        'id':int(attrs.get('id')),
-        'lon':float(attrs.get('lat')),
-        'lat':float(attrs.get('lon'))
-        }
-      self.tags = {}
-    elif(name == 'way'):
-      self.meta = {'id':int(attrs.get('id'))}
-      self.tags = {}
-      self.waynodes = []
-    elif(name == 'relation'):
-      self.tags = {}
-    elif name == 'nd':
-      """Nodes within a way -- add them to a list"""
-      self.waynodes.append(int(attrs.get('ref')))
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/compress/decompress.py

@@ -1,118 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-#
-#------------------------------------------------------
-# Usage: 
-#
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-import sys
-import os
-from struct import *
-
-class BinaryOsm:
-  def __init__(self):
-    self.values = {}
-    pass
-    
-  def decode(self, filename, output):
-    if(not os.path.exists(filename)):
-      print "No such data file %s" % filename
-      return
-    Output = open(output, "w")
-    Input = open(filename, "rb")
-    self.readBinary(Input, Output)
-    Input.close()
-    Output.close()
-
-  def readBinary(self, Input, Output):
-    while(True):
-      type = Input.read(1)
-      if(type == 'N'):
-        self.readNode(Input, Output)
-      elif(type == 'W'):
-        self.readWay(Input, Output)
-      elif(type == 'X'):
-        print "Reached end of data!!!"
-        return
-      else:
-        print "Unknown type"
-
-  def readNode(self, Input, Output):
-    nid = unpack("L", Input.read(4))[0]
-    lat,lon = self.decodeLL(Input.read(8))
-    #print "Node %u at (%f,%f)"%(nid,lat,lon)
-    self.readTags(Input, Output)
-    
-  def readWay(self, Input, Output):
-    wid = unpack("L", Input.read(4))[0]
-    numNodes = unpack("H", Input.read(2))[0]
-    nodes = []
-    for i in range(numNodes):
-      nid = unpack('L',Input.read(4))[0]
-      nodes.append(nid)
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/dataStore.py

@@ -1,46 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Global data table 
-#
-# Usage: 
-#   (library code for pyroute GUI, not for direct use)
-#
-# Types of data stored:
-#   * Options and settings
-#   * Data (e.g. current position)
-#   * Event-related data (e.g. position of last click)
-#
-# Not stored here:
-#   * Routes (internal within the routing module)
-#   * POIs and map data
-#
-# TODO:
-#   * Event handling code needs to be moved into a module
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-from base import pyrouteModule
-
-class DataStore(pyrouteModule):
-    def __init__(self, modules):
-        pyrouteModule.__init__(self,modules)
-        self.options = {}
-    
-    def getData(self,name,default=None):
-        return(self.options.get(name,default))
-    
-    def setData(self,name,value):
-        self.options[name] = value

### 2013-11-14 pyroute/applications/routing/pyroute/geometry.py

@@ -1,88 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Handles geometry on the earth's surface (e.g. bearing/distance)
-#
-# Usage: 
-#   (library code)
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-from math import *
-from time import clock
-
-def bearing(a,b):
-  dlat = radians(b[0] - a[0])
-  dlon = radians(b[1] - a[1])
-
-  dlon = dlon * cos(radians(a[0]))
-  
-  return(degrees(atan2(dlon, dlat)))
-
-def distance(a,b, haversine=False):
-  if(haversine):
-    return(distance_haversine(a,b))
-  lat1 = radians(a[0])
-  lon1 = radians(a[1])
-  lat2 = radians(b[0])
-  lon2 = radians(b[1])
-  d = acos(sin(lat1)*sin(lat2) + cos(lat1)*cos(lat2) * cos(lon2-lon1)) * 6371;
-  return(d)
-
- 	
-def distance_haversine(a,b):
-  dlat = radians(b[0] - a[0])
-  dlon = radians(b[1] - a[1])
-  a1 = sin(0.5 * dlat)
-  a2a = cos(radians(a[0]))
-  a2b = cos(radians(b[0]))
-  a3 = sin(0.5 * dlon)
-  
-  a = a1*a1 + a2a*a2b * a3*a3
-  c = 2 * atan2(sqrt(a), sqrt(1-a))
-  d = 6371 * c
-  return(d)
-
-def compassPoint(x):
-  points = ('N','NNE','NE','ENE','E','ESE','SE','SSE','S','SSW','SW','WSW','W','WNW','NW','NNW')
-  part = 360.0 / len(points)
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/listable.py

@@ -1,53 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Interface for things which can be listed
-#
-# Usage: 
-#   (base-class for pyroute GUI libraries)
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-
-class listable:
-  """Base-class (interface) for anything that can be listed in a menu"""
-  def numItems(self):
-    """Return how many items are available"""
-    return(0)
-  
-  def getItemText(self,n):
-    """Return the label for any item number"""
-    return("-")
-  
-  def getItemStatus(self,n):
-    """Return current status for any item number"""
-    return("-")
-  
-  def isLocation(self,n):
-    """Return true if the item represents a location"""
-    return(False)
-  
-  def getItemLatLon(self,n):
-    """If the item represents a location, return it's position"""
-    return(0,0)
-  
-  def getItemClickable(self,n):
-    """If not a location, return true if the item should have a button to click on"""
-    return(False)
-    
-  def getItemAction(self,n):
-    """If the item isn't a location, return what happens if it's selected"""
-    return("")
-

### 2013-11-14 pyroute/applications/routing/pyroute/menuIcons.py

@@ -1,60 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Menu graphics (icons)
-#
-# Usage: 
-#   (library code for pyroute GUI, not for direct use)
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-import cairo
-import os
-class menuIcons:
-  def __init__(self):
-    self.images = {}
-    self.cantLoad = []
-    self.load('blank')
-    self.load('generic')
-  def load(self,name):
-    filename = os.path.join(os.path.dirname(__file__), "icons", "bitmap/%s.png" % name)
-    if(not os.path.exists(filename)):
-      print "Can't load %s" % filename
-      return(0)
-    
-    image = cairo.ImageSurface.create_from_png(filename)
-    if(not image):
-      return(0)
-    w = float(image.get_width())
-    h = float(image.get_height())
-    #print "Loaded %s: %d x %d" % (name,w,h)
-    self.images[name] = {'image':image,'w':w,'h':h}
-    return(1)
-  def draw(self,cr,name,x,y,w,h):
-    if not name in self.images.keys():
-      if(name in self.cantLoad):
-        name = 'generic'
-      elif(not self.load(name)):
-        self.cantLoad.append(name)
-        name='generic'
-        
-    icon = self.images[name]
-    cr.save()
-    cr.translate(x,y)
-    cr.scale(w / icon['w'], h / icon['h'])
-    cr.set_source_surface(icon['image'],0,0)
-    cr.paint()
-    cr.restore()
-  

### 2013-11-14 pyroute/applications/routing/pyroute/meta.py

@@ -1,41 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------# Meta-information (self-testing, self-diagnosis, etc.) for pyroute
-#
-# Usage: 
-#   Library for pyroute
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#----------------------------------------------------------------------------
-from base import pyrouteModule
-from listable import *
-
-class moduleInfo(pyrouteModule, listable):
-  def __init__(self, modules):
-    pyrouteModule.__init__(self, modules)
-    
-  def numItems(self):
-    return(len(self.m))
-  def getItemText(self,n):
-    return("Module: \"%s\"" % (self.m.keys()[n]))
-  def getItemStatus(self,n):
-    module = self.m.values()[n]
-    if("getStatus" in dir(module)):
-      return module.getStatus();
-    return("")
-  def getItemClickable(self,n):
-    return(True)
-  def getItemAction(self,n):
-    return("")

### 2013-11-14 pyroute/applications/routing/pyroute/mod_osmData.py

@@ -1,44 +1,0 @@
-from loadOsm import LoadOsm
-from base import pyrouteModule
-import os
-import urllib
-
-class osmData(pyrouteModule):
-  def __init__(self, modules):
-    pyrouteModule.__init__(self,modules)
-    self.data = LoadOsm(None)
-
-  def defaultFilename(self):
-    return("data/routing.osm")
-
-  def loadDefault(self):
-    self.load(self.defaultFilename())
-
-  def load(self,filename):
-    print "Loading OSM data from %s"%filename
-    self.data.loadOsm(filename)
-
-  def download(self,params):
-    ownpos = self.get('ownpos')
-    if(not ownpos['valid']):
-      print "Can only download around own position"
-      return
-
-    lat = ownpos['lat']
-    lon = ownpos['lon']
-    size = 0.2
-
-    url = "http://open.mapquestapi.com/xapi/api/0.6/way[bbox=%1.4f,%1.4f,%1.4f,%1.4f][highway|railway|waterway=*]" % (lon-size,lat-size,lon+size,lat+size)
-
-    print "downloading %s" % url
-
-    filename = self.defaultFilename()
-
-    if(os.path.exists(filename)):
-      print "Removing existing file"
-      os.remove(filename)
-
-    urllib.urlretrieve(url, filename)
-
-    print "Finished downloading"
-    self.load(filename)

### 2013-11-14 pyroute/applications/routing/pyroute/overlayArea.py

@@ -1,156 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Graphics library for drawing pyroute GUI menus
-#
-# Usage: 
-#   (library code for pyroute GUI)
-#
-# Features:
-#   Start by initialising a 'rectangle' that covers a certain bit of screen
-#   Then you can
-#     * Draw an icon there
-#     * Draw text in the rectangle
-#     * Make it clickable (so that it triggers an event when clicked)
-#     * Split it into smaller rectangles (to do complex GUI layouts)
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-import cairo
-import os
-
-class overlayArea:
-    def __init__(self,cr,x,y,dx,dy,modules,iconSet):
-        self.cr = cr
-        self.x1 = x;
-        self.y1 = y;
-        self.x2 = x + dx;
-        self.y2 = y + dy;
-        self.w = dx
-        self.h = dy
-        self.cx = x + 0.5 * dx
-        self.cy = y + 0.5 * dy
-        self.event = None
-        self.modules = modules
-        self.iconSet = iconSet
-    def fill(self,r,g,b,outline=0,alpha=None):
-        if(alpha == None):
-          self.cr.set_source_rgb(r,g,b)
-        else:
-          self.cr.set_source_rgba(r,g,b,alpha)
-        self.cr.rectangle(self.x1,self.y1,self.w,self.h)
-        if(outline):
-            self.cr.stroke()
-        else:
-            self.cr.fill()
-    def drawTextSomewhere(self,text,px1,py1,px2,py2):
-        if(text == None or text == ''):
-          return
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/poi_base.py

@@ -1,69 +1,0 @@
-import geometry
-from base import pyrouteModule
-import listable
-
-class poi:
-  def __init__(self,lat,lon):
-    self.lat = lat
-    self.lon = lon
-    self.title = 'Untitled at %1.3f, %1.3f' % (lat,lon)
-  def formatText(self):
-    return(self.title)
-  def distanceFrom(self,pos):
-    a = (pos['lat'], pos['lon'])
-    b = (self.lat,self.lon)
-    self.d = geometry.distance(a,b)
-    return(self.d)
-    
-  def __cmp__(self, other):
-    return cmp(self.d, other.d)
-
-class poiGroup(listable.listable):
-  def __init__(self,name):
-    self.items = []
-    self.name = name
-    self.sortpos = {'valid':False}
-    
-  # Functions to implement the listable interface
-  def numItems(self):
-    return(len(self.items))
-  def getItemText(self,n):
-    return(self.items[n].title)
-  def isLocation(self,n):
-    return(True)
-  def getItemLatLon(self,n):
-    item = self.items[n]
-    return(item.lat,item.lon)
-
-  def sort(self,pos):
-    
-    if(pos == self.sortpos):
-      return
-    self.sortpos = pos
-    print "Sorting"
-
-    if(pos['valid']):
-      for i in self.items:
-        i.d = i.distanceFrom(pos)
-
-    self.items.sort()
-    if(0):
-      for i in self.items:
-        print "%1.3f" % i.d
-
-    
-class poiModule(pyrouteModule):
-  def __init__(self, modules):
-    pyrouteModule.__init__(self, modules)
-    self.groups = []
-    self.draw = True
-
-  def sort(self, pos):
-    for g in self.groups:
-      g.sort(pos)
-      
-  def report(self):
-    for g in self.groups:
-      print "=== %s ===" % g.name
-      for i in g.items:
-        print "%1.3f, %1.3f = %s" % (i.lat, i.lon, i.title)

### 2013-11-14 pyroute/applications/routing/pyroute/poi_geoRss.py

@@ -1,66 +1,0 @@
-from poi_base import *
-import feedparser
-
-class geoRss(poiModule):
-    def __init__(self, modules, filename):
-        poiModule.__init__(self, modules)
-        f = open(filename,"r")
-        try:
-            for line in f:
-                url = line.rstrip()
-                if(url):
-                    feed = feedparser.parse(url)
-                    name = feed.feed.title
-                    self.add(name, feed)
-        finally:
-            f.close()
-        print self.groups
-
-    def getLatLon(self,item):
-        # Try getting the "point = lat lon"
-        try:
-            lat,lon = [float(ll) for ll in item['point'].split(" ")]
-            return(lat,lon,True)
-        except KeyError:
-            pass
-        except ValueError:
-            pass
-
-        # Try getting the "pos = lat lon"
-        try:
-            lat,lon = [float(ll) for ll in item['pos'].split(" ")]
-            return(lat,lon,True)
-        except KeyError:
-            pass
-        except ValueError:
-            pass
-
-        # Try getting the "geo:lat = lat, geo:lon = lon"
-        try:
-            lat = float(item['geo_lat'])
-            lon = float(item['geo_lon'])
-            return(lat,lon,True)
-        except KeyError:
-            pass
-
-        return(0,0,False)
-        
-    def add(self, name, feed):
-        group = poiGroup(name)
-        count = 0
-        for item in feed.entries:
-            lat, lon, valid = self.getLatLon(item)
-            if(valid):
-                x = poi(lat,lon)
-                x.title = item.title
-                group.items.append(x)
-                count = count + 1
-        #print "Added %d items from %s" % (count, name)
-
-        self.groups.append(group)
-
-if __name__ == "__main__":
-    g = geoRss('../Setup/feeds.txt')
-    name = g.groups.keys()[0]
-    print g.groups[name].items
-    

### 2013-11-14 pyroute/applications/routing/pyroute/poi_geonames.py

@@ -1,44 +1,0 @@
-from poi_base import *
-import feedparser
-from xml.sax import make_parser, handler
-
-class geonamesParser(handler.ContentHandler):
-  def __init__(self, filename):
-    self.entries = []
-    parser = make_parser()
-    parser.setContentHandler(self)
-    parser.parse(filename)
-  def startElement(self, name, attrs):
-    if(name == "entry"):
-      self.entry = {}
-    self.text = ''
-  def characters(self, text):
-    self.text = self.text + text
-  def endElement(self, name):
-    if(name in ('title')):
-      self.entry[name] = self.text
-    if(name in ('lat','lng')):
-      self.entry[name] = float(self.text)
-    if(name == "entry"):
-      self.entries.append(self.entry)
-      
-class geonames(poiModule):
-    def __init__(self, modules):
-        poiModule.__init__(self, modules)
-        g = geonamesParser("data/wiki.xml")
-        self.add("Wikipedia entries",g)
-
-    def add(self, name, parser):
-        group = poiGroup(name)
-        count = 0
-        for item in parser.entries:
-            x = poi(item['lat'], item['lng'])
-            x.title = item['title']
-            group.items.append(x)
-            count = count + 1
-        print "Added %d items from %s" % (count, name)
-
-        self.groups.append(group)
-
-if __name__ == "__main__":
-    g = geonamesParser("data/wiki.xml")

### 2013-11-14 pyroute/applications/routing/pyroute/poi_osm.py

@@ -1,128 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# OSM POI handler for pyroute
-#
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-from xml.sax import make_parser, handler
-from poi_base import *
-import os
-from xml.sax._exceptions import SAXParseException
-import urllib
-
-class osmPoiModule(poiModule, handler.ContentHandler):
-	def __init__(self, modules):
-		poiModule.__init__(self, modules)
-		self.draw = False
-		self.loadPOIs("all", "amenity|shop=*")
-		
-	def loadPOIs(self, name, search):
-		filename = os.path.join(os.path.dirname(__file__),
-								"data", "poi_%s.osm" % name)
-		
-		url = "http://www.informationfreeway.org/api/0.5/node[%s][%s]" %(search,
-																		self.bbox())
-		
-		if(not os.path.exists(filename)):
-			print "Downloading POIs from OSM"
-			urllib.urlretrieve(url, filename)
-		self.load(filename, os.path.join(os.path.dirname(__file__),
-														"Setup", "poi.txt"))
-
-	def bbox(self):
-		# TODO: based on location!
-		return "bbox=-6,48,2.5,61"
-	
-	def load(self, filename, listfile):
-		self.filters = []
-		print "Loading POIs from %s" % listfile
-		f = open(listfile,"r")
-		try:
-			for line in f:
-				if(len(line) > 1):
-					text = line.rstrip()
-					name, filter = text.split('|')
-					group = poiGroup(name)
-					self.groups.append(group)
-					self.filters.append({'name':name,'filter':filter,'group':group})
-		finally:
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/poi_waypoints.py

@@ -1,106 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# Waypoint handler for pyroute
-#
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-from xml.sax import make_parser, handler
-from poi_base import *
-import os
-
-class waypointsModule(poiModule, handler.ContentHandler):
-  def __init__(self, modules, filename = None):
-    poiModule.__init__(self, modules)
-    self.storeFields = ('name','sym')
-    self.groups.append(poiGroup("Waypoints"))
-    self.filename = None
-    self.nextNumericWpt = 1
-    if(filename):
-      if(os.path.exists(filename)):
-        self.load(filename)
-        self.filename = filename
-
-  def load(self, filename):
-    self.inField = False
-    parser = make_parser()
-    parser.setContentHandler(self)
-    parser.parse(filename)
-  
-  def startElement(self, name, attrs):
-    if name == "wpt":
-      self.parsedWaypoint = { \
-        'lat': float(attrs.get('lat')),
-        'lon': float(attrs.get('lon'))}
-    if name in self.storeFields:
-      self.fieldText = ''
-      self.inField = True
-      
-  def endElement(self, name):
-    if self.inField:
-      if name in self.storeFields:
-        self.parsedWaypoint[name] = self.fieldText
-      self.inField = False
-    if(name == "wpt"):
-      self.storeWaypoint(self.parsedWaypoint)
-        
-  def characters(self, text):
-    if self.inField:
-      self.fieldText = self.fieldText + text
-    
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/projection.py

@@ -1,152 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# Projection code (lat/long to screen conversions)
-#
-# Usage: 
-#   (library code for pyroute GUI, not for direct use)
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-from tilenames import *
-
-class Projection:
-  def __init__(self):
-    self.xyValid = False
-    self.llValid = False
-    self.needsEdgeFind = False
-    
-    # Scale is the number of display pixels per projected unit
-    self.scale = tileSizePixels()
-    
-  def isValid(self):
-    """Test if the module contains all the information needed to do conversions"""
-    return(self.xyValid and self.llValid)
-  
-  def setView(self,x,y,w,h):
-    """Setup the display"""
-    self.w = w
-    self.h = h
-    self.xc = x + self.w
-    self.yc = y + self.h
-    self.xyValid = True
-    if(self.needsEdgeFind):
-      self.findEdges()
-    
-  def recentre(self,lat,lon,zoom = None):
-    """Move the projection to a particular geographic location
-    (with optional zoom level)"""
-    self.lat = lat
-    self.lon = lon
-    if(zoom != None):
-      self.implementNewZoom(zoom)
-      # note: implementNewZoom calls findEdges, hence the else: statement
-    else:
-      self.findEdges()
-    self.llValid = True
-    
-  def setZoom(self, value, isAdjustment=False):
-    """Change the zoom level, keeping same map centre
-    if isAdjustment is true, then value is relative to current zoom
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/pyroute.py

@@ -1,297 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# pyRoute, a routing program for OpenStreetMap-style data
-#
-#------------------------------------------------------
-# Usage: 
-#  pyroute.py [input OSM file] [start node] [end node]
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-# Changelog:
-#  2007-11-03  OJW  Created
-#------------------------------------------------------
-import sys
-import cairo
-import math 
-from xml.sax import make_parser, handler
-
-class GetRoutes(handler.ContentHandler):
-  """Parse an OSM file looking for routing information, and do routing with it"""
-  def __init__(self):
-    """Initialise an OSM-file parser"""
-    self.routing = {}
-    self.nodes = {}
-    self.minLon = 180
-    self.minLat = 90
-    self.maxLon = -180
-    self.maxLat = -90
-  def startElement(self, name, attrs):
-    """Handle XML elements"""
-    if name in('node','way','relation'):
-      if name == 'node':
-        """Nodes need to be stored"""
-        id = int(attrs.get('id'))
-        lat = float(attrs.get('lat'))
-        lon = float(attrs.get('lon'))
-        self.nodes[id] = (lat,lon)
-        if lon < self.minLon:
-          self.minLon = lon
-        if lat < self.minLat:
-          self.minLat = lat
-        if lon > self.maxLon:
-          self.maxLon = lon
-        if lat > self.maxLat:
-          self.maxLat = lat
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/routeAsOsm.py

@@ -1,73 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# routeAsOsm - routes within an OSM file, and generates an
-# OSM file containing the result
-#
-#------------------------------------------------------
-# Usage: 
-#  routeAsOsm.py [input OSM file] [start node] [end node] [transport] [description]
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-# Changelog:
-#  2007-11-04  OJW  Created
-#  2007-11-05  OJW  Multiple forms of transport
-#------------------------------------------------------
-from route import *
-  
-def routeToOsm(nodeList, osmData, description="", transport=""):
-  """Format a route (as list of nodes) into an OSM file"""
-  output = ''
-  output = output + "<?xml version='1.0' encoding='UTF-8'?>\n";
-  output = output + "<osm version='0.5' generator='pyroute'>\n";
-  
-  for i in nodeList:
-    output = output + " <node id='%d' lat='%f' lon='%f' />\n" % ( \
-      i,
-      osmData.nodes[i][0],
-      osmData.nodes[i][1])
-
-  output = output + " <way id='1'>\n"
-  for i in nodeList:
-    output = output + "  <nd ref='%d' />\n" % i
-    
-  output = output + "  <tag k='route_display' v='yes' />\n"
-  output = output + "  <tag k='name' v='%s' />\n" % description
-  output = output + "  <tag k='transport' v='%s' />\n" % transport
-  output = output + " </way>\n"
-  output = output + "</osm>"
-  
-  return(output)
-  
-
-if __name__ == "__main__":
-  try:
-    # Load data
-    data = LoadOsm(sys.argv[1])
-  
-    # Do routing
-    router = Router(data)
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/routeOrDirect.py

@@ -1,43 +1,0 @@
-from route import Router
-
-class RouteOrDirect(Router):
-    def __init__(self, data):
-        Router.__init__(self,data)
-        self.route = {'valid':False}
-        self.mode = 'direct';
-    def setMode(self, mode):
-      self.mode = mode
-    def setStartNode(self,node):
-        self.route['startnode'] = node
-        self.route['startpos'] = self.data.nodes[node]
-    def setEndNode(self,node):
-        self.route['endnode'] = node
-        self.route['endpos'] = self.data.nodes[node]
-    def setStartLL(self,lat,lon,transport):
-        self.route['startnode'] = self.data.findNode(lat,lon,transport)
-        self.route['startpos'] = (lat,lon)
-        self.route['transport'] = transport
-    def setEndLL(self,lat,lon,transport):
-        self.route['endnode'] = self.data.findNode(lat,lon,transport)
-        self.route['endpos'] = (lat,lon)
-        self.route['transport'] = transport
-    def update(self):
-      if(self.mode == 'route'):
-	      result, newroute = self.doRouteAsLL( \
-	          self.route['startnode'],
-	          self.route['endnode'],
-	          self.route['transport'])
-	      if result == 'success':
-	          self.route['route'] = newroute
-	          self.route['valid'] = True
-	      else:
-	          self.route['route'] = [self.route['startpos'],self.route['endpos']]
-	          self.route['valid'] = True
-      else:
-        self.route['route'] = []
-        self.route['route'].append(self.route['startpos'])
-        self.route['route'].append(self.route['endpos'])
-        self.route['valid'] = True
-        
-    def valid(self):
-        return(self.route['valid'])

### 2013-11-14 pyroute/applications/routing/pyroute/tilenames.py

@@ -1,91 +1,0 @@
-#!/usr/bin/env python
-#-------------------------------------------------------
-# Translates between lat/long and the slippy-map tile
-# numbering scheme
-#
-# http://wiki.openstreetmap.org/index.php/Slippy_map_tilenames
-#
-# Written by Oliver White, 2007
-# This file is public-domain
-#-------------------------------------------------------
-from math import *
-
-def numTiles(z):
-  return(pow(2,z))
-
-def sec(x):
-  return(1/cos(x))
-
-def latlon2relativeXY(lat,lon):
-  x = (lon + 180) / 360
-  y = (1 - log(tan(radians(lat)) + sec(radians(lat))) / pi) / 2
-  return(x,y)
-
-def latlon2xy(lat,lon,z):
-  n = numTiles(z)
-  x,y = latlon2relativeXY(lat,lon)
-  return(n*x, n*y)
-
-def tileXY(lat, lon, z):
-  x,y = latlon2xy(lat,lon,z)
-  return(int(x),int(y))
-
-def xy2latlon(x,y,z):
-  n = numTiles(z)
-  relY = y / n
-  lat = mercatorToLat(pi * (1 - 2 * relY))
-  lon = -180.0 + 360.0 * x / n
-  return(lat,lon)
-
-def latEdges(y,z):
-  n = numTiles(z)
-  unit = 1 / n
-  relY1 = y * unit
-  relY2 = relY1 + unit
-  lat1 = mercatorToLat(pi * (1 - 2 * relY1))
-  lat2 = mercatorToLat(pi * (1 - 2 * relY2))
-  return(lat1,lat2)
-
-def lonEdges(x,z):
-  n = numTiles(z)
-  unit = 360 / n
-  lon1 = -180 + x * unit
-  lon2 = lon1 + unit
-  return(lon1,lon2)
-
-def tileEdges(x,y,z):
-  lat1,lat2 = latEdges(y,z)
-  lon1,lon2 = lonEdges(x,z)
-  return((lat2, lon1, lat1, lon2)) # S,W,N,E
-
-def mercatorToLat(mercatorY):
-  return(degrees(atan(sinh(mercatorY))))
-
-def tileSizePixels():
-  return(256)
-
-def tileLayerExt(layer):
-  if(layer in ('oam')):
-    return('jpg')
-  return('png')
-
-def tileLayerBase(layer):
-  layers = { \
[…]

### 2013-11-14 pyroute/applications/routing/pyroute/tracklog.py

@@ -1,49 +1,0 @@
-#!/usr/bin/python
-#-----------------------------------------------------------------------------
-# 
-#
-# Usage: 
-# 
-#-----------------------------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#-----------------------------------------------------------------------------
-from base import pyrouteModule
-import os
-import cairo
-from lib_gpx import lib_gpx
-
-class tracklog(pyrouteModule, lib_gpx):
-  """  """
-  def __init__(self, modules):
-    lib_gpx.__init__(self)
-    pyrouteModule.__init__(self, modules)
-    self.active = []
-    self.lines.append(self.active)
-    self.pointsSinceSave = 0
-    
-  def addPoint(self,lat,lon):
-    self.active.append([lat,lon])
-    self.pointsSinceSave = self.pointsSinceSave + 1
-
-  def checkIfNeedsSaving(self, forceSave = False):
-    if(self.pointsSinceSave > 20 or forceSave):
-      self.save()
-      
-  def save(self):
-    self.saveAs(os.path.join(os.path.dirname(__file__),
-                             "data","tracklogs.gpx"), "tracklogs")
-    self.pointsSinceSave = 0
-    

### 2013-11-14 pyroute/applications/routing/pyroute/weights.py

@@ -1,28 +1,0 @@
-Weightings = { \
-  'motorway': {'car':10},
-  'trunk':    {'car':10, 'cycle':0.05},
-  'primary':  {'cycle': 0.3, 'car':2, 'foot':1, 'horse':0.1},
-  'secondary': {'cycle': 1, 'car':1.5, 'foot':1, 'horse':0.2},
-  'tertiary': {'cycle': 1, 'car':1, 'foot':1, 'horse':0.3},
-  'unclassified': {'cycle': 1, 'car':1, 'foot':1, 'horse':1},
-  'minor': {'cycle': 1, 'car':1, 'foot':1, 'horse':1},
-  'cycleway': {'cycle': 3, 'foot':0.2},
-  'residential': {'cycle': 3, 'car':0.7, 'foot':1, 'horse':1},
-  'track': {'cycle': 1, 'car':1, 'foot':1, 'horse':1, 'mtb':3},
-  'service': {'cycle': 1, 'car':1, 'foot':1, 'horse':1},
-  'bridleway': {'cycle': 0.8, 'foot':1, 'horse':10, 'mtb':3},
-  'footway': {'cycle': 0.2, 'foot':1},
-  'steps': {'foot':1, 'cycle':0.3},
-  'rail':{'train':1},
-  'light_rail':{'train':1},
-  'subway':{'train':1}
-  }
-
-def getWeight(transport, wayType):
-  try:
-    return(Weightings[wayType][transport])
-  except KeyError:
-    # Default: if no weighting is defined, then assume it can't be routed
-    return(0)
- 
- 

### 2013-11-14 pyroute/applications/routing/pyroute_webGUI/server.py

@@ -1,160 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------------------
-# 
-#----------------------------------------------------------------------------
-# Copyright 2008, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#---------------------------------------------------------------------------
-from BaseHTTPServer import *
-import re
-import sys
-import math
-import os
-import pickle
-
-from tile_route import TileRoute
-
-sys.path.append("../pyroutelib2")
-import routeAsCSV
-
-class tileServer(BaseHTTPRequestHandler):
-  def __init__(self, request, client_address, server):
-    self.settings = None
-    self.re_tile = re.compile('/tile/(\w+)/(\d+)/(\d+)/(\d+)\.png')
-    self.re_route = re.compile('/route\?start=(.*?)%2C(.*?)&end=(.*?)%2C(.*?)&type=(.*?)')
-    BaseHTTPRequestHandler.__init__(self, request, client_address, server)
-
-  def getNextRoute(self):
-    for id in range(1,10000):
-      filename = "route/%d.txt" % id
-      if(not os.path.exists(filename)):
-        return(filename,id)
-
-  def settingsFilename(self):
-    return("settings.txt")
-  
-  def getSettings(self):
-    """Load self.settings from disk, or return existing copy, or create blank copy"""
-    if(not self.settings):
-      try:
-        self.settings = {}
-        f = open(self.settingsFilename(), "r")
-        self.settings = pickle.load(f)
-        f.close()
-      except IOError:
-        print "Couldn't load settings from disk"
-        
-        
-  def saveSettings(self):
-    """save self.settings to disk"""
-    f = open(self.settingsFilename(), "w")
-    pickle.dump(self.settings, f)
-    f.close()
-    
[…]

### 2013-11-14 pyroute/applications/routing/pyroute_webGUI/tile_base.py

@@ -1,83 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------------------
-# Base class for rendering tile-style images
-#----------------------------------------------------------------------------
-# Copyright 2008, authors:
-# * Sebastian Spaeth
-# * Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#---------------------------------------------------------------------------
-import StringIO
-import cairo
-from tilenames import *
-
-class proj:
-  """Simple projection class for geographic data.  Converts lat/long to pixel position"""
-  def __init__(self, tx,ty,tz, to):
-    """Setup a projection.  
-    tx,ty,tz is the slippy map tile number.  
-    to is the (width,height) of an image to render onto
-    """ 
-    (S,W,N,E) = tileEdges(tx,ty,tz)
-    self.to = to
-    self.S = S
-    self.N = N
-    self.E = E
-    self.W = W
-    self.dLat = N - S
-    self.dLon = E - W
-    self.x1 = 0
-    self.y1 = 0
-    self.x2 = to[0]
-    self.y2 = to[1]
-    self.dx = self.x2 - self.x1
-    self.dy = self.y2 - self.y1
-  def project(self,lat,lon):
-    """Project lat/long (in degrees) into pixel position on the tile"""
-    pLat = (lat - self.S) / self.dLat
-    pLon = (lon - self.W) / self.dLon
-    x = self.x1 + pLon * self.dx
-    y = self.y2 - pLat * self.dy
-    return(x,y)
-
-class TileBase:
-  def draw(self):
-    pass # Override this function
-    
-  def RenderTile(self, z,x,y, outputFile):
-    
-    # Create the image
-    im = cairo.ImageSurface (cairo.FORMAT_ARGB32, 256, 256)
-    self.proj = proj(x,y,z,(256,256))  # create a projection for this tile
[…]

### 2013-11-14 pyroute/applications/routing/pyroute_webGUI/tile_route.py

@@ -1,40 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# Generates map tiles showing a route from stored CSV file
-#----------------------------------------------------------------
-# Copyright 2008, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#----------------------------------------------------------------
-from tile_base import TileBase
-
-class TileRoute(TileBase):
-  def __init__(self, filename):
-    self.filename = filename
-  def draw(self):
-    self.ctx.set_source_rgb(0, 0, 0)
-    f = open(self.filename, 'r')
-    if(f):
-      first = True
-      for line in f:
-        (id,lat,lon) = map(float, line.split(','))
-        (x,y) = self.proj.project(lat,lon)
-        #print "%f,%f -> %f,%f" % (lat,lon,x,y)
-        if(first):
-          self.ctx.move_to(x,y)
-          first = False
-        else:
-          self.ctx.line_to(x,y)
-      f.close()
-      self.ctx.stroke()

### 2013-11-14 pyroute/applications/routing/pyroutelib2/loadOsm.py

@@ -1,201 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# load OSM data file into memory
-#
-#------------------------------------------------------
-# Copyright 2007, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-# Changelog:
-#  2007-11-04  OJW  Modified from pyroute.py
-#  2007-11-05  OJW  Multiple forms of transport
-#------------------------------------------------------
-import sys
-import os
-import tiledata
-import tilenames
-import re
-import weights
-
-class LoadOsm:
-  """Parse an OSM file looking for routing information, and do routing with it"""
-  def __init__(self, transport):
-    """Initialise an OSM-file parser"""
-    self.routing = {}
-    self.rnodes = {}
-    self.transport = transport
-    self.tiles = {}
-    self.weights = weights.RoutingWeights()
-
-  def getArea(self, lat, lon):
-    """Download data in the vicinity of a lat/long"""
-
-    z = tiledata.DownloadLevel()
-    (x,y) = tilenames.tileXY(lat, lon, z)
-
-    tileID = '%d,%d'%(x,y)
-    if(self.tiles.get(tileID,False)):
-      #print "Already got %s" % tileID
-      return
-    self.tiles[tileID] = True
-
-    filename = tiledata.GetOsmTileData(z,x,y)
-    #print "Loading %d,%d at z%d from %s" % (x,y,z,filename)
-    return(self.loadOsm(filename))
-
-  def loadOsm(self, filename):
-    if(not os.path.exists(filename)):
-      print "No such data file %s" % filename
-      return(False)
-    fp = open(filename, "r")
-    re_way = re.compile("<way id='(\d+)'>\s*$")
[…]

### 2013-11-14 pyroute/applications/routing/pyroutelib2/route.py

@@ -1,150 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------
-# Routing for OSM data
-#
-#------------------------------------------------------
-# Usage as library:
-#   datastore = loadOsm('transport type')
-#   router = Router(datastore)
-#   result, route = router.doRoute(node1, node2)
-#
-# (where transport is cycle, foot, car, etc...)
-#------------------------------------------------------
-# Copyright 2007-2008, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#------------------------------------------------------
-import sys
-import math
-from loadOsm import *
-
-class Router:
-  def __init__(self, data):
-    self.data = data
-  def distance(self,n1,n2):
-    """Calculate distance between two nodes"""
-    lat1 = self.data.rnodes[n1][0]
-    lon1 = self.data.rnodes[n1][1]
-    lat2 = self.data.rnodes[n2][0]
-    lon2 = self.data.rnodes[n2][1]
-    # TODO: projection issues
-    dlat = lat2 - lat1
-    dlon = lon2 - lon1
-    dist2 = dlat * dlat + dlon * dlon
-    dist = math.sqrt(dist2)
-    return(dist)
-
-  def doRoute(self,start,end):
-    """Do the routing"""
-    self.searchEnd = end
-    closed = [start]
-    self.queue = []
-
-    # Start by queueing all outbound links from the start node
-    blankQueueItem = {'end':-1,'distance':0,'nodes':str(start)}
-
-    try:
-      for i, weight in self.data.routing[start].items():
-        self.addToQueue(start,i, blankQueueItem, weight)
-    except KeyError:
-      return('no_such_node',[])
-
-    # Limit for how long it will search
-    count = 0
-    while count < 1000000:
-      count = count + 1
-      try:
-        nextItem = self.queue.pop(0)
-      except IndexError:
-        # Queue is empty: failed
[…]

### 2013-11-14 pyroute/applications/routing/pyroutelib2/tiledata.py

@@ -1,60 +1,0 @@
-#!/usr/bin/python
-#----------------------------------------------------------------------------
-# Download OSM data covering the area of a slippy-map tile 
-#
-# Features:
-#  * Cached (all downloads stored in cache/z/x/y/data.osm)
-#----------------------------------------------------------------------------
-# Copyright 2008, Oliver White
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-#---------------------------------------------------------------------------
-from urllib import *
-import os
-
-def DownloadLevel():
-  """All primary downloads are done at a particular zoom level"""
-  return(15)
-
-def GetOsmTileData(z,x,y):
-  """Download OSM data for the region covering a slippy-map tile"""
-  if(x < 0 or y < 0 or z < 0 or z > 25):
-    print "Disallowed %d,%d at %d" % (x,y,z)
-    return
-  
-  directory = 'cache/%d/%d/%d' % (z,x,y)
-  filename = '%s/data.osm' % (directory)
-  if(not os.path.exists(directory)):
-    os.makedirs(directory)
-  
-  if(z == DownloadLevel()):
-    # Download the data
-    URL = 'http://dev.openstreetmap.org/~ojw/api/?/map/%d/%d/%d' % (z,x,y)
-     
-    if(not os.path.exists(filename)): # TODO: allow expiry of old data
-      urlretrieve(URL, filename)
-    return(filename)
-    
-  elif(z > DownloadLevel()):
-    # use larger tile
-    while(z > DownloadLevel()):
-      z = z - 1
-      x = int(x / 2)
-      y = int(y / 2)
-    return(GetOsmTileData(z,x,y))
-  return("")
-
-if(__name__ == "__main__"):
-  """test mode"""
-  print GetOsmTileData(15, 16218, 10741)

### 2013-11-14 pyroute/applications/routing/yours/branches/version-1.0-via/www/routing.js

@@ -1,1390 +1,0 @@
-// Waypoint class for storing all waypoint related data (marker, route to
-// next way point)
-function Waypoint()
-{
-	this.set_prev= function(prev)
-	{
-		this.prev= prev;
-
-		this.style= style_mid;
-		if (this.prev == undefined)
-			this.style= style_from;
-		else if (this.next == undefined)
-			this.style= style_to;
-	}
-
-	this.set_next= function(next)
-	{
-		this.next= next;
-
-		this.style= style_mid;
-		if (this.prev == undefined)
-			this.style= style_from;
-		else if (this.next == undefined)
-			this.style= style_to;
-	}
-
-	this.set_position= function(lonlat)
-	{
-		this.clear_position();
-
-		var marker_url= 'markers/marker-yellow.png';
-		if (this.prev == undefined)
-			marker_url= 'markers/marker-green.png';
-		if (this.next == undefined)
-			marker_url= 'markers/marker-red.png';
-		var size = new OpenLayers.Size(21,25);
-		var offset = new OpenLayers.Pixel(-(size.w/2), -size.h);
-
-		var icon = new OpenLayers.Icon(marker_url,
-			size,offset);
-		this.marker = new OpenLayers.Marker(lonlat.clone(), icon);
-		markers.addMarker(this.marker);
-
-		if (this.pos_el != undefined)
-		{
-			map_ll= lonlat.clone();
-			map_ll.transform(map.projection,
-				map.displayProjection);
-
-			precision= 6;
-			str= map_ll.lat.toFixed(precision) + ', ' +
-				map_ll.lon.toFixed(precision);
-			this.pos_el.innerHTML= str;
-		}
-	}
-	this.clear_position= function()
-	{
-		if (this.marker != undefined)
-		{
-			markers.removeMarker(this.marker);
-			this.marker.destroy();
-			this.marker= undefined;
-
-			this.remove_route();
-			if (this.prev != undefined)
-				this.prev.remove_route();
-			if (this.pos_el != undefined)
-				this.pos_el.innerHTML= "";
-		}
-	}
-	this.set_route= function(routelist)
-	{
-		if (this.route != undefined)
-		{
-			alert('Waypoint.set_route: should update route');
-			return;
-		}
-		this.route= routelist;
-	}
-	this.set_distance= function(distance)
-	{
-		this.distance= parseFloat(distance);
-	}
-	this.remove_route= function()
-	{
-		if (this.route == undefined)
-			return;
[…]

### 2013-11-14 pyroute/applications/routing/yours/trunk/www/jquery/jquery-ui.js

@@ -1,1 +1,0 @@
-link jquery-ui-1.8.custom.min.js

### 2013-11-14 pyroute/applications/routing/yours/trunk/www/jquery/jquery.js

@@ -1,1 +1,0 @@
-link jquery-1.6.1.min.js

### 2013-11-14 pyroute/base.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Projection code (lat/long to screen conversions)
+#
+# Usage:
+#   * Derive all pyroute modules fom this class
+#   * Put "pyrouteModule.__init__(self,modules)" in your init function
+#   * Instantiate using modules.append(yourmodule(modules))
+#      where "modules" is the list of all pyroute modules
+#
+# Features:
+#   * Get and set data from the global table
+#   * Send messages or trigger events
+#   * Access other modules (using "self.m['modulename']")
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#----------------------------------------------------------------------------
+class pyrouteModule:
+  def __init__(self, modules):
+    self.m  = modules
+  def get(self, name, default=None):
+    return(self.m['data'].getData(name, default))
+  def set(self, name, value):
+    return(self.m['data'].setData(name, value))
+  def action(self, message):
+    self.m['events'].handleEvent(message)
+  def ownPos(self):
+    return(self.m['position'].get())
+  # Meta-info
+  def getStatus(self):
+    return("")

### 2013-11-14 pyroute/compress/compress.py

@@ -1,0 +1,140 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+#
+#------------------------------------------------------
+# Usage:
+#
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+import sys
+import os
+from xml.sax import make_parser, handler
+import xml
+from struct import *
+
+class BinaryOsm(handler.ContentHandler):
+  def __init__(self):
+    pass
+
+  def encode(self, filename, output):
+    self.nextKID = 3
+    self.nextVID = 1
+    self.tags = {}
+    self.values = {}
+
+    if(not os.path.exists(filename)):
+      print "No such data file %s" % filename
+      return
+    try:
+      self.out = open(output, "wb")
+      parser = make_parser()
+      parser.setContentHandler(self)
+      parser.parse(filename)
+      self.out.write("X")
+      self.out.close()
+    except xml.sax._exceptions.SAXParseException:
+      print "Error loading %s" % filename
+
+  def startElement(self, name, attrs):
+    """Handle XML elements"""
+    if(name =='node'):
+      self.meta = { \
+        'id':int(attrs.get('id')),
+        'lon':float(attrs.get('lat')),
+        'lat':float(attrs.get('lon'))
+        }
+      self.tags = {}
+    elif(name == 'way'):
+      self.meta = {'id':int(attrs.get('id'))}
+      self.tags = {}
+      self.waynodes = []
+    elif(name == 'relation'):
+      self.tags = {}
+    elif name == 'nd':
+      """Nodes within a way -- add them to a list"""
+      self.waynodes.append(int(attrs.get('ref')))
+    elif name == 'tag':
[…]

### 2013-11-14 pyroute/compress/decompress.py

@@ -1,0 +1,118 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+#
+#------------------------------------------------------
+# Usage:
+#
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+import sys
+import os
+from struct import *
+
+class BinaryOsm:
+  def __init__(self):
+    self.values = {}
+    pass
+
+  def decode(self, filename, output):
+    if(not os.path.exists(filename)):
+      print "No such data file %s" % filename
+      return
+    Output = open(output, "w")
+    Input = open(filename, "rb")
+    self.readBinary(Input, Output)
+    Input.close()
+    Output.close()
+
+  def readBinary(self, Input, Output):
+    while(True):
+      type = Input.read(1)
+      if(type == 'N'):
+        self.readNode(Input, Output)
+      elif(type == 'W'):
+        self.readWay(Input, Output)
+      elif(type == 'X'):
+        print "Reached end of data!!!"
+        return
+      else:
+        print "Unknown type"
+
+  def readNode(self, Input, Output):
+    nid = unpack("L", Input.read(4))[0]
+    lat,lon = self.decodeLL(Input.read(8))
+    #print "Node %u at (%f,%f)"%(nid,lat,lon)
+    self.readTags(Input, Output)
+
+  def readWay(self, Input, Output):
+    wid = unpack("L", Input.read(4))[0]
+    numNodes = unpack("H", Input.read(2))[0]
+    nodes = []
+    for i in range(numNodes):
+      nid = unpack('L',Input.read(4))[0]
+      nodes.append(nid)
[…]

### 2013-11-14 pyroute/dataStore.py

@@ -1,0 +1,46 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Global data table
+#
+# Usage:
+#   (library code for pyroute GUI, not for direct use)
+#
+# Types of data stored:
+#   * Options and settings
+#   * Data (e.g. current position)
+#   * Event-related data (e.g. position of last click)
+#
+# Not stored here:
+#   * Routes (internal within the routing module)
+#   * POIs and map data
+#
+# TODO:
+#   * Event handling code needs to be moved into a module
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from base import pyrouteModule
+
+class DataStore(pyrouteModule):
+    def __init__(self, modules):
+        pyrouteModule.__init__(self,modules)
+        self.options = {}
+
+    def getData(self,name,default=None):
+        return(self.options.get(name,default))
+
+    def setData(self,name,value):
+        self.options[name] = value

### 2013-11-14 pyroute/events.py

@@ -1,0 +1,161 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Event handler.  Messages (as text) get sent here, telling pyroute
+# to do various things (e.g. save a waypoint, open a menu, route to
+# some point)
+#
+# Usage:
+#   (library code)
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from base import pyrouteModule
+
+class pyrouteEvents(pyrouteModule):
+  def __init__(self, modules):
+      pyrouteModule.__init__(self,modules)
+
+  def handle_zoom(self,params):
+    """zoom:[in|out|zoomlevel] - zooms to a quadtile level (17=max detail, <6=whole world)"""
+    if(params == 'in'):
+      self.m['projection'].setZoom(1, True)
+    elif(params == 'out'):
+      self.m['projection'].setZoom(-1, True)
+    else:
+      self.m['projection'].setZoom(int(params))
+    self.set("needRedraw", True)
+
+  def handle_menu(self,params):
+    """menu:(name) - displays a menu. Use blank name to hide the menu"""
+    self.set('menu', params)
+
+  def handle_mode(self,params):
+    """mode:(name) - sets the transport type in use (e.g. car, bike)"""
+    self.set('mode', params)
+
+  def handle_save(self,params):
+    whichModule = params
+    self.m[whichModule].save()
+
+  def handle_option(self,params):
+    """option:add|toggle:(name):(value)"""
+    method, name = params.split(':',1)
+    if(method == 'toggle'):
+      self.set(name, not self.get(name))
+    elif(method == 'add'):
+      name,add = name.split(':')
[…]

### 2013-11-14 pyroute/follow/follow.py

@@ -1,0 +1,48 @@
+import sys
+from xml.sax import make_parser, handler
+from time import *
+
+class LoadTrack(handler.ContentHandler):
+  def __init__(self, filename):
+    self.inTrkpt = 0
+    self.inTime = 0
+    self.samples = []
+    parser = make_parser()
+    parser.setContentHandler(self)
+    parser.parse(filename)
+
+  def startElement(self, name, attrs):
+    """Handle XML elements"""
+    if name == "trkpt":
+      self.tags = { \
+        'lat':float(attrs.get('lat')),
+        'lon':float(attrs.get('lon'))}
+      self.inTrkpt = 1
+    if name == "time":
+      if self.inTrkpt:
+        self.inTime = 1
+        self.timeStr = ''
+
+  def characters(self, content):
+    if(self.inTime):
+      self.timeStr = self.timeStr + content
+
+  def endElement(self, name):
+    if name == 'time':
+      if(self.inTime):
+        self.inTime = 0
+        self.tags['t'] = mktime(strptime(self.timeStr[0:-1], "%Y-%m-%dT%H:%M:%S"))
+    if name == 'trkpt':
+      self.samples.append(self.tags)
+      self.inTrkpt = 0
+
+  def play(self, filename):
+    for pos in self.samples:
+      file = open(filename, 'w')
+      file.write("%f,%f\n" % (pos['lat'],pos['lon']))
+      file.close
+      sleep(0.5)
+
+if __name__ == "__main__":
+  track = LoadTrack(sys.argv[1])
+  track.play(sys.argv[2])

### 2013-11-14 pyroute/gui.py

@@ -1,0 +1,409 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Pyroute main GUI
+#
+# Usage:
+#   gui.py
+#
+# Controls:
+#   * drag left/right along top of window to zoom in/out
+#   * drag the map to move around
+#   * click on the map for a position menu
+#       * set your own position, if the GPS didn't already do that
+#       * set that location as a destination
+#       * route to that point
+#   * click on the top-left of the window for the main menu
+#       * download routing data around your position
+#       * browse geoRSS, wikipedia, and OSM points of interest
+#       * select your mode of transport for routing
+#           * car, bike, foot currently supported
+#       * toggle whether the map is centred on your GPS position
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it Under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+import pygtk
+pygtk.require('2.0')
+import gobject
+import gtk
+import cairo
+
+import sys
+import urllib
+import os
+from math import sqrt
+from time import clock
+from gtk import gdk
+
+#sys.path.append("../pyroutelib2")
+
+# Our modules:
+from mod_osmData import osmData
+from routeOrDirect import *
+from tilenames import *
+from geoPosition import *
+from projection import Projection
+from overlay import *
+from dataStore import *
+from poi_geoRss import geoRss
+from poi_geonames import geonames
+from poi_waypoints import waypointsModule
+from poi_osm import osmPoiModule
[…]

### 2013-11-14 pyroute/meta.py

@@ -1,0 +1,42 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Meta-information (self-testing, self-diagnosis, etc.) for pyroute
+#
+# Usage:
+#   Library for pyroute
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#----------------------------------------------------------------------------
+from base import pyrouteModule
+from listable import *
+
+class moduleInfo(pyrouteModule, listable):
+  def __init__(self, modules):
+    pyrouteModule.__init__(self, modules)
+
+  def numItems(self):
+    return(len(self.m))
+  def getItemText(self,n):
+    return("Module: \"%s\"" % (self.m.keys()[n]))
+  def getItemStatus(self,n):
+    module = self.m.values()[n]
+    if("getStatus" in dir(module)):
+      return module.getStatus();
+    return("")
+  def getItemClickable(self,n):
+    return(True)
+  def getItemAction(self,n):
+    return("")

### 2013-11-14 pyroute/overlayArea.py

@@ -1,0 +1,156 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Graphics library for drawing pyroute GUI menus
+#
+# Usage:
+#   (library code for pyroute GUI)
+#
+# Features:
+#   Start by initialising a 'rectangle' that covers a certain bit of screen
+#   Then you can
+#     * Draw an icon there
+#     * Draw text in the rectangle
+#     * Make it clickable (so that it triggers an event when clicked)
+#     * Split it into smaller rectangles (to do complex GUI layouts)
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+import cairo
+import os
+
+class overlayArea:
+    def __init__(self,cr,x,y,dx,dy,modules,iconSet):
+        self.cr = cr
+        self.x1 = x;
+        self.y1 = y;
+        self.x2 = x + dx;
+        self.y2 = y + dy;
+        self.w = dx
+        self.h = dy
+        self.cx = x + 0.5 * dx
+        self.cy = y + 0.5 * dy
+        self.event = None
+        self.modules = modules
+        self.iconSet = iconSet
+    def fill(self,r,g,b,outline=0,alpha=None):
+        if(alpha == None):
+          self.cr.set_source_rgb(r,g,b)
+        else:
+          self.cr.set_source_rgba(r,g,b,alpha)
+        self.cr.rectangle(self.x1,self.y1,self.w,self.h)
+        if(outline):
+            self.cr.stroke()
+        else:
+            self.cr.fill()
+    def drawTextSomewhere(self,text,px1,py1,px2,py2):
+        if(text == None or text == ''):
+          return
[…]

### 2013-11-14 pyroute/poi_base.py

@@ -1,0 +1,69 @@
+import geometry
+from base import pyrouteModule
+import listable
+
+class poi:
+  def __init__(self,lat,lon):
+    self.lat = lat
+    self.lon = lon
+    self.title = 'Untitled at %1.3f, %1.3f' % (lat,lon)
+  def formatText(self):
+    return(self.title)
+  def distanceFrom(self,pos):
+    a = (pos['lat'], pos['lon'])
+    b = (self.lat,self.lon)
+    self.d = geometry.distance(a,b)
+    return(self.d)
+
+  def __cmp__(self, other):
+    return cmp(self.d, other.d)
+
+class poiGroup(listable.listable):
+  def __init__(self,name):
+    self.items = []
+    self.name = name
+    self.sortpos = {'valid':False}
+
+  # Functions to implement the listable interface
+  def numItems(self):
+    return(len(self.items))
+  def getItemText(self,n):
+    return(self.items[n].title)
+  def isLocation(self,n):
+    return(True)
+  def getItemLatLon(self,n):
+    item = self.items[n]
+    return(item.lat,item.lon)
+
+  def sort(self,pos):
+
+    if(pos == self.sortpos):
+      return
+    self.sortpos = pos
+    print "Sorting"
+
+    if(pos['valid']):
+      for i in self.items:
+        i.d = i.distanceFrom(pos)
+
+    self.items.sort()
+    if(0):
+      for i in self.items:
+        print "%1.3f" % i.d
+
+
+class poiModule(pyrouteModule):
+  def __init__(self, modules):
+    pyrouteModule.__init__(self, modules)
+    self.groups = []
+    self.draw = True
+
+  def sort(self, pos):
+    for g in self.groups:
+      g.sort(pos)
+
+  def report(self):
+    for g in self.groups:
+      print "=== %s ===" % g.name
+      for i in g.items:
+        print "%1.3f, %1.3f = %s" % (i.lat, i.lon, i.title)

### 2013-11-14 pyroute/poi_geoRss.py

@@ -1,0 +1,66 @@
+from poi_base import *
+import feedparser
+
+class geoRss(poiModule):
+    def __init__(self, modules, filename):
+        poiModule.__init__(self, modules)
+        f = open(filename,"r")
+        try:
+            for line in f:
+                url = line.rstrip()
+                if(url):
+                    feed = feedparser.parse(url)
+                    name = feed.feed.title
+                    self.add(name, feed)
+        finally:
+            f.close()
+        print self.groups
+
+    def getLatLon(self,item):
+        # Try getting the "point = lat lon"
+        try:
+            lat,lon = [float(ll) for ll in item['point'].split(" ")]
+            return(lat,lon,True)
+        except KeyError:
+            pass
+        except ValueError:
+            pass
+
+        # Try getting the "pos = lat lon"
+        try:
+            lat,lon = [float(ll) for ll in item['pos'].split(" ")]
+            return(lat,lon,True)
+        except KeyError:
+            pass
+        except ValueError:
+            pass
+
+        # Try getting the "geo:lat = lat, geo:lon = lon"
+        try:
+            lat = float(item['geo_lat'])
+            lon = float(item['geo_lon'])
+            return(lat,lon,True)
+        except KeyError:
+            pass
+
+        return(0,0,False)
+
+    def add(self, name, feed):
+        group = poiGroup(name)
+        count = 0
+        for item in feed.entries:
+            lat, lon, valid = self.getLatLon(item)
+            if(valid):
+                x = poi(lat,lon)
+                x.title = item.title
+                group.items.append(x)
+                count = count + 1
+        #print "Added %d items from %s" % (count, name)
+
+        self.groups.append(group)
+
+if __name__ == "__main__":
+    g = geoRss('../Setup/feeds.txt')
+    name = g.groups.keys()[0]
+    print g.groups[name].items
+

### 2013-11-14 pyroute/poi_geonames.py

@@ -1,0 +1,44 @@
+from poi_base import *
+import feedparser
+from xml.sax import make_parser, handler
+
+class geonamesParser(handler.ContentHandler):
+  def __init__(self, filename):
+    self.entries = []
+    parser = make_parser()
+    parser.setContentHandler(self)
+    parser.parse(filename)
+  def startElement(self, name, attrs):
+    if(name == "entry"):
+      self.entry = {}
+    self.text = ''
+  def characters(self, text):
+    self.text = self.text + text
+  def endElement(self, name):
+    if(name in ('title')):
+      self.entry[name] = self.text
+    if(name in ('lat','lng')):
+      self.entry[name] = float(self.text)
+    if(name == "entry"):
+      self.entries.append(self.entry)
+
+class geonames(poiModule):
+    def __init__(self, modules):
+        poiModule.__init__(self, modules)
+        g = geonamesParser("data/wiki.xml")
+        self.add("Wikipedia entries",g)
+
+    def add(self, name, parser):
+        group = poiGroup(name)
+        count = 0
+        for item in parser.entries:
+            x = poi(item['lat'], item['lng'])
+            x.title = item['title']
+            group.items.append(x)
+            count = count + 1
+        print "Added %d items from %s" % (count, name)
+
+        self.groups.append(group)
+
+if __name__ == "__main__":
+    g = geonamesParser("data/wiki.xml")

### 2013-11-14 pyroute/poi_osm.py

@@ -1,0 +1,126 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+# OSM POI handler for pyroute
+#
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+from xml.sax import make_parser, handler
+from poi_base import *
+import os
+from xml.sax._exceptions import SAXParseException
+import urllib
+
+class osmPoiModule(poiModule, handler.ContentHandler):
+	def __init__(self, modules):
+		poiModule.__init__(self, modules)
+		self.draw = False
+		self.loadPOIs("all", "amenity|shop=*")
+
+	def loadPOIs(self, name, search):
+		filename = os.path.join(os.path.dirname(__file__),
+								"data", "poi_%s.osm" % name)
+
+		url = "http://www.informationfreeway.org/api/0.5/node[%s][%s]" %(search,
+																		self.bbox())
+
+		if(not os.path.exists(filename)):
+			print "Downloading POIs from OSM"
+			urllib.urlretrieve(url, filename)
+		self.load(filename, os.path.join(os.path.dirname(__file__),
+														"Setup", "poi.txt"))
+
+	def bbox(self):
+		# TODO: based on location!
+		return "bbox=-6,48,2.5,61"
+
+	def load(self, filename, listfile):
+		self.filters = []
+		print "Loading POIs from %s" % listfile
+		f = open(listfile,"r")
+		try:
+			for line in f:
+				if(len(line) > 1):
+					text = line.rstrip()
+					name, filter = text.split('|')
+					group = poiGroup(name)
+					self.groups.append(group)
+					self.filters.append({'name':name,'filter':filter,'group':group})
+		finally:
+			f.close()
+
[…]

### 2013-11-14 pyroute/poi_waypoints.py

@@ -1,0 +1,106 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+# Waypoint handler for pyroute
+#
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+from xml.sax import make_parser, handler
+from poi_base import *
+import os
+
+class waypointsModule(poiModule, handler.ContentHandler):
+  def __init__(self, modules, filename = None):
+    poiModule.__init__(self, modules)
+    self.storeFields = ('name','sym')
+    self.groups.append(poiGroup("Waypoints"))
+    self.filename = None
+    self.nextNumericWpt = 1
+    if(filename):
+      if(os.path.exists(filename)):
+        self.load(filename)
+        self.filename = filename
+
+  def load(self, filename):
+    self.inField = False
+    parser = make_parser()
+    parser.setContentHandler(self)
+    parser.parse(filename)
+
+  def startElement(self, name, attrs):
+    if name == "wpt":
+      self.parsedWaypoint = { \
+        'lat': float(attrs.get('lat')),
+        'lon': float(attrs.get('lon'))}
+    if name in self.storeFields:
+      self.fieldText = ''
+      self.inField = True
+
+  def endElement(self, name):
+    if self.inField:
+      if name in self.storeFields:
+        self.parsedWaypoint[name] = self.fieldText
+      self.inField = False
+    if(name == "wpt"):
+      self.storeWaypoint(self.parsedWaypoint)
+
+  def characters(self, text):
+    if self.inField:
+      self.fieldText = self.fieldText + text
+
+  def storeWaypoint(self, waypoint):
[…]

### 2013-11-14 pyroute/projection.py

@@ -1,0 +1,152 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Projection code (lat/long to screen conversions)
+#
+# Usage:
+#   (library code for pyroute GUI, not for direct use)
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from tilenames import *
+
+class Projection:
+  def __init__(self):
+    self.xyValid = False
+    self.llValid = False
+    self.needsEdgeFind = False
+
+    # Scale is the number of display pixels per projected unit
+    self.scale = tileSizePixels()
+
+  def isValid(self):
+    """Test if the module contains all the information needed to do conversions"""
+    return(self.xyValid and self.llValid)
+
+  def setView(self,x,y,w,h):
+    """Setup the display"""
+    self.w = w
+    self.h = h
+    self.xc = x + self.w
+    self.yc = y + self.h
+    self.xyValid = True
+    if(self.needsEdgeFind):
+      self.findEdges()
+
+  def recentre(self,lat,lon,zoom = None):
+    """Move the projection to a particular geographic location
+    (with optional zoom level)"""
+    self.lat = lat
+    self.lon = lon
+    if(zoom != None):
+      self.implementNewZoom(zoom)
+      # note: implementNewZoom calls findEdges, hence the else: statement
+    else:
+      self.findEdges()
+    self.llValid = True
+
+  def setZoom(self, value, isAdjustment=False):
+    """Change the zoom level, keeping same map centre
+    if isAdjustment is true, then value is relative to current zoom
[…]

### 2013-11-14 pyroute/pyroutelib2/route.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python
+#----------------------------------------------------------------
+# Routing for OSM data
+#
+#------------------------------------------------------
+# Usage as library:
+#   router = Router(LoadOsmObject)
+#   result, route = router.doRoute(node1, node2, transport)
+#
+# Usage from command-line:
+#   route.py filename.osm node1 node2 transport
+#
+# (where transport is cycle, foot, car, etc...)
+#------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#------------------------------------------------------
+# Changelog:
+#  2007-11-04  OJW  Modified from pyroute.py
+#  2007-11-05  OJW  Multiple forms of transport
+#------------------------------------------------------
+import sys
+import math
+from loadOsm import *
+
+class Router:
+  def __init__(self, data):
+    self.data = data
+  def distance(self,n1,n2):
+    """Calculate distance between two nodes"""
+    lat1 = self.data.nodes[n1][0]
+    lon1 = self.data.nodes[n1][1]
+    lat2 = self.data.nodes[n2][0]
+    lon2 = self.data.nodes[n2][1]
+    # TODO: projection issues
+    dlat = lat2 - lat1
+    dlon = lon2 - lon1
+    dist2 = dlat * dlat + dlon * dlon
+    return(math.sqrt(dist2))
+
+  def doRouteAsLL(self,start,end,transport):
+    result, nodes = self.doRoute(start,end,transport)
+    if(result != 'success'):
+      return(result,[])
+    pos = []
+    for node in nodes:
+      lat,lon = self.data.nodes[node]
+      pos.append((lat,lon))
+    return(result,pos)
+  def doRoute(self,start,end,transport):
+    """Do the routing"""
+    self.searchEnd = end
+    closed = [start]
+    self.queue = []
+
[…]

### 2013-11-14 pyroute/pyroutelib2/tilenames.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python
+#-------------------------------------------------------
+# Translates between lat/long and the slippy-map tile
+# numbering scheme
+#
+# http://wiki.openstreetmap.org/index.php/Slippy_map_tilenames
+#
+# Written by Oliver White, 2007
+# This file is public-domain
+#-------------------------------------------------------
+from math import *
+
+def numTiles(z):
+  return(pow(2,z))
+
+def sec(x):
+  return(1/cos(x))
+
+def latlon2relativeXY(lat,lon):
+  x = (lon + 180) / 360
+  y = (1 - log(tan(radians(lat)) + sec(radians(lat))) / pi) / 2
+  return(x,y)
+
+def latlon2xy(lat,lon,z):
+  n = numTiles(z)
+  x,y = latlon2relativeXY(lat,lon)
+  return(n*x, n*y)
+
+def tileXY(lat, lon, z):
+  x,y = latlon2xy(lat,lon,z)
+  return(int(x),int(y))
+
+def xy2latlon(x,y,z):
+  n = numTiles(z)
+  relY = y / n
+  lat = mercatorToLat(pi * (1 - 2 * relY))
+  lon = -180.0 + 360.0 * x / n
+  return(lat,lon)
+
+def latEdges(y,z):
+  n = numTiles(z)
+  unit = 1 / n
+  relY1 = y * unit
+  relY2 = relY1 + unit
+  lat1 = mercatorToLat(pi * (1 - 2 * relY1))
+  lat2 = mercatorToLat(pi * (1 - 2 * relY2))
+  return(lat1,lat2)
+
+def lonEdges(x,z):
+  n = numTiles(z)
+  unit = 360 / n
+  lon1 = -180 + x * unit
+  lon2 = lon1 + unit
+  return(lon1,lon2)
+
+def tileEdges(x,y,z):
+  lat1,lat2 = latEdges(y,z)
+  lon1,lon2 = lonEdges(x,z)
+  return((lat2, lon1, lat1, lon2)) # S,W,N,E
+
+def mercatorToLat(mercatorY):
+  return(degrees(atan(sinh(mercatorY))))
+
+def tileSizePixels():
+  return(256)
+
+def tileLayerExt(layer):
+  if(layer in ('oam')):
+    return('jpg')
+  return('png')
+
+def tileLayerBase(layer):
+  layers = { \
[…]

### 2013-11-14 pyroute/routeOrDirect.py

@@ -1,0 +1,60 @@
+import sys
+sys.path.append('./pyroutelib2')
+sys.path.append('../grower')
+from route import Router
+from grower import Grower
+
+class RouteOrDirect(Router, Grower):
+    def __init__(self, data):
+        Router.__init__(self,data)
+        Grower.__init__(self,data)
+        self.route = {'valid':False}
+        self.mode = 'direct';
+    def setMode(self, mode):
+      self.mode = mode
+    def setStartNode(self,node):
+        self.route['startnode'] = node
+        self.route['startpos'] = self.data.nodes[node]
+    def setEndNode(self,node):
+        self.route['endnode'] = node
+        self.route['endpos'] = self.data.nodes[node]
+    def setStartLL(self,lat,lon,transport):
+        self.route['startnode'] = self.data.findNode(lat,lon,transport)
+        self.route['startpos'] = (lat,lon)
+        self.route['transport'] = transport
+    def setEndLL(self,lat,lon,transport):
+        self.route['endnode'] = self.data.findNode(lat,lon,transport)
+        self.route['endpos'] = (lat,lon)
+        self.route['transport'] = transport
+    def update(self):
+        if(self.mode == 'route'):
+            result, newroute = self.doRouteAsLL(self.route['startnode'],
+                                                self.route['endnode'],
+                                                self.route['transport'])
+            if result == 'success':
+                self.route['route'] = newroute
+                self.route['valid'] = True
+            else:
+                print 'failed to route'
+                self.route['route'] = [self.route['startpos'],self.route['endpos']]
+                self.route['valid'] = True
+        elif self.mode == 'direct':
+            self.route['route'] = []
+            self.route['route'].append(self.route['startpos'])
+            self.route['route'].append(self.route['endpos'])
+            self.route['valid'] = True
+        elif self.mode == 'cycle':
+            self.route['route'] = []
+            result, newroute = self.growCycleAsLL(self.route['startnode'],
+                                                  20,
+                                                  0,
+                                                  0,
+                                                  self.route['transport'])
+            if result == 'success':
+                self.route['route'] = newroute
+                self.route['valid'] = True
+            else:
+                self.route['valid'] = False
+
+    def valid(self):
+        return(self.route['valid'])

### 2013-11-14 pyroute/sketch.py

@@ -1,0 +1,46 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+# Sketch-on-map module for pyroute
+#
+# Usage:
+#
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from base import pyrouteModule
+import os
+import cairo
+from lib_gpx import lib_gpx
+
+class sketching(pyrouteModule, lib_gpx):
+  """  """
+  def __init__(self, modules):
+    lib_gpx.__init__(self)
+    pyrouteModule.__init__(self, modules)
+
+  def startStroke(self,x,y):
+    lat,lon = self.m['projection'].xy2ll(x,y)
+    self.latest = [(lat,lon)]
+    self.lines.append(self.latest)
+
+  def moveTo(self,x,y):
+    lat,lon = self.m['projection'].xy2ll(x,y)
+    self.latest.append((lat,lon))
+    self.set("needRedraw", 1)
+
+  def save(self):
+      self.saveAs("data/sketches/latest.gpx")
+      

### 2013-11-14 pyroute/tracklog.py

@@ -1,0 +1,49 @@
+#!/usr/bin/python
+#-----------------------------------------------------------------------------
+#
+#
+# Usage:
+#
+#-----------------------------------------------------------------------------
+# Copyright 2007, Oliver White
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+#-----------------------------------------------------------------------------
+from base import pyrouteModule
+import os
+import cairo
+from lib_gpx import lib_gpx
+
+class tracklog(pyrouteModule, lib_gpx):
+  """  """
+  def __init__(self, modules):
+    lib_gpx.__init__(self)
+    pyrouteModule.__init__(self, modules)
+    self.active = []
+    self.lines.append(self.active)
+    self.pointsSinceSave = 0
+
+  def addPoint(self,lat,lon):
+    self.active.append([lat,lon])
+    self.pointsSinceSave = self.pointsSinceSave + 1
+
+  def checkIfNeedsSaving(self, forceSave = False):
+    if(self.pointsSinceSave > 20 or forceSave):
+      self.save()
+
+  def save(self):
+    self.saveAs(os.path.join(os.path.dirname(__file__),
+                             "data","tracklogs.gpx"), "tracklogs")
+    self.pointsSinceSave = 0
+

### 2013-11-18 paper.tex
Did a lot of work on improving the code and added Brent's algorithm to the writeup
Brent's algorithm to be implemented in the code shortly.

--- 2013-11-08 paper.tex
@@
 \usepackage{algpseudocode}
+\usepackage{algorithm}
 \usepackage[toc,page]{appendix}
@@
 equation to correspond with our starting point and radius as follows:
-\[ x = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + x_0.x \]
-\[ y = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + x_0.y \]
+\[ x = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + x_0 \]
+\[ y = \frac{d}{2\pi}(\cos ( t + \phi ) - \cos \phi ) + y_0 \]
 Of course, this needs some adjustment to deal with the difference of using
@@
 Incorporating this yields the final equations:
-\[ x = \frac{d}{2\pi}(\cos (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \cos \phi) + x_0.x \]
-\[ y = \frac{d}{2\pi}(\sin (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \sin \phi)+ x_0.y. \]
+\[ x = \frac{d}{2\pi}(\cos (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \cos \phi) + x_0 \]
+\[ y = \frac{d}{2\pi}(\sin (\min(\frac{2\pi}{d}d_i,2\pi) + \phi) - \sin \phi)+ y_0. \]
 
@@
 \begin{align}
-  x_j.x = \frac{d}{2\pi} ( & \cos( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
-                                  + \phi ) \notag \\ & - \cos \phi ) + x_0.x
-                                  \label{eq:xjx} \\
-  x_j.y = \frac{d}{2\pi} ( & \sin( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
-                                  + \phi ) \notag \\ & - \sin \phi ) + x_0.y.
-                                  \label{eq:xjy}
+  x_j = \frac{d}{2\pi} ( & \cos( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
+                                  + \phi ) \notag \\ & - \cos \phi ) + x_0
+                                  \label{eq:xj} \\
+  y_j = \frac{d}{2\pi} ( & \sin( \frac{ 2 \pi }{ d } ( \min( d, d_i + d_j ) )
+                                  + \phi ) \notag \\ & - \sin \phi ) + y_0.
+                                  \label{eq:yj}
 \end{align}
 To satisfy our constraint, we have
+\[ d_j = \sqrt{ ( x_j(d_j) - x_i )^2 + ( x_j(d_j) - x_i )^2 }. \]
+
+\subsubsection{Finding $d_j$}
+Obviously, this is a rather difficult equation to truly solve, so we must only
+heuristically find a solution. Unfortunately, even the heuristic solution is
+a difficult one for a few reasons. Most problematically, the sine and cosine
+functions have up to two stationary points on the interval we are considering
+and there may not be a solution of $d_j$ that will satisfy the equality.
+Nonetheless, we will do our best to mitigate these issues and apply a good
+heuristic to find $d_j$. First, we rearrange our equation so that we can apply
+a root-finding approximation algorithm to it:
 \begin{equation}
-  d_j = \sqrt{ ( x_j.x - x_i.x )^2 + ( x_j.y - x_i.y )^2 }. \label{eq:dists}
+  f(d_j) = \sqrt{(x_j(d_j) - x_i)^2 + (y_j(d_j) - y_i)^2} - d_j. \label{eq:dj}
 \end{equation}
-Obviously, this is a rather difficult equation to truly solve, so we must only
-heuristically find a solution. Luckily, we
-have a fairly small search space, since $d - d_i > d_j > 0$. On the other hand,
-it is not readily apparent how these solutions will behave. We can, however,
-be certain that it is continuous, so we can proceed as follows:
-\begin{enumerate}
-\item Check if the optimal solution would require that we move around the loop
-  again. This will happen if
-  \[d_i+\sqrt{(x_0.x-x_i.x)^2+(x_0.y-x_i.y)^2} > d.\]
-  In this case, we set $x_j = x_0$, and stop searching.
-\item \emph{NEEDS MORE WORK}
-\end{enumerate}
+This simply allows the $d_j$ we are looking for to be the zero of the function.
+The first exciting bit of news is that for most solutions of this equation with
+$d_j < d$, it will work out that $f(0) > 0$ and $f(d-d_i) < 0$.
+We know that $f(0) \geq 0$ by the
+positivity of norms, and the square root of the sum of the squares is the
+euclidian norm. We also can be certain that $f(d-d_i) < 0$ since
+the norm is also unable to change by more than the diameter
+of the ideal loop, or even less based on the proximity of $x_i$ to the center of
+the loop. In situations where $f(d-d_i) > 0$, we notice that the distance to the
+start of the loop is further away than the amount of distance we have left to
+travel; this means that we should just route back to the start anyways. As such,
+we have bounds inside of which we know that there exists a solution. We apply
+Brent's method, a robust root approximation algorithm, to determine the solution
+inside of this zone. The idea behind Brent's method is to combine the bisection
+method, the secant method, and inverse quadratic interpolation. Readers
+unfamiliar with any of these techniques should refer to CITATIONS. Some
+pseudocode is given for Brent's Method in Algorithm~\ref{alg:brent}. The idea
+is this:
 
-At this point, we have found $x_j$. From here, calculating $\theta$ is fairly
-straightforward:
+First, we need a bracket in which our function has a root. For us, this is
+simple enough; we just use $[0, d-d_i]$. If that bracket does not satisfy the
+condition, we just set $d_j = d-d_i$ and don't bother with anything.
+
+The algorithm details out the actual swapping of $a_k$ and $b_k$, but here
+we'll just assume that $|f(a_k)| > |f(b_k)|$ at all points in time; that is,
+$b_k$ is a better approximation of the solution than $a_k$. We also require
+$b_{k-1}$; for now, we'll set it to $a_k$.
+
+This is a heuristic, so we'll keep repeating the algorithm until either
+$a_k \approx b_k$ or $f(b_k) \approx 0$. At the $k^{\mbox{{\tiny th}}}$ iteration,
+we'll calculate $b_{k+1}$ using both inverse quadratic interpolation and the
+bisection method.
+
+In general, the inverse quadratic interpolation can proceed very quickly, but we
+add the bisection method to ensure convergence. In using interpolation, one of
+the following conditions must be satisfied:
+\begin{itemize}
+\item Inverse Quadratic Interpolation was performed last time,
+  \[ |s - b_k| < \left|\frac{b_{k-1}-b_{k-2}}{2}\right|, \]
+  and
+  \[|\delta| < |b_{k-1} - b_{k-2}| \]
+\item The Bisection Method was used last time,
+  \[|s - b_k| < \left|\frac{b_k-b_{k-1}}{2}\right|, \]
+  and
+  \[ |\delta| < |b_k - b_{k-1}| \]
+\end{itemize}
+The rest of the pseudocode serves only to ensure that variables are assigned
+correctly. One notes that mflag indicates whether interpolation was used last
+time or not.
+
+\begin{algorithm}
+  \caption{Using Brent's Method to find a zero of a function}
+  \label{alg:brent}
+  \begin{algorithmic}
+    \Require $f(a_0)f(b_0) > 0$
+    \Function{Brent}{$f : [a,b] \to \mathbb{R}$, $a_0$, $b_0$}
+      \If{$|f(a_0)| < |f(b_0)|$}
+        \Call{swap}{$a_0$,$b_0$}
+      \EndIf
+      \State $b_{k-1} \gets a_0$
+      \State mflag $\gets$ True
+      \While{$f(b_k) \not = 0$ {\bf and} $|b_k - a_k| > \epsilon$}
+      \begin{align*}
+        s \gets &\frac{a_kf(b_k)f(b_{k-1})}{(f(a_k)-f(b_k))(f(a_k)-f(b_{k-1}))} \\
+        & + \frac{b_kf(a_k)f(b_{k-1})}{(f(b_k)-f(a_k))(f(b_k)-f(b_{k-1}))} \\
+        & + \frac{b_{k-1}f(a_k)f(b_k)}{(f(b_{k-1})-f(a_k))(f(b_{k-1})-f(b_k))}
+      \end{align*}
+      \State {\bf if} $\displaystyle s \not \in \left[ \frac{3a_k+b_k}{4},b_k \right]$
+             {\bf or}
+             \State ~~~~(mflag is True {\bf and}
+             \State ~~~~~~~~ ($\displaystyle |s-b_k| \geq \frac{|b_k-b_{k-1}|}{2}$
+             \State ~~~~~~~~~~ {\bf or} $|b_k-b_{k-1}| < |\delta|$)) {\bf or}
+             \State ~~~~(mflag is False {\bf and}
+             \State ~~~~~~~~ ($\displaystyle |s-b_k| \geq \frac{|b_{k-1}-b_{k-2}|}{2}$
+             \State ~~~~~~~~~~ {\bf or} $|b_{k-1}-b_{k-2}| < |\delta|$)) {\bf then}
+             \State ~~~~ $\displaystyle s \gets \frac{a_k+b_k}{2}$
+             \State ~~~~ mflag $\gets$ True
+             \State {\bf else}
+             \State ~~~~ mflag $\gets$ False
+        \State $b_{k-2} \gets b_{k-1}$
+        \State $b_{k-1} \gets b_k$
+        \If{$f(a_k)f(s) < 0$}
+          \State $b_k \gets s$
+        \Else
+          \State $a_k \gets s$
+        \EndIf
+        \If{$|f(a_k)| < |f(b_k)|$}
+          \Call{swap}{$a_k$,$b_k$}
+        \EndIf
+      \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+Thus, by utilizing Brent's Algorithm, we can find $x_j$. From here, calculating
+$\theta$ is fairly straightforward:
 \begin{align}
-  \tan \theta = & \frac{x_j.y - x_i.y}{x_j.x-x_i.x} \notag \\
-  \theta = & \tan^{-1} \frac{x_j.y - x_i.y}{x_j.x-x_i.x} \label{eq:theta}
+  \tan \theta = & \frac{y_j - y_i}{x_j-x_i} \notag \\
+  \theta = & \tan^{-1} \frac{y_j - y_i}{x_j-x_i} \label{eq:theta}
 \end{align}
@@
 Finally, we have a method for calculating the weights based on distance and
-direction! Use \eqref{eq:xjx}, \eqref{eq:xjy}, and \eqref{eq:dists} to find
-an $x_j$, and plug into \eqref{eq:theta} to find a $\theta$. Finally, use
-$\theta$ in conjunction with \eqref{eq:weight} to assign weights to
-directions.
+direction! Use Brent's algorithm as described in Algorithm~\ref{alg:brent}
+with the function to be zeroed as \eqref{eq:dj}. Use that $d_j$ in conjunction
+with \eqref{eq:xj} and \eqref{eq:yj} to find
+$x_j$ and $y_j$, respectively, and plug into \eqref{eq:theta} to find a
+$\theta$. Finally, use $\theta$ in conjunction with \eqref{eq:weight} to assign
+weights to directions.
 

### 2013-11-18 pyroute/events.py

@@ -125,12 +125,11 @@ class pyrouteEvents(pyrouteModule):
       lat,lon = self.get('clicked')
     else:
       lat, lon = [float(ll) for ll in params.split(':',1)]
-
-    transport = self.get('mode')
-
+    transport = 'cycle'
     router = self.m['route']
     router.setStartLL(lat, lon, transport)
     router.setMode('cycle')
+    router.setDistEle(float(raw_input()),int(raw_input()))
     router.update()
     self.set('needRedraw', True)
 

### 2013-11-18 pyroute/routeOrDirect.py

@@ -26,6 +26,9 @@ class RouteOrDirect(Router, Grower):
         self.route['endnode'] = self.data.findNode(lat,lon,transport)
         self.route['endpos'] = (lat,lon)
         self.route['transport'] = transport
+    def setDistEle(self, distGain, elevationGoal):
+        self.route['distance'] = distGain
+        self.route['ascent'] = elevationGoal
     def update(self):
         if(self.mode == 'route'):
             result, newroute = self.doRouteAsLL(self.route['startnode'],
@@ -44,17 +47,11 @@ class RouteOrDirect(Router, Grower):
             self.route['route'].append(self.route['endpos'])
             self.route['valid'] = True
         elif self.mode == 'cycle':
-            self.route['route'] = []
-            result, newroute = self.growCycleAsLL(self.route['startnode'],
-                                                  20,
-                                                  0,
-                                                  0,
-                                                  self.route['transport'])
-            if result == 'success':
-                self.route['route'] = newroute
-                self.route['valid'] = True
-            else:
-                self.route['valid'] = False
-
+            (self.route['valid'],
+             self.route['route']) = self.growCycleAsLL(self.route['startnode'],
+                                                       self.route['distance'],
+                                                       self.route['ascent'],
+                                                       0)
+            print self.route['route']
     def valid(self):
         return(self.route['valid'])

### 2013-11-19 paper.tex
More 2d - 3d conversions...

@@
 and the algorithm does its best to direct you along that loop. See
-Figure~\ref{fig:ideal} for an example of what this might look like.
+Figure~\ref{fig:ideal} for an example of what this might look like.In order to
+direct you along this loop, weights are generated based on
+direction. We'll consider the method for finding the optimal direction,
+$\theta$.
 
@@
 
-In order to direct you along this loop, weights are generated based on
-direction. We'll consider the method for finding the optimal direction,
-$\theta$, briefly. First, consider how the weights are generated once
+\subsubsection{Calculating the Weights}
+
+First, consider how the weights are generated once
 that direction is discovered. Basically, there is a weighted compass oriented
@@
 \end{equation}
+
+\subsubsection{Calculating the Ideal Loop}
 
@@
 To satisfy our constraint, we have
-\[ d_j = \sqrt{ ( x_j(d_j) - x_i )^2 + ( x_j(d_j) - x_i )^2 }. \]
+\begin{equation}
+d_j = \sqrt{ ( x_j(d_j) - x_i )^2 + ( x_j(d_j) - x_i )^2 }. \label{eq:dj}
+\end{equation}
 
@@
 a root-finding approximation algorithm to it:
-\begin{equation}
-  f(d_j) = \sqrt{(x_j(d_j) - x_i)^2 + (y_j(d_j) - y_i)^2} - d_j. \label{eq:dj}
-\end{equation}
+\[ f(d_j) = \sqrt{(x_j(d_j) - x_i)^2 + (y_j(d_j) - y_i)^2} - d_j. \]
 This simply allows the $d_j$ we are looking for to be the zero of the function.
@@
 In general, the inverse quadratic interpolation can proceed very quickly, but we
-add the bisection method to ensure convergence. In using interpolation, one of
-the following conditions must be satisfied:
-\begin{itemize}
-\item Inverse Quadratic Interpolation was performed last time,
-  \[ |s - b_k| < \left|\frac{b_{k-1}-b_{k-2}}{2}\right|, \]
-  and
-  \[|\delta| < |b_{k-1} - b_{k-2}| \]
-\item The Bisection Method was used last time,
-  \[|s - b_k| < \left|\frac{b_k-b_{k-1}}{2}\right|, \]
-  and
-  \[ |\delta| < |b_k - b_{k-1}| \]
-\end{itemize}
+add the bisection method to ensure convergence. In order to use interpolation,
+we require that a few conditions are satisfied. Namely, $s$ has to be in a certain
+interval, and the iterates need to obey certain bounds.
+
 The rest of the pseudocode serves only to ensure that variables are assigned
-correctly. One notes that mflag indicates whether interpolation was used last
-time or not.
+correctly. One notes that $B$ indicates whether the bisection method was used
+on the previous iteration.
 
@@
       \State $b_{k-1} \gets a_0$
-      \State mflag $\gets$ True
+      \State $B \gets$ True \Comment{bisected last time?}
       \While{$f(b_k) \not = 0$ {\bf and} $|b_k - a_k| > \epsilon$}
-      \begin{align*}
-        s \gets &\frac{a_kf(b_k)f(b_{k-1})}{(f(a_k)-f(b_k))(f(a_k)-f(b_{k-1}))} \\
-        & + \frac{b_kf(a_k)f(b_{k-1})}{(f(b_k)-f(a_k))(f(b_k)-f(b_{k-1}))} \\
-        & + \frac{b_{k-1}f(a_k)f(b_k)}{(f(b_{k-1})-f(a_k))(f(b_{k-1})-f(b_k))}
-      \end{align*}
-      \State {\bf if} $\displaystyle s \not \in \left[ \frac{3a_k+b_k}{4},b_k \right]$
-             {\bf or}
-             \State ~~~~(mflag is True {\bf and}
-             \State ~~~~~~~~ ($\displaystyle |s-b_k| \geq \frac{|b_k-b_{k-1}|}{2}$
-             \State ~~~~~~~~~~ {\bf or} $|b_k-b_{k-1}| < |\delta|$)) {\bf or}
-             \State ~~~~(mflag is False {\bf and}
-             \State ~~~~~~~~ ($\displaystyle |s-b_k| \geq \frac{|b_{k-1}-b_{k-2}|}{2}$
-             \State ~~~~~~~~~~ {\bf or} $|b_{k-1}-b_{k-2}| < |\delta|$)) {\bf then}
-             \State ~~~~ $\displaystyle s \gets \frac{a_k+b_k}{2}$
-             \State ~~~~ mflag $\gets$ True
-             \State {\bf else}
-             \State ~~~~ mflag $\gets$ False
-        \State $b_{k-2} \gets b_{k-1}$
-        \State $b_{k-1} \gets b_k$
-        \If{$f(a_k)f(s) < 0$}
-          \State $b_k \gets s$
-        \Else
-          \State $a_k \gets s$
-        \EndIf
       \If{$|f(a_k)| < |f(b_k)|$}
@@
       \EndIf
+      \State $b_{k+1} \gets$\Call{inv\_quad\_interp}{$f,a_k,b_k,b_{k-1}$}
+      \State $B$ $\gets$ \Call{need\_bisect}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
+      \If{$B$}
+        \State $\displaystyle b_{k+1} \gets \frac{a_k+b_k}{2}$ \Comment{bisection method}
+      \EndIf
+      \State $b_{k-2} \gets b_{k-1}$
+      \State $b_{k-1} \gets b_k$
+      \If{$f(a_k)f(s) < 0$}~~$b_k \gets s$
+      \Else~~$a_k \gets s$
+      \EndIf
       \EndWhile
+    \EndFunction
+  \end{algorithmic}
+  \begin{algorithmic}
+    \Function{need\_bisect}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
+      \If{$\displaystyle b_{k+1} \not \in \left[ \frac{3a_k+b_k}{4},b_k \right]$}
+      \State \Return True
+      \ElsIf{$B$ is True}
+      \State \Return
+        $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_k-b_{k-1}|}{2}$
+      \State ~~~~~~~~~~~$\land$~~$|b_k-b_{k-1}| < |\delta|$
+      \Else~
+      \Return $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_{k-1}-b_{k-2}|}{2}$
+      \State ~~~~~~~~~~~~~~$\land$~~$|b_{k-1}-b_{k-2}| < |\delta|$
+      \EndIf
+    \EndFunction
+  \end{algorithmic}
+  \begin{algorithmic}
+    \Function{inv\_quad\_interp}{$f$,$a$,$b$,$c$}
+      \If{$f(a) \not= f(c)$ {\bf and} $f(b) \not= f(c)$}
+        \State \Return $\displaystyle \frac{af(b)f(c)}{(f(a)-f(b))(f(a)-f(c))}$
+        \State ~~~~~~~~~~~$\displaystyle + \frac{bf(a)f(c)}{(f(b)-f(a))(f(b)-f(c))}$
+        \State ~~~~~~~~~~~$\displaystyle + \frac{cf(a)f(b)}{(f(c)-f(a))(f(c)-f(b))}$
+      \Else
+        \State \Return $\displaystyle b - f(b)\frac{b-a}{f(b)-f(a)}$
+      \EndIf
     \EndFunction
@@
 
-\subsection{Weight for Elevation Gain}
-
-Now that weights have been assigned based on distance and direction, we can
-move on to worrying about elevation gain.
-
-FILL IN THIS SECTION
-
 \subsection{Miscellaneous Weights}
@@
 
+Now that we have developed all of the weight calculations, we can consider using
+them to generate a route. Algorithm~\ref{alg:grow} lays out the basic idea in
+pseudocode. It omits definitions for many of the functions because they were
+covered in sufficient detail in previous sections. The general procedure is
+to loop until the algorithm returns to the start point after at least 90\%
+of the distance, $d$ is travelled. At each iteration, $\theta$ will be
+calculated using \eqref{eq:theta}, where $(x_j,y_j)$ are calculated by applying
+Algorithm~\ref{alg:brent} on \eqref{eq:dj}. Once $\theta$ is calculated, a
+weight is generated for each node adjacent to $x_i$, and one of the nodes is
+selected at random based on their weights.
+
+\begin{algorithm}[t!]
+  \caption{Calculating a Route} \label{alg:grow}
+  \begin{algorithmic}
+    \Require \Call{edges}{} finds adjacent nodes and \Call{random}{} generates
+    a random number in the given range.
+    \Function{grow\_cycle}{$x_0$,$d$,$e$,$\phi$}
+    \State $X \gets \{\}$ \Comment{the route}
+    \State $d_k \gets 0$
+    \State $\theta \gets \phi$
+
+    \While{$x_{k}\not = x_0$ {\bf or} $d_k < 0.9d$}
+      \State $\theta \gets$ \Call{get\_theta}{}
+
+      \State $w \gets 0$ \Comment{sum of all weights}
+      \For{$x \in$ \Call{edges}{$x_k$}}
+        \State $w \gets w +$\Call{weight}{$x$}
+      \EndFor
+      \State $q \gets$ \Call{random}{$[0,w]$} \Comment{to choose node}
+      \For{$x \in$ \Call{edges}{$x_k$}}
+        \If{$q < $ \Call{weight}{$x$,$\theta$}}
+          \State $x_{k+1} \gets x$
+          \State $d_{k+1} \gets d_k +$\Call{dist}{$x_k$,$x_{k+1}$}
+          \State $X \gets X \cup \{x_{k+1}\}$
+          \State break
+        \Else~$q \gets q -$\Call{weight}{$x$,$\theta$}
+        \EndIf
+      \EndFor
+    \EndWhile
+    \State \Return $X$
+  \EndFunction
+
+  \end{algorithmic}
+\end{algorithm}
+
 \section{Moving to Three Dimensions} \label{sec:latlong}
+
+\subsection{Distance Calculations}
+As mentioned earlier, using the Euclidian norm for latitudes and longitudes
+is highly inaccurate; latitudes and longitudes are more similar to 3D polar
+coordinates with a fixed $r$ than they are to a coordinate plane. The
+haversine formula is used to calculate distances between two points on the
+surface of a sphere. The haversine formula uses the haversin function,
+which is defined as follows:
+\newcommand{\haversin}{\mbox{haversin}}
+\[ \haversin (\theta) = \sin^2(\frac{\theta}{2}). \]
+Given two coordinate pairs, $(\phi_1, \lambda_1)$ and $(\phi_2, \lambda_2)$,
+and a radius, $r$, the haversine formula calculates the distance $d$ between
+the two coordinate pairs:
+\begin{align*}
+  d = r\haversin^{-1}(&\haversin(\phi_2 - \phi_1) + \\
+  & \cos(\phi_1)\cos(\phi_2)\haversin(\lambda_2 -\lambda_1)
+\end{align*}
+Using the definition of the haversin function, this can be reduced into a
+function in terms of elementary trigonometric functions. The only non-trivial
+thing to note is that $\haversin^{-1}(x) = 2\sin^{-1}(\sqrt{x})$. Armed with
+this knowledge, it is fairly easy to reduce. We'll use an intermediate variable
+to hold the value under the square root:
+\begin{align*}
+  h = & \haversin(\phi_2-\phi_1) + \\
+  & \cos(\phi_1)\cos(\phi_2)\haversin(\lambda_2-\lambda_1) \\
+  = & \sin^2\left(\frac{\phi_2 - \phi_1}{2}\right) + \\
+  & \cos(\phi_1)\cos(\phi_2)\sin^2\left(\frac{\lambda_2-\lambda_1}{2}\right)\\
+  d = & r\haversin^{-1}\left(\sqrt{h}\right) \\
+  = & 2r\sin^{-1}\left(\sqrt{h}\right)
+\end{align*}
+By simply substituting this as the right hand side of \eqref{eq:dj}, many of the
+projection issues can be avoided.
+
+\subsection{Ideal Loop Calculation}
+
+However, the actual ideal loop and, consequently,
+\eqref{eq:xj} and \eqref{eq:yj} depend on a set of parametric equations along
+a cartesian coordinate plane. These are an inaccurate representation of the
+intended ideal loop; as the loop progresses further from the equator, it will
+become increasingly squashed in the east/west direction.
+
+To find the proper loop, a cone must be projected from the origin of the sphere,
+and the intersection of the cone and the sphere can be used to calculate the
+ideal loop. The following equation describes a cone,
+\[ 0 = (u \cdot d)^2 - |d||u|\cos \phi , \]
+where $u= (x,y,z)$, $d = (a,b,c)$ is a vector parallel to the axis of the
+cone, and $\phi$ is one-half the aperture of the cone. Additionally, recall
+the equation for a sphere:
+\[ r = |u|. \]
+Unfortunately, both of these equations are of little aid, since they require
+input in the form of cartesian coordinates. We would like to convert these to
+a set of equations in spherical form. However, these equations become rather
+complicated; for now, we've accepted the projected sphere as ``good enough.''
 
@@
 to generate the routes will likely improve the algorithm.
+
+Unfortunately, the API we used for OSM did not have easy access to elevation
+data, something that would have also proved very useful to cyclists. A more
+robust implementation of this algorithm would also find the elevation data of
+every coordinate and use this information to augment the weights.
 

### 2013-11-19 paper.tex
Added a few images to the writeup.

@@
 
+As mentioned earlier, using the Euclidian norm for latitudes and longitudes
+is highly inaccurate; latitudes and longitudes are spherical coordinates with
+fixed $r$, so considering the latitude and longitude to be $x$ and $y$ values is
+a very flawed idea. As one can see in Figure~\ref{fig:sphere}, the contrast is
+stark. Latitude and longitudes are angles, not positions in space.
+
+\begin{figure}
+  \includegraphics[width=3in]{images/558px-3D_Spherical.png}
+  \caption{The Spherical Coordinate System} \label{fig:sphere}
+\end{figure}
+
 \subsection{Distance Calculations}
-As mentioned earlier, using the Euclidian norm for latitudes and longitudes
-is highly inaccurate; latitudes and longitudes are more similar to 3D polar
-coordinates with a fixed $r$ than they are to a coordinate plane. The
-haversine formula is used to calculate distances between two points on the
+The haversine formula is used to calculate distances between two points on the
 surface of a sphere. The haversine formula uses the haversin function,
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=2in]{images/220px-Numerical_aperture.png}
+  \caption{The aperture of a cone} \label{fig:aperture}
+\end{figure}
 To find the proper loop, a cone must be projected from the origin of the sphere,
@@
 where $u= (x,y,z)$, $d = (a,b,c)$ is a vector parallel to the axis of the
-cone, and $\phi$ is one-half the aperture of the cone. Additionally, recall
+cone, and $\phi$ is one-half the aperture of the cone. In
+Figure~\ref{fig:aperture}, the $\theta$ pictured is the same as the $\phi$ in
+this equation. Additionally, recall
 the equation for a sphere:
 \[ r = |u|. \]
-Unfortunately, both of these equations are of little aid, since they require
+For the most part, we can consider $r = 1$, since we are dealing with the
+surface of a sphere. However, we do have to make certain calculations using
+the actual radius of the earth. For example, in order to calculate the
+aperture $\phi$, we realize that the length of the sides of the cone will be the
+radius of the earth. Then $\sin \phi = \frac{r_c}{r}$, so we can calculate
+$\phi$ as follows:
+\begin{equation}
+  \phi = \sin^{-1} \left( \frac{\frac{d}{2\pi}}{r} \right) \label{eq:phi}
+\end{equation}
+
+Unfortunately, the equations for spheres and cones are of little aid, since
+they require
 input in the form of cartesian coordinates. We would like to convert these to
 a set of equations in spherical form. However, these equations become rather
-complicated; for now, we've accepted the projected sphere as ``good enough.''
+complicated; for now, we've accepted the projected circle as ``good enough.''
 

### 2013-12-03 paper.tex
Serious updates to the paper.

@@
-\documentclass[twocolumn,11pt]{article}
+\documentclass[twocolumn,12pt]{article}
 
@@
 \usepackage{amsmath}
+\usepackage{bm}
 \usepackage{graphicx}
 \usepackage{epstopdf}
+\usepackage{hyperref}
+\usepackage{natbib}
 \usepackage{tikz}
@@
 \usepackage[toc,page]{appendix}
-\usepackage{url}
 
@@
 
+\newcommand{\mycite}[1]{[\citenum{#1}]}
+
 \begin{abstract}
@@
 
-\section{Background}
+\section{Background} \label{sec:back}
 
@@
 the maps themselves and to various (mostly open-source) software projects that
-utilize the format. More information on this format can be found on their
-website, openstreetmap.org.
+utilize the format. The interested reader should refer to \citenum{wik:osm} for
+almost all information regarding OSM, including how to contribute, how to use,
+and links to projects that utilize OSM instead of proprietary mapping software.
 
@@
 allows easy utilization of the Pyroute tools for GUI setup and OSM download
-while also making it rather explicit where the navigation functions are. The
-OSM wiki pages have a good deal of information
-on Pyroute and PyrouteLib; refer to them for more information.
+while also making it rather explicit where the navigation functions are.
+Notably, pyroute has generally been abandoned in favor of the more advanced
+Open Source Routing Machine (OSRM) project, but pyroute was chosen for this
+paper instead due to its relative ease of prototyping and intuitiveness. Readers
+interested in OSRM should refer to \mycite{wik:osrm}; those interested in
+pyroute can sate their interest with \mycite{wik:pyroute}. One notes that
+pyroute uses the relatively simple $A^*$ algorithm for routing between two
+points. This is a slower implementation than OSRM, but our usage of the actual
+routing algorithm is minimal; for the most part, we use pyroute only for loading
+maps and displaying routes on them.
 
@@
 and the algorithm does its best to direct you along that loop. See
-Figure~\ref{fig:ideal} for an example of what this might look like.In order to
+Figure~\ref{fig:ideal} for an example of what this might look like. In order to
 direct you along this loop, weights are generated based on
@@
 $\theta$.
+
+\subsubsection{Calculating the Weights}
 
@@
 \end{figure}
-
-\subsubsection{Calculating the Weights}
 
@@
     \filldraw (0,0) circle(0.05);
-    \node at (0.4,0.1) {$x_0$};
+    \node at (0.4,0.1) {$\bm{x_0}$};
 
@@
     \filldraw (4,0) circle(0.05);
-    \node at (4.2,0.2) {$x_j$};
+    \node at (4.2,0.2) {$\bm{x_j}$};
 
-    \node at (1.8,-0.7) {$x_i$};
-    \node at (2.7,-1.4) {$x_{\mbox{{\tiny ideal}}}$};
+    \node at (1.8,-0.7) {$\bm{x_i}$};
+    \node at (2.7,-1.4) {$\bm{x}_{\mbox{{\tiny ideal}}}$};
 
@@
 The next step is to utilize these equations to calculate $\theta$. At any point
-along the algorithm, we are at some $x_i$, and we have travelled a distance,
-$d_i$. Figure~\ref{fig:algvals} should help to understand what exactly the
-algorithm is attempting to achieve. The idea is this: if we have travelled some
-distance $d_i$, then there is an $x_{\mbox{{\tiny ideal}}}$ on the ``ideal''
-loop. The arc between $x_{\mbox{{\tiny ideal}}}$ and $x_0$ will be of length
-$d_i$. The algorithm searches for a point $x_j$ such that the arc between
-$x_{\mbox{{\tiny ideal}}}$ and $x_j$ will have the \emph{same} distance as the
-line between $x_i$ and $x_j$. Fortunately, we have framed the equations for
-calculating $x_j$ in terms of the distance travelled along the arc, and the
-distance between $x_i$ and $x_j$ can easily be calculated using the pythagorean
-theorem. Note that we find $x_j$ as follows:
+along the algorithm, we are at some $\bm{x_i}$, and we have travelled a
+distance, $d_i$. Figure~\ref{fig:algvals} should help to understand what exactly
+the algorithm is attempting to achieve. The idea is this: if we have travelled
+some distance $d_i$, then there is an $\bm{x}_{\mbox{{\tiny ideal}}}$ on then
+``ideal'' loop. The arc between $\bm{x}_{\mbox{{\tiny ideal}}}$ and $\bm{x_0}$
+will be of length $d_i$. The algorithm searches for a point $x_j$ such that the
+arc between $\bm{x}_{\mbox{{\tiny ideal}}}$ and $\bm{x_j}$ will have the
+\emph{same} distance as the line between $\bm{x_i}$ and $\bm{x_j}$. Fortunately,
+we have framed the equations for calculating $\bm{x_j}$ in terms of the distance
+travelled along the arc, and the distance between $\bm{x_i}$ and $\bm{x_j}$ can
+easily be calculated using the pythagorean theorem. Note that we find $\bm{x_j}$
+as follows:
 \begin{align}
@@
 method, the secant method, and inverse quadratic interpolation. Readers
-unfamiliar with any of these techniques should refer to CITATIONS. Some
-pseudocode is given for Brent's Method in Algorithm~\ref{alg:brent}. The idea
+unfamiliar with any of these techniques should refer to \mycite{wik:sec},
+\mycite{wik:bisect}, \mycite{wik:invquad}, \mycite{wik:brent} for a brief
+overview of the techniques. A more interested reader might consider
+\mycite{sauanal} for an in-depth analysis of the techniques as well as some
+context for using and understanding them. Some pseudocode is given for Brent's
+Method in Algorithm~\ref{alg:brent}, with some helper functions in
+Algorithm~\ref{alg:bhelp}. The idea
 is this:
+
+\begin{algorithm}[t]
+  \caption{Using Brent's Method to find a zero of a function}
+  \label{alg:brent}
+  \begin{algorithmic}
+    \Require $f(a_0)f(b_0) > 0$
+    \Function{Brent}{$f : [a,b] \to \mathbb{R}$, $a_0$, $b_0$}
+      \If{$|f(a_0)| < |f(b_0)|$}
+        \State \Call{swap}{$a_0$,$b_0$}
+      \EndIf
+      \State $b_{k-1} \gets a_0$
+      \State $B \gets$ True \Comment{bisected last time?}
+      \While{$f(b_k) \not = 0$ {\bf and} $|b_k - a_k| > \epsilon$}
+      \If{$|f(a_k)| < |f(b_k)|$}
+        \State \Call{swap}{$a_k$,$b_k$}
+      \EndIf
+      \State $b_{k+1} \gets$\Call{inv\_quad\_interp}{$f,a_k,b_k,b_{k-1}$}
+      \State $B$ $\gets$ \Call{nds\_bi}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
+      \If{$B$} \Comment{use bisection method}
+        \State $\displaystyle b_{k+1} \gets \frac{a_k+b_k}{2}$
+      \EndIf
+      \State $b_{k-2} \gets b_{k-1}$
+      \State $b_{k-1} \gets b_k$
+      \If{$f(a_k)f(s) < 0$}
+        \State $b_k \gets s$
+      \Else
+        \State $a_k \gets s$
+      \EndIf
+      \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+\begin{algorithm}[t!]
+  \caption{Helper functions for Brent's method} \label{alg:bhelp}
+  \begin{algorithmic}
+    \State \Comment{\emph{Determines whether to use bisection~~~~~~~}}
+    \State \Comment{\emph{method or inverse quadratic~~~~~~~~~~~~~~~~~}}
+    \State \Comment{\emph{interpolation~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
+    \Function{nds\_bi}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
+      \If{$\displaystyle b_{k+1} \not \in \left[ \frac{3a_k+b_k}{4},b_k \right]$}
+      \State \Return True
+      \ElsIf{$B$ is True}
+      \State \Return
+        $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_k-b_{k-1}|}{2}$
+      \State ~~~~~~~~~~~$\land$~~$|b_k-b_{k-1}| < |\delta|$
+      \Else
+      \State \Return $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_{k-1}-b_{k-2}|}{2}$
+      \State ~~~~~~~~~~~$\land$~~$|b_{k-1}-b_{k-2}| < |\delta|$
+      \EndIf
+    \EndFunction
+  \end{algorithmic}
+  \begin{algorithmic}
+    \State \Comment{\emph{returns the next iterate under inverse~~~~~}}
+    \State \Comment{\emph{quadratic interpolation~~~~~~~~~~~~~~~~~~~~~~~~~}}
+    \Function{inv\_quad\_interp}{$f$,$a$,$b$,$c$}
+      \If{$f(a) \not= f(c)$ {\bf and} $f(b) \not= f(c)$}
+        \State \Return $\displaystyle \frac{af(b)f(c)}{(f(a)-f(b))(f(a)-f(c))}$
+        \State ~~~~~~~~~~~$\displaystyle + \frac{bf(a)f(c)}{(f(b)-f(a))(f(b)-f(c))}$
+        \State ~~~~~~~~~~~$\displaystyle + \frac{cf(a)f(b)}{(f(c)-f(a))(f(c)-f(b))}$
+      \Else
+        \State \Return $\displaystyle b - f(b)\frac{b-a}{f(b)-f(a)}$
+      \EndIf
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 
@@
 $b_k$ is a better approximation of the solution than $a_k$. We also require
-$b_{k-1}$; for now, we'll set it to $a_k$.
+$b_{k-1}$; at the beginning, $a_k$ will suffice instead.
 
@@
 on the previous iteration.
-
-\begin{algorithm}
-  \caption{Using Brent's Method to find a zero of a function}
-  \label{alg:brent}
-  \begin{algorithmic}
-    \Require $f(a_0)f(b_0) > 0$
-    \Function{Brent}{$f : [a,b] \to \mathbb{R}$, $a_0$, $b_0$}
-      \If{$|f(a_0)| < |f(b_0)|$}
-        \Call{swap}{$a_0$,$b_0$}
-      \EndIf
-      \State $b_{k-1} \gets a_0$
-      \State $B \gets$ True \Comment{bisected last time?}
-      \While{$f(b_k) \not = 0$ {\bf and} $|b_k - a_k| > \epsilon$}
-      \If{$|f(a_k)| < |f(b_k)|$}
-      \Call{swap}{$a_k$,$b_k$}
-      \EndIf
-      \State $b_{k+1} \gets$\Call{inv\_quad\_interp}{$f,a_k,b_k,b_{k-1}$}
-      \State $B$ $\gets$ \Call{need\_bisect}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
-      \If{$B$}
-        \State $\displaystyle b_{k+1} \gets \frac{a_k+b_k}{2}$ \Comment{bisection method}
-      \EndIf
-      \State $b_{k-2} \gets b_{k-1}$
-      \State $b_{k-1} \gets b_k$
-      \If{$f(a_k)f(s) < 0$}~~$b_k \gets s$
-      \Else~~$a_k \gets s$
-      \EndIf
-      \EndWhile
-    \EndFunction
-  \end{algorithmic}
-  \begin{algorithmic}
-    \Function{need\_bisect}{$a_k$,$b_{k-2}$,$b_{k-1}$,$b_k$,$b_{k+1}$,$B$}
-      \If{$\displaystyle b_{k+1} \not \in \left[ \frac{3a_k+b_k}{4},b_k \right]$}
-      \State \Return True
-      \ElsIf{$B$ is True}
-      \State \Return
-        $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_k-b_{k-1}|}{2}$
-      \State ~~~~~~~~~~~$\land$~~$|b_k-b_{k-1}| < |\delta|$
-      \Else~
-      \Return $\displaystyle |b_{k+1}-b_k| \geq \frac{|b_{k-1}-b_{k-2}|}{2}$
-      \State ~~~~~~~~~~~~~~$\land$~~$|b_{k-1}-b_{k-2}| < |\delta|$
-      \EndIf
-    \EndFunction
-  \end{algorithmic}
-  \begin{algorithmic}
-    \Function{inv\_quad\_interp}{$f$,$a$,$b$,$c$}
-      \If{$f(a) \not= f(c)$ {\bf and} $f(b) \not= f(c)$}
-        \State \Return $\displaystyle \frac{af(b)f(c)}{(f(a)-f(b))(f(a)-f(c))}$
-        \State ~~~~~~~~~~~$\displaystyle + \frac{bf(a)f(c)}{(f(b)-f(a))(f(b)-f(c))}$
-        \State ~~~~~~~~~~~$\displaystyle + \frac{cf(a)f(b)}{(f(c)-f(a))(f(c)-f(b))}$
-      \Else
-        \State \Return $\displaystyle b - f(b)\frac{b-a}{f(b)-f(a)}$
-      \EndIf
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
 
@@
 pedestrian walkways and other unridable roads also get high weights.
+Interestingly, pyroute already sets weights for these values, but these are
+generated based on preferences for navigating; these vary greatly from
+preferences for going out and having a good time. A good example of this is the
+weight that pyroute assigns for cycling on steps, which is not 0. It is
+certainly possible for the cyclist to dismount and climb the steps, but one who
+is riding for fun is highly unlikely to be excited about this prospect.
 
@@
 travelled. Repeatedly riding along the same stretch of road can make a ride
-rather boring, so by weighting against this, it can be avoided.
+rather boring, so by weighting against this, it can be avoided. In order to deal
+with this, the algorithm stores stretches of road that have been travelled and
+halves the weight of any path that the rider has already ridden.
 
-\subsection{Using the Weights Together}
+\subsection{Using the Weights to Generate a Route}
 
@@
 pseudocode. It omits definitions for many of the functions because they were
-covered in sufficient detail in previous sections. The general procedure is
+covered in sufficient detail in previous sections. In particular the function
+for calculating weights is omitted, but it utilizes the algorithms and
+characteristics discussed in previous sections
+The general procedure is
 to loop until the algorithm returns to the start point after at least 90\%
@@
       \For{$x \in$ \Call{edges}{$x_k$}}
-        \State $w \gets w +$\Call{weight}{$x$}
+        \State $w \gets w +$\Call{weight}{$x$,$\theta$}
       \EndFor
-      \State $q \gets$ \Call{random}{$[0,w]$} \Comment{to choose node}
+      \State $q \gets$ \Call{random}{$[0,w]$}
       \For{$x \in$ \Call{edges}{$x_k$}}
@@
 
-\section{Moving to Three Dimensions} \label{sec:latlong}
+\section{Using Spherical Coordinates} \label{sec:latlong}
 
 As mentioned earlier, using the Euclidian norm for latitudes and longitudes
-is highly inaccurate; latitudes and longitudes are spherical coordinates with
-fixed $r$, so considering the latitude and longitude to be $x$ and $y$ values is
-a very flawed idea. As one can see in Figure~\ref{fig:sphere}, the contrast is
-stark. Latitude and longitudes are angles, not positions in space.
+is inaccurate; latitudes and longitudes are spherical coordinates  with
+fixed $r$. As one can see in Figure~\ref{fig:sphere},
+spherical coordinates are the three dimensional
+equivalent of polar coordinates. Unfortunately, this poses two problems,
+since we have only described generating a route around the origin in a two
+dimensional plane. The first problem is switching to a spherical coordinate
+system; the second is switching to three dimensions. Clearly,
+considering the latitude and longitude to be values on a cartesian
+coordinate plane is a flawed idea. Latitudes and longitudes are angles, not
+positions in space.
 
 \begin{figure}
-  \includegraphics[width=3in]{images/558px-3D_Spherical.png}
-  \caption{The Spherical Coordinate System} \label{fig:sphere}
+  \centering
+  \includegraphics[height=2in]{images/sphere.png}
+  \caption{The Spherical Coordinate System~\mycite{img:spher}} \label{fig:sphere}
 \end{figure}
@@
 \subsection{Distance Calculations}
-The haversine formula is used to calculate distances between two points on the
-surface of a sphere. The haversine formula uses the haversin function,
+Fortunately, distances are very well defined under any coordinate system, so we
+can tackle both problems here without much ado. In the spherical coordinate
+system, The haversine formula is used to calculate distances between two points
+on the surface of a sphere. The haversine formula uses the haversin function,
 which is defined as follows:
@@
 and a radius, $r$, the haversine formula calculates the distance $d$ between
-the two coordinate pairs:
+the two coordinate pairs \mycite{wik:haversin}:
 \begin{align*}
@@
 
+ However, it still isn't perfect; the haversine
+formula does not account for variations in the elevation of the earth. Instead,
+it assumes one is travelling at sea level. Additionally, it assumes the earth is
+a perfect sphere, which is also slightly inaccurate. Less accurate formulae
+include flat-surface projection formulae, while more accurate formulae
+generate geodesics along the surface of an ellipsoid that models the earth
+\mycite{wik:dist}. For our purposes, however, the haversine formula will be
+sufficiently accurate.
+
 \subsection{Ideal Loop Calculation}
 
-However, the actual ideal loop and, consequently,
+Distance calculations are the easier half of the problem;
+the actual ideal loop and, consequently,
 \eqref{eq:xj} and \eqref{eq:yj} depend on a set of parametric equations along
-a cartesian coordinate plane. These are an inaccurate representation of the
-intended ideal loop; as the loop progresses further from the equator, it will
-become increasingly squashed in the east/west direction.
+a cartesian coordinate plane. We'll consider a few different methods for
+converting to spherical coordinates.
+
+\subsubsection{A Na\"{i}ve Approach} \label{sec:naiveloop}
+
+The first, and perhaps most obvious, method is to simply use latitude and
+longitude as the $x$ and $y$ in \eqref{eq:xj} and \eqref{eq:yj}. This is
+not a superb solution, but it does have a few advantages, chief of which are
+the relative ease of computation and development. For small loops relatively
+close to the equator, it may even be fairly similar to the intended ideal loop.
+
+However, the larger the loop and the further from the equator the more squashed
+the loop will begin to be. One also notes that the conversion does require a
+slight change to the original formulae: one cannot use $d$ as the radius of the
+circle. Instead, one must use an approximate conversion of the input distance
+to an angular delta. Latitudinal distances change very little (they only
+change because the Earth is an ellipsoid, not a sphere), and, as such, the
+nautical mile was derived as the distance between a minute of latitude
+\mycite{wik:nautmil}. Thus, we can easily convert between a distance goal and an
+approximate latitudinal radius. Unfortunately, this will be dramatically
+incorrect the closer to the poles we get.
+
+\subsubsection{Accurate Approach}
 
@@
   \includegraphics[width=2in]{images/220px-Numerical_aperture.png}
-  \caption{The aperture of a cone} \label{fig:aperture}
+  \caption{The half-aperture of a cone \mycite{img:aperture}} \label{fig:aperture}
 \end{figure}
-To find the proper loop, a cone must be projected from the origin of the sphere,
-and the intersection of the cone and the sphere can be used to calculate the
-ideal loop. The following equation describes a cone,
-\[ 0 = (u \cdot d)^2 - |d||u|\cos \phi , \]
-where $u= (x,y,z)$, $d = (a,b,c)$ is a vector parallel to the axis of the
-cone, and $\phi$ is one-half the aperture of the cone. In
+
+To find the real ideal loop, a cone must be projected from the origin of the
+sphere, and the intersection of the cone and the sphere can be used to calculate
+the ideal loop. Note that this approach, while far superior to the flattened
+approach, still does not compensate for the ellipsoidal nature of the Earth, or
+for the variations in the elevation on the surface of the earth.
+
+The following equation describes a cone:,
+\[ 0 = (\bm{u} \cdot \bm{d})^2 - |\bm{d}|^2|\bm{u}|^2\cos^2 \phi , \]
+where $\bm{u}= (x,y,z)$, $\bm{d} = (a,b,c)$ is a vector parallel to the axis of
+the cone, and $\phi$ is one-half the aperture of the cone \mycite{wik:cones}. In
 Figure~\ref{fig:aperture}, the $\theta$ pictured is the same as the $\phi$ in
-this equation. Additionally, recall
-the equation for a sphere:
-\[ r = |u|. \]
+this equation; we have used $\phi$ instead of the more accepted $\theta$ to
+avoid confusion with the zenith in spherical coordinates.
+Additionally, recall the equation for a sphere:
+\[ r = |\bm{u}|. \]
 For the most part, we can consider $r = 1$, since we are dealing with the
@@
 
-Unfortunately, the equations for spheres and cones are of little aid, since
-they require
-input in the form of cartesian coordinates. We would like to convert these to
-a set of equations in spherical form. However, these equations become rather
-complicated; for now, we've accepted the projected circle as ``good enough.''
+With $r = 1$, we do our best to create an equation for the circle of interest:
+\begin{align*}
+  0 = & (\bm{u}\cdot \bm{d})^2 - |\bm{d}|^2|\bm{u}|^2\cos^2 \phi \\
+    = & (ax + by + cz)^2 - \cos^2 \phi \\
+    = & a^2x^2 + b^2y^2 + c^2z^2 \\
+    & + 2abxy + 2acxz
+     + 2bcyz - \cos^2 \phi \\
+\end{align*}
+
+Unfortunately, these equations for spheres and cones are of little aid. The
+ parametric equations for a circle are inspired by the polar coordinate form
+of a circle, so we convert these equations to spherical form. Ideally, this will
+likewise inspire a set of parametric equations for this circle.
+\begin{align*}
+  0 = & a^2x^2 + b^2y^2 + c^2z^2 \\
+      & 2abxy + 2acxz + 2bcyz - \cos^2 \phi \\
+    = & a^2\cos^2 \psi + b^2\sin^2 \psi + c^2\sin^2 \theta \\
+      & + 2ab\cos \psi\sin \psi + 2ac\cos \psi \sin \theta \\
+      & + 2bc\sin \psi \sin \theta  - \cos \phi
+\end{align*}
+Unfortunately, this doesn't make much headway. Without further inspiration,
+we'll stick with the na\"{i}ve approach discussed in
+Section~\ref{sec:naiveloop}.
 
@@
 
-\section{Discussion}
+At first, the algorithm was rather unsuccessful. The generated weights may have
+been useful, but a few things kept them from being very successful. First, the
+weights were calculated at every node. This means that at every point along a
+road, it would be determined if one should continue down the road or turn around
+and head back in the other direction. Unfortunately, since many roads are rather
+curvy, the weights could often tell the user to oscillate back and forth on a
+single road for an entirely uninteresting ride.
+
+In subsequent iterations of the algorithm, this was noticed and adjusted for;
+instead, the next intersection is found, and the weights are calculated for the
+point at the next intersection. This also allows for weights for previously
+travelled sections of road to be compressed to pairs of nodes for each stretch
+between an intersection.
+
+Another issue arose with the preliminary calculation of $\theta$. At first, a
+much more na\"{i}ve approach was taken. Instead of using Brent's method to find
+the zeroes of \eqref{eq:dj}, the algorithm simply divided the search space into
+one hundred sections and chose the section that was closest.
+
+Another difficult issue was getting the algorithm to terminate. Sometimes the
+algorithm might get stuck in a dead end where $x_0$ is a straight line through
+the dead end as the crow flies, so the algorithm weights continuing down the
+dead end higher. Even if something like this did not happen, the loops were
+almost invariably well above the distance input. In order to avoid this problem,
+the algorithm utilizes point-to-point routing to route back to the start once
+$d_i + \|\bm{x}_0-\bm{x}_i\| > 0.95d$; that is, once the direct distance between
+the current point and the starting point summed with the distance travelled is
+more than 95\% of the distance goal. This allows for both flexibility and
+variation. If the route back to the starting point is direct, the loop will be
+somewhat below the desired distance goal. On the other hand, if the route back
+to the starting point is less direct, the loop will slightly exceed the input
+distance goal.
 
@@
 our best to utilize as much data as possible, expanding the set of data utilized
-to generate the routes will likely improve the algorithm.
+to generate the routes will likely improve the algorithm. Additionally, some
+features were abandoned due to time constraints.
 
@@
 robust implementation of this algorithm would also find the elevation data of
-every coordinate and use this information to augment the weights.
+every coordinate and use this information to augment the weights. This would
+also give rise to some very interesting challenges due to the competing
+interests of elevation and distance.
 
- (ASK DAN FOR THIS
-PAPER) There has been research done into analyzing the probability of accidents
+There has been research done into analyzing the probability of accidents
 on a road based on certain metadata. This metadata is readily available to the
-cities that own the roads, but it is seldom available for direct access inside
-of maps. If this data becomes more readily available, then it can be integrated
-into the application to help increase user safety.
+cities that maintain the roads, but it is beyond the scope of the information
+contained in OSM data or even better-funded mapping applications such as
+Google Maps. Ideally, as time progresses the data will percolate into these
+services; if this data becomes more readily available, then it can be integrated
+into the algorithm to help increase user safety.
 
-Additionally, this has been a facet of a three pronged project developing a
-platform for bicycle training. The other two aspects are developing an Android
-application to track training data during a ride and a website to track
+Additionally, this has been a facet of a three pronged project developing an
+immersive experience for bicycle training. The other two prongs are an
+Android application to track training data during a ride and a website to track
 long-term training data. Ideally, this algorithm will eventually be seamlessly
 integrated into the mobile and web projects, so that routes can be generated
-and sent directly to the application for the user to follow.
+on the web and sent directly to the user's mobile phone for the user to follow
+with the Android application.
 
@@
 the data from the other parts would also provide valuable input for the
-algorithm. One of the most exciting applications of this information is to
-generate something similar to a heatmap of roads that users of the website
-ride. With this heatmap, the weights could be improved and generated based on
-popularity.
+algorithm. As mentioned in Section~\ref{sec:back}, cyclists generally perform
+their own version of this algorithm to find routes that they will enjoy. Once
+the web experience is fully fleshed out users will upload all of their rides
+to the website so that they can be viewed and analyzed in the future. This also
+provides extremely valuable data for the algorithm, since user generated routes
+may favor better, more interesting roads than a purely weight driven experience.
+With this data, the algorithm could add a ``heatmap'' layer to the algorithm
+that keeps track of how popular a road is. Roads that are seldom used could be
+weighted negatively, while extremely popular roads would be almost mandatorily
+included in generated routes.
 
-Finally, it might be interesting to generate routes that are not necessarily
-circuits. Loops are generally more useful since cyclists are likely to want
-to return home after a good training ride, but it might also be useful to
-have some sort of quasi-navigation that aims for the most fun route
-between two locations rather than the most direct route.
+Another valuable extension would be to generate routes that are not necessarily
+circuits. In this paper, we have focused on loops since cyclists are likely to
+want to return home after a good training ride. However, it might also be useful
+to have some sort of quasi-navigation that aims for the most fun route
+between two locations rather than the most direct route. This way, riders might
+be able to mix commute and training.
+
+Additionally, it might be worthwhile to explore other methods for generating
+routes. A weight based algorithm makes randomization fairly easy, but other
+concepts certainly exist. Another idea might be to just take a
+breadth-first-search that returns to the start and choose at random one of the
+solutions that is within some epsilon of the distance goal. This approach may
+be a pretty solid one, but it does raise some challenges when extended for
+additional goals, and enumerating all possibilities may prove computationally
+taxing, especially if space constraints become an issue.
+
+\bibliographystyle{plainnat}
+\raggedright
+\bibliography{paper}
 

### 2013-12-04 paper.tex
Final commit before G's reading.

@@
 
+\begin{figure}
+  \includegraphics[width=3in]{images/route.png}
+  \caption{A Short Route in Troy} \label{img:route}
+\end{figure}
+
+Finally, consider the results that the loop generator produces. A sample route
+is given in Figure~\ref{img:route}. This is a short loop with a distance goal of
+one mile generated in eastern Troy. Unfortunately, some issues with the
+algorithm remain, as there are far too many situations where the algorithm
+creates a U-turn. That being said, it does do a decent job of generating a path
+that covers nearby roads to travel along. Indeed, especially at the beginning of
+the project, the routes don't need to be perfect. Instead, the vision involves
+the user uitlizing the algorithm to generate a prototype for a route and
+altering it slightly to avoid known bad roads or to take scenic detours, and
+other minor adjustments.
+
 \section{Future Work}
@@
 weighted negatively, while extremely popular roads would be almost mandatorily
-included in generated routes.
+included in generated routes. One interesting challenge to avoid here would be
+dealing with population density. That is, there may be a rural road that is
+everything a cyclist could desire, while city riding is absolutely nightmarish.
+Unfortunately, the city also has a much higher population density, so even
+riders riding in the city only to get out of it and find better roads will
+likely add more ``heat'' to unpleasant city roads than to beautiful rural
+roads.
 
@@
 
+All of these pieces are hypothetical additional features to add; however, there
+is room for improvement on the algorithm laid out here as well. Further
+development on this algorithm should include a refinement of the weight
+generation formulas, including experimentation with increasing adherence to the
+ideal loop.
+
 \bibliographystyle{plainnat}

### 2013-12-04 grower/grower.py

@@ -216,7 +216,7 @@ class Grower:
            last, weight) = self.getNextIntersection(prev,node,initweight,start)
           if res == True:
             weight = self.getWeight(prev, last, theta, weight/len(nodes))
-            if node in cycle: weight /= 2
+            if node in cycle: weight /= 8
             weightsum += weight
             info.append((weight, nodes, segmentDist, last))
       except KeyError: pass
@@ -224,7 +224,7 @@ class Grower:
       if len(info) == 0:
         return (False,[])
 
-      rand = random.uniform(0,weightsum)
+      rand = random.gauss(weightsum/2,weightsum/3)
       i = 0
       while i < len(info) and rand > info[i][0]:
         rand -= info[i][0]
@@ -263,7 +263,6 @@ class Grower:
         nodeList.append(node)
         dist += self.distance(prev,node)
 
-        if node == start: break
         rnodes = self.data.routing[self.transport][node].items()
 
         # Unroutable node; do not allow this direction
